### 2016-02-09 MSRChallenge2016.tex
First commit

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Alternate {\ttlit ACM} SIG PrTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawredfe P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2016-02-09 MSRChallenge2016.tex
Changed most of the info in the file
I put my paper there, feel free to edit all of it to include and remove
parts of it as you think it works best. I will remove the unimportant
parts of my contributions

@@
 \documentclass{sig-alternate-05-2015}
+\usepackage{graphicx}
+\graphicspath{ {} }
 
@@
 %Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
 
-\acmPrice{\$15.00}
+%\acmPrice{\$0.00}
 
@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+\conferenceinfo{MSR}{2016 Austin, Texas USA}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\title{Alternate {\ttlit ACM} SIG PrTeX
-Format\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
+\title{Most common replacements performed by programmers when fixing bugs}
+
 %
@@
 
-\numberofauthors{8} %  in this sample file, there are a *total*
+\numberofauthors{3} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+Mauricio Soto\\
+       \affaddr{Carnegie Mellon University}\\
+       \affaddr{Pittsburgh, PA}\\
+       \email{mauriciosoto@cmu.edu}
 % 2nd. author
+\alignauthor Chu Pan Wong   
+       \affaddr{Carnegie Mellon University}\\
+       \affaddr{Pittsburgh, PA}\\
+       \email{email@domain.com}       
+\and  % use '\and' if you need 'another row' of author names
+% 3rd. author
+\alignauthor Ferdinand Lastname
+       \affaddr{Carnegie Mellon University}\\
+       \affaddr{Pittsburgh, PA}\\
+       \email{email@domain.com}
+% 4th. author
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawredfe P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+Claire Le Goues\\
+       \affaddr{Carnegie Mellon University}\\
+       \affaddr{Pittsburgh, PA}\\
+       \email{clegoues@cs.cmu.edu}
 }
@@
 % in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
+%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
+%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
+\date{February 2, 2016}
 % Just remember to make sure that the TOTAL number of authors
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
+\textbf{
+With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered.
+We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.
+}
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
+\textbf{
+We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other.
+We also analyzed, once you have a statement that you want to replace (a faulty statement), what are the most likely statements to replace it for.
+These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
+}
 
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
 \end{abstract}
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
 %
@@
 
-\keywords{ACM proceedings; \LaTeX; text tagging}
+\keywords{Automatic error repair; Maintainability; Human-like patches}
 
 \section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software.
+There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, which is an evolutionary program repair tool and applies four different kinds of possible changes to code in order to find a patch for a given bug.
+These changes are the following: Delete, Replace, Swap and Append.
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+Our research aims to provide guidelines to improve three out of four of these possible changes: Delete, Replace and Append.
+It will provide the data necessary for this tool and other approaches to have a guide on what is the way in which human programmers change their code when coding a fix for a bug.
+This way it will make it more likely for automatic error repair approaches to succeed in finding a patch for a particular error, and also, to provide automatic error repair software with heuristics to make the patches more human-like and therefore more readable and maintainable by human developers.
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+In this article we study the frequency with which human programmers replace, delete and append different statements to their source code in order to fix a bug.
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+\section{Methodology}
+Our methodology is applied to the latest official data dump of Github as of September 2015 provided by \cite{robert}.
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+\subsection{Statements}
+Statements are the building blocks of software.
+There are several kinds of statements in which software can be divided into.
+In our approach we are trying to find patterns in the way human programmers replace, delete or append statements in order to fix a bug in their code.
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+The definitions of statements vary slightly depending on the programming language being used, but regardless of this, the vast majority of statements classifications are very similar independent of the language used.
+For our study we took a very standard classification of statements provided by the Java Development Tools package.
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+In this classification we have twenty two kinds of statements, from which we took fifteen of them for the gathering and analysis of our data.
+The list of statements taken for our analysis is the following:
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+\begin{verbatim}
+AssertStatement
+BreakStatement
+ContinueStatement 
+DoStatement 
+ForStatement 
+IfStatement 
+LabeledStatement
+ReturnStatement 
+SwitchCase 
+SwitchStatement 
+SynchronizedStatement
+ThrowStatement 
+TryStatement 
+TypeDeclarationStatement
+WhileStatement
+\end{verbatim}
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+The remaining six kinds of statements were not considered to be part of our analysis for three main reasons. We will start with this following statement type:
 
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
+\begin{verbatim}
+Block
+\end{verbatim}
 
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+The statement type known as "Block" was not included since our main goal is to provide guidelines to automatic bug repair software to be able to create patches in a more guided way.
+It is irrelevant for an automatic bug repair software to know that an statement was replaced by a "Block", since a Block is an unknown amount of statements concatenated together and knowing that there is an infinite amount of possible permutations of statements that can be a Block, makes it useless to know that an statement was replaced by a Block, since a Block can be basically any possible combination of statements.
 
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
+The next statement type:
+\begin{verbatim}
+EmptyStatement 
+\end{verbatim}
 
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
+The statement known as "EmptyStatement" is an statement that doesn't perform any action.
+Therefore, replacing any statement for an empty statement is equivalent to deleting that statement, and that case is treated separately.
 
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
+The third reason of why the remaining five statement types were not included in the analysis is because these statement types are not supported by Boa as a StatementKind to the best of our knowledge.
+The remaining five statement types are the following:
 
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
+\begin{verbatim}
+ConstructorInvocation
+EnhancedForStatement
+ExpressionStatement
+SuperConstructorInvocation
+VariableDeclarationStatement
+\end{verbatim}
 
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
+We focused on the initial list of fifteen statement kinds mentioned at the beginning of the section.
 
@@
 \centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
+\caption{Amount of appearances per replace kind}
+\resizebox{\textwidth}{100pt}{
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
+ &Assert&Break&Continue&Do& For&If&Label&Return&Switch&Switch& Synchronized&Throw&Try&TypeDecl&While
+\\ \hline
+\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
+\\ \hline
+\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
+ \\ \hline
+\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
+ \\   \hline
+\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
+  \\ \hline
+\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
+ \\ \hline
+\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
+ \\ \hline
+\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
+\\ \hline
+\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
+ \\ \hline
+\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
+\\ \hline
+\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
+ \\ \hline
+\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
+ \\ \hline
+\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
+ \\ \hline
+\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
+ \\ \hline
+\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
+ \\ \hline
+\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
+ \\ \hline
+\end{tabular}
+}
 \end{table*}
-% end the environment with {table*}, NOTE not {table}!
 
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
+\subsection{Data Collection}
+We used the Boa platform \cite{robert} to be able to query the Github repository looking for patterns that humans use to patch errors in the their code.
+Our main goal is to provide automatic error fixing approaches with the data necessary to be able to replace, delete and append statements in the patches being created by them.
 
-This sample document contains examples of \textbf{.eps} files to be
-displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
-\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
-\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
-each of these is found in the \textit{Author's Guide}.
+Our Boa queries are divided in two types:
 
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
+\subsubsection{Replace Query}
+The replace query is a query in which first we set the project that we are going to use, which is the Github dump of September 2015 provided by \cite{robert}.
 
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
+We then create a visitor to traverse all the nodes of this repository.
+First thing the visitor does is to ask weather the node is a Revision, and if it is, then it asks if it is a fixing revision.
+Therefore we are analyzing only files that were already committed and are now being reviewed to fix an error.
+We use Boa's infrastructure to do this by visiting the node they label as "Revision" and then calling the function defined by Boa "isfixingrevision()".
 
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
+A replacement needs two statements, one that is deleted and another one that is inserted.
+We then go through all the files that have been changed in this data set asking for two conditions: it must be a fixing revision and there must have been a previous version of this file before.
+If these conditions are met then we initialize two counters: one for the first statement we are analyzing (the one that was deleted), and another one for the second statement we are analyzing (the one that was inserted).
 
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
+At this point we visit each statement in the previous state of that changed file, before the change was applied and we count the amount of appearances of the first statement we are analyzing (the one that was deleted), and then we count the amount of appearances of the second statement we are analyzing (the one that was inserted).
+We save these values, and do the same for the latest version of the file and save these values as well.
 
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
+We then compare these results to see if either the first and second statements being analyzed increased or decreased. Depending on these we have two conditionals:
 
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
+If the amount of occurrences of the first statement decreased and the amount of occurrences  of the second statement increased on the same file, then we say that the first statement was replaced by the second statement in that file.
+Likewise, if the amount of occurrences of the first statement increased and the amount of occurrences  of the second statement decreased on the same file, we say that the second statement was replaced by the first statement in that file.
+We count the amount of files in which this happens for each of these two cases.
 
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
+We need to test this with all the possible combinations of two different statement types since we want to know what is the probability of an specific statement to be replaced by another specific statement.
+For example, we want to know how often does a For loop gets replaced by a While loop in a successful human written patch, or how often does a Break statement gets replaced by a Continue statement in a successful human written patch.
 
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
+Because of this we have created Table 1 which records the amount of replaces happening from one kind of statement to another.
+It is a matrix of fifteen by fifteen slots that describes which statements are being replaced by which other.
+
+The numbers in the slots represent the amount of files in which that replacement took place.
+In the first column we have the list of statements that are being replaced, and on the top row we have the list of statements for which that statement was replaced for.
+For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column), we have a 32, which means that from the 46,301,429 files categorized by Boa as fixing revisions in Github in the month of September 2015, only 32 of them replaced a DoStatement for an AssertStatement.
+
+It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the statement kind, since it is counting the amount of appearances of each statement kind.
+So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file is going to remain the same
+
+\subsubsection{Delete/Append Query}
+
+The Delete/Append Query is similar to the Replace Query with some variations to count for the amount of times that a file was changed and a particular statement kind was either deleted or append, and the rest of the statement kinds remained the same.
+
+We created a Boa file in which first we create an output variable to count all the amount of files in which a statement kind was deleted or appended.
+Similar to the previous query, we visit all the files labeled as fixing revisions, then visit every node of the previous version of the revision, counting the amount of statement kinds of each one of the possible fifteen different ones.
+We then do the same for the later version of the revision, counting the different statement kinds.
+
+Finally, we compare the amounts of the previous version, with the new version.
+For each of the revisions, we ask if the amount of statements stays the same for all the statement kinds, except for X kind of statement.
+When the amount of statements is different in the previous version than the latest version for X kind of statement.
+Then we ask if X kinds of statement is greater in the previous version or the latest version.
+If the amount of appearances of X kind of statement is greater in the previous version than the latest version, and all the remaining fourteen statement kinds have the same amount in the previous than the latest version, then we say that one or more of the statements of kind X were deleted.
+Otherwise, if the latest version has a greater amount of appearances of X kind of statement and the rest have the same amount of appearances in both the previous and the latest version, then we say that one or more statements of kind X were appended or added to the fixing revision.
+
+%\begin{table}
+%\centering
+%\caption{Amount of appearances of replaces}
+%\begin{tabular}{ | c | c | c | }\hline
+% &Deleted&Appended
+%\\ \hline
+%\texttt{Assert} & &\\ \hline
+%\texttt{Break} &   & \\ \hline
+%\texttt{Continue} & & \\   \hline
+%\texttt{Do} & &  \\ \hline
+%\texttt{For} & & \\ \hline
+%\texttt{If} &  &  \\ \hline
+%\texttt{Label} & & \\ \hline
+%\texttt{Return} &  & \\ \hline
+%\texttt{Case} &  & \\ \hline
+%\texttt{Switch} &  & \\ \hline
+%\texttt{Synchronized} & & \\ \hline
+%\texttt{Throw} &  &\\ \hline
+%\texttt{Try} &   & \\ \hline
+%\texttt{TypeDecl} &&    \\ \hline
+%\texttt{While} &   &   \\ \hline
+%\end{tabular}
+%\end{table}
+
+\subsection{Data Analysis}
+Our queries were ran on the dump of Github of September 2015.
+In these real life projects we found 46,301,429 files being fixed.
+In these files, there is a total of 517,281 statement kinds being replaced, and 511,198 replacing these statements kinds.
+
+We analyzed each of these files looking for statement kinds being either replaced by other kinds, deleted or appended to the file.
+
+We found that the most common Replacer statement kind, meaning the statement kind that most commonly replaces others is the \textbf{If Statement} with 101,366 appearances.
+The least common Replacer, meaning the statement kind which is less likely to replace other statement kinds is the \textbf{Type Declaration Statement} with 447 appearances.
+
+The most common Replacee, which is the most likely statement kind to be replaced by another statement kind is the \textbf{Return Statement} with 111,938 appearances.
+The least common Replacee, which is the least common statement to be replaced by another statement kind is the \textbf{Type Declaration Statement} with 399 appearances.
+
+\subsubsection{Likeliness of replacement}
+This study is directly applicable to automatic software repair.
+Most common tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire} first find a faulty statement using several different fault localization techniques \cite{zach}, and once they have that faulty statement, they apply different kinds of edits to it, usually at random.
+Which makes it equally likely to replace an statement for another without looking at the kinds of statements being replaced.
+
+With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
+By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
+
+For example, if we have a faulty statement that happens to be a For Statement.
+Then we can look up in Table 1 the For Statement Column (6th column).
+If we add all the values in that column, we get 59,870 changes in which a For Statement was replaced by some other kind of statement.
+Then we calculate the percentage of each of the values in the column to see the likeliness of each of the statements to replace it for, and in this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.88\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.73\% of likeliness to replace a For Statement.
+
+\subsubsection{Most common replacements}
+Our results show that the most common replacement is when developers replace a Return statement for an If statement.
+This showed up in 30,489 files in the code database.
+The second most common replacement is an If statement being replaced by a Return statement, which had 28,536 appearances in the code database.
+Third to that, is a Return statement being replaced by a Throw statement.
+
+\includegraphics[scale=0.5]{g1.png}
+
+\subsubsection{Least common replacements}
+On the opposite side of the data, we can see that the least common replacement was an Assert statement replacing a Type Declaration statement.
+This was the only replacement to have zero appearances in our search through the 46,301,429 files being fixed.
+Close to it, as the second least common replacement was replacing a Do statement for a Type Declaration statement, with one appearance in our code database, and on third place, the replacement of a Label being replaced by a Type Declaration Statement had one appearance in our code database.
+
+\includegraphics[scale=0.5]{g2.png}
+
+\section{Related Work}
+A similar study was performed by Dongsun Kim et al.
+\cite{dongsun} in which they look for the most common ways in which programmers patch bugs in software.
+The researchers developed a variation of the tool Genprog \cite{weimer}\cite{claire} with several different templates resembling patters programmers use to patch bugs.
+
+A good complement for this paper is \cite{hao}, where they search additions and deletions in a smaller data set.
+In this paper, we focus on the replacements, which have been left out of the analysis of \cite{hao}.
 
 \section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
+The findings of our study provide a set of useful guidelines for automatic program repair tools with which their search for a patch can be now improved by having the knowledge of how likely it is to replace a faulty statement by the different kinds of statements available.
+
 %\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
 
@@
 %\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
+
+\begin{thebibliography}{9}
+
+\bibitem{robert}
+  Robert Dyer et al.,
+  \emph{Boa: A Language and Infrastructure for Analyzing Ultra-Large-Scale Software Repositories},
+35th International Conference on Software Engineering; ICSE 2013, San Francisco CA, USA
+
+\bibitem{hao}
+Hao Zhong, Zhendong Su
+\emph{An Empirical Study on Real Bug Fixes},
+In Proceedings of ICSE 2015, Firenze, Italy, May 16-24, 2015.
+
+\bibitem{kai}
+Kai Pan et al.
+\emph{Towards an understanding of bug fix patterns},
+Journal
+Empirical Software Engineering
+Volume 14 Issue 3, June 2009 
+Pages 286 - 315
+
+\bibitem{dongsun}
+Dongsun Kim et al.
+\emph{Automatic patch generation learned from human-written patches},
+Proceeding
+ICSE '13 Proceedings of the 2013 International Conference on Software Engineering
+
+\bibitem{zach}
+Zachary P.Fry and Westley Weimer
+\emph{A human study of fault localization accuracy},
+ICSM '10 Proceedings of the 2010 IEEE International Conference on Software Maintenance
+
+\bibitem{claire}
+Claire Le Goues, ThanhVu Nguyen, Stephanie Forrest, Westley Weimer
+\emph{GenProg: A Generic Method for Automated Software Repair.} 
+IEEE Trans. Software Engineering 38(1): 54-72 (January/February 2012)
+
+\bibitem{weimer}
+Westley Weimer, ThanVu Nguyen, Claire Le Goues, Stephanie Forrest
+\emph{Automatically Finding Patches Using Genetic Programming.}
+International Conference on Software Engineering (ICSE) 2009: 364-374
+
+\end{thebibliography}
+
 %\balancecolumns % GM June 2007

### 2016-02-09 MSRChallenge2016.tex
Changed title
Removed some unimportant part of my sections

@@
 
-\title{Most common replacements performed by programmers when fixing bugs}
+\title{A deeper look into bug fixes: patterns, replacements, deletions, and additions}
 
@@
 
-\subsection{Statements}
-Statements are the building blocks of software.
-There are several kinds of statements in which software can be divided into.
-In our approach we are trying to find patterns in the way human programmers replace, delete or append statements in order to fix a bug in their code.
-
-The definitions of statements vary slightly depending on the programming language being used, but regardless of this, the vast majority of statements classifications are very similar independent of the language used.
-For our study we took a very standard classification of statements provided by the Java Development Tools package.
-
-In this classification we have twenty two kinds of statements, from which we took fifteen of them for the gathering and analysis of our data.
-The list of statements taken for our analysis is the following:
-
-\begin{verbatim}
-AssertStatement
-BreakStatement
-ContinueStatement 
-DoStatement 
-ForStatement 
-IfStatement 
-LabeledStatement
-ReturnStatement 
-SwitchCase 
-SwitchStatement 
-SynchronizedStatement
-ThrowStatement 
-TryStatement 
-TypeDeclarationStatement
-WhileStatement
-\end{verbatim}
-
-The remaining six kinds of statements were not considered to be part of our analysis for three main reasons. We will start with this following statement type:
-
-\begin{verbatim}
-Block
-\end{verbatim}
-
-The statement type known as "Block" was not included since our main goal is to provide guidelines to automatic bug repair software to be able to create patches in a more guided way.
-It is irrelevant for an automatic bug repair software to know that an statement was replaced by a "Block", since a Block is an unknown amount of statements concatenated together and knowing that there is an infinite amount of possible permutations of statements that can be a Block, makes it useless to know that an statement was replaced by a Block, since a Block can be basically any possible combination of statements.
-
-The next statement type:
-\begin{verbatim}
-EmptyStatement 
-\end{verbatim}
-
-The statement known as "EmptyStatement" is an statement that doesn't perform any action.
-Therefore, replacing any statement for an empty statement is equivalent to deleting that statement, and that case is treated separately.
-
-The third reason of why the remaining five statement types were not included in the analysis is because these statement types are not supported by Boa as a StatementKind to the best of our knowledge.
-The remaining five statement types are the following:
-
-\begin{verbatim}
-ConstructorInvocation
-EnhancedForStatement
-ExpressionStatement
-SuperConstructorInvocation
-VariableDeclarationStatement
-\end{verbatim}
-
-We focused on the initial list of fifteen statement kinds mentioned at the beginning of the section.
-
 \begin{table*}
@@
 So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file is going to remain the same
-
-\subsubsection{Delete/Append Query}
-
-The Delete/Append Query is similar to the Replace Query with some variations to count for the amount of times that a file was changed and a particular statement kind was either deleted or append, and the rest of the statement kinds remained the same.
-
-We created a Boa file in which first we create an output variable to count all the amount of files in which a statement kind was deleted or appended.
-Similar to the previous query, we visit all the files labeled as fixing revisions, then visit every node of the previous version of the revision, counting the amount of statement kinds of each one of the possible fifteen different ones.
-We then do the same for the later version of the revision, counting the different statement kinds.
-
-Finally, we compare the amounts of the previous version, with the new version.
-For each of the revisions, we ask if the amount of statements stays the same for all the statement kinds, except for X kind of statement.
-When the amount of statements is different in the previous version than the latest version for X kind of statement.
-Then we ask if X kinds of statement is greater in the previous version or the latest version.
-If the amount of appearances of X kind of statement is greater in the previous version than the latest version, and all the remaining fourteen statement kinds have the same amount in the previous than the latest version, then we say that one or more of the statements of kind X were deleted.
-Otherwise, if the latest version has a greater amount of appearances of X kind of statement and the rest have the same amount of appearances in both the previous and the latest version, then we say that one or more statements of kind X were appended or added to the fixing revision.
 

### 2016-02-13 MSRChallenge2016.tex
Into done

@@
        \email{mauriciosoto@cmu.edu}
+       % 3rd. author
+\alignauthor Ferdian Thung\\
+       \affaddr{University}\\
+       \affaddr{City}\\
+       \email{email@domain.com}
 % 2nd. author
-\alignauthor Chu Pan Wong   
+\alignauthor Chu Pan Wong   \\
        \affaddr{Carnegie Mellon University}\\
@@
 \and  % use '\and' if you need 'another row' of author names
-% 3rd. author
-\alignauthor Ferdinand Lastname
-       \affaddr{Carnegie Mellon University}\\
-       \affaddr{Pittsburgh, PA}\\
-       \email{email@domain.com}
 % 4th. author
@@
        \affaddr{Pittsburgh, PA}\\
+       \email{clegoues@cs.cmu.edu}
+% 5th. author
+\alignauthor
+David\\
+       \affaddr{University}\\
+       \affaddr{City}\\
        \email{clegoues@cs.cmu.edu}       
@@
 Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software.
-There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, which is an evolutionary program repair tool and applies four different kinds of possible changes to code in order to find a patch for a given bug.
+There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an evolutionary program repair tool which applies four different kinds of possible edits to code in order to find a patch for a given bug.
 These changes are the following: Delete, Replace, Swap and Append.
+
+Another well known approach is PAR \cite{dongsun}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair it.
+In this paper we have taken 7 out of the 10 PAR templates and tested how common they are in the repairs made by programmers in the latest official data dump of Github as of September 2015 provided by \cite{robert}.
 
@@
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
- &Assert&Break&Continue&Do& For&If&Label&Return&Switch&Switch& Synchronized&Throw&Try&TypeDecl&While
+ &Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
 \\ \hline

### 2016-02-15 MSRChallenge2016.tex
Added characteristic section

@@
 
+\section{Results}
+
+This section investigates how do developer fix bugs from three different
+perspectives. To begin with, we show some characteristics of real-world bug
+fixes.  Afterwards, we look deeper to find out what kinds of statements are
+usually added, modified or deleted by human developers to fix bugs. Lastly, we
+show how common PAR's fixing templates are in our dataset.
+
+\subsection{Characteristics}
+
+This subsection shows a bird's-eye view of real-world bug fixes at
+ultra-large-scale. We did our analysis on the \emph{2015 September/Github}
+dataset on Boa. This dataset includes $7,830,023$ Java projects with
+$23,229,406$ revisions. Among all the revisions, $4,590,679$ revisions are
+identified by Boa as bug fixing revisions. Our analysis in this subsection
+focuses on these bug fixing revisions. We hope that this population
+is big enough to reflect the bug fixing practice.
+
+To begin with, we are interested in:
+
+\begin{quote}
+	How many files are changed to fix a bug?
+\end{quote}
+
+To answer this question, we identified all the bug fixing revisions in our
+dataset and count the number of changed files. In total, $52,052,571$ files got
+changed. Thus, on average each bug fixing revision changes 11.3 files.  This
+number is surprisingly high because most automatic program repair techniques
+assume that bugs are local in most cases. There could be several reasons behind
+this number. It could be the case that other software artifacts (e.g.
+documentation) are updated after bug fixing. It could also be the case that bug
+fixing commit also contains changes that are not related to fixing bug (e.g. new
+features, refactoring). To better understand why so many files are changed, we
+continue to ask:
+
+\begin{quote}
+	What are the file types of those changed files?
+\end{quote}
+
+In Boa, each changed file is represented by a \emph{ChangedFile} node, and it
+has a field called \emph{FileKind}, describing the type of each file.
+Table~\ref{tbl:fileType} shows the file types that Boa could identify. To answer
+this question, we iterate all the changed files in each bug fixing revision and
+count the total number for each file type. Results are shown in
+Table~\ref{tbl:fileType}.
+
+\begin{table}
+\centering
+  \begin{tabular}{| c | r | r |}
+  \hline
+  File Kind & Total Number & Average \\ \hline \hline
+  BINARY & 752,945 & 0.16 \\ \hline
+  SOURCE\_JAVA\_ERROR & 2,073,558 & 0.45 \\ \hline
+  SOURCE\_JAVA\_JLS2 & 2,607,413 & 0.57 \\ \hline
+  SOURCE\_JAVA\_JLS3 & 15,748,967 & 3.43 \\ \hline
+  SOURCE\_JAVA\_JLS4 & 83,798 & 0.02 \\ \hline
+  TEXT & 541,023 & 0.12 \\ \hline
+  XML & 6,818,299 & 1.49 \\ \hline
+  UNKNOWN & 23426568 & 5.10 \\ \hline
+  \end{tabular}
+  \caption{File Types of Changed Files}
+  \label{tbl:fileType}
+\end{table}
+
+\emph{SOURCE\_JAVA\_ERROR} file kind represents files that Boa failed to parse.
+\emph{JLS2} refers to Java files that are written in all versions of Java
+languages up to and including J2SE 1.4. \emph{JLS3} refers to J2SE 1.5, and JLS4
+refers to J2SE 1.6 and 1.7. Boa documentation does not explicitly explain what
+is \emph{TEXT} and what is \emph{UNKNOWN}. Our assumption is that \emph{TEXT}
+refers to files whose file name ends with ``.txt'', and \emph{UNKNOWN} refers to
+all other kinds of files (e.g. .c file, .cpp files).
+
+From Table~\ref{tbl:fileType}, we can see that \emph{TEXT} files and
+\emph{BINARY} files are changed least frequently. This is not surprising because
+\emph{TEXT} files are usually documentation files, and \emph{BINARY} files
+should only be changed in rare case (e.g.  milestone, new release, dependency
+update). If we consider all 4 kinds of Java files as one kind, then on average
+each bug fixing revision changes $4.47$ Java files. But still, it does not
+conform to our assumption of bug locality. \emph{XML} files in Java projects
+usually represents build files, thus changing one build file after each bug
+fixing is not surprising.  What surprises us is that \emph{UNKNOWN} files are
+changed most frequently. Note that all the projects in our dataset are Java
+projects, so it is reasonable to assume that these files are not source files
+that written in other programming languages.  One possible explanation is that
+they are test resources. However, due to the limitations of Boa, we can not look
+into the content of these \emph{UNKNOWN} files.
+
+Since Boa does not distinguish Java files that related to functionality and Java
+files that related to testing, it could be the case that among those $4.47$
+changed Java files, some of them are related to testing, such as modifying the
+test cases and creating new test classes. To better understand what changes are
+usually made to Java source code files, we continue to ask:
+
+\begin{quote}
+	How often do developers introduce new classes, methods, fields, variables in
+	bug fixing commits?
+\end{quote}
+
+This research question is interesting because most automatic program repair
+approaches could not create new classes/methods/fields/variables to fix bugs.
+Most approaches guess and synthesize the patches based on existing source code.
+
+Table~\ref{tbl:new} shows our analysis results. This table shows that
+introducing new classes and new variables are rare. This is good news for
+automatic program repair approaches. On average, we still have $0.69$ new method
+per bug fix. If we consider the possibility of creating new test method (i.e.
+methods that annotated by @Test if JUnit is used), this number is not that
+scary. However, what surprises us is that $1.32$ fields are created per bug fix.
+This indicates that automatic program repair approaches should pay attention to
+the state of the class when fixing Java programs.
+
+\begin{table}
+\centering
+  \begin{tabular}{| c | r | r |}
+  \hline
+  Introducing & Total Number & Average \\ \hline \hline
+  Class & 729201 & 0.16 \\ \hline
+  Methods & 3186867 & 0.69 \\ \hline
+  Fields & 6076646 & 1.32 \\ \hline
+  Variables & 924259 & 0.2 \\ \hline
+  \end{tabular}
+  \caption{File Types of Changed Files}
+  \label{tbl:new}
+\end{table}
+
 \begin{thebibliography}{9}

### 2016-02-15 MSRChallenge2016.tex
update methodology section

@@
 Our methodology is applied to the latest official data dump of Github as of September 2015 provided by \cite{robert}.
+In the following subsections, we first describe data source and objective of our study.
+We then describe how we detect bug fixing patterns in PAR to find out how common they are the dataset.
+Last but not least, we describe our approach to detect Delete, Replace, and Append bug-fixing patterns.
 
@@
 
-\subsection{Data Collection}
+\subsection{Data Source and Research Objective}
 We used the Boa platform \cite{robert} to be able to query the Github repository looking for patterns that humans use to patch errors in the their code.
-Our main goal is to provide automatic error fixing approaches with the data necessary to be able to replace, delete and append statements in the patches being created by them.
+Our main goal is to provide guidelines for automatic error fixing approaches by providing necessary information regarding historical replace, delete and append statements in human written patches.
 
-Our Boa queries are divided in two types:
+\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
+The bug fixing patterns that we analyze in this work are adopted from Kim et al. paper~\cite{dongsun}. The following is the description of each considered pattern.
+\begin{enumerate}
+	\item {\bf Altering method parameters (AMP)}\\
+	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
+	{\bf Description:} This pattern changes the input for method parameters.
+	\item {\bf Calling another method with the same parameters (MSM)}\\
+	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
+	{\bf Description:} This pattern changes the method name.
+	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
+	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
+	{\bf Description:} This pattern adds one more parameter to the method.
+	\item {\bf Changing a branch condition (CBC)}\\
+	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
+	{\bf Description:} This pattern adds or removes condition.
+	\item {\bf Initializing an object (IAO)}\\
+	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
+	{\bf Description:} This pattern adds a initialization to object declaration.
+	\item {\bf Adding a null checker (ANC)}\\
+	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
+	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
+	\item {\bf Adding an array out of bound checker (AOB)}\\
+	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
+	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
+\end{enumerate}
 
-\subsubsection{Replace Query}
+To analyze bug fixing patterns, we utilizes Boa's language infrastructure~\cite{robert}.
+It contains a large number of dataset and provide a domain specific language to perform analysis on source code.
+Despite this advantage, Boa still have limited capability that prevents us from performing precise detection of bug fixing patterns.
+For example, it is unable to perform a diff between two file versions, which is needed to compare the pre-fix and the post-fix version of a buggy file.
+Thus, rather than finding the exact count of bug fixing patterns, we will find an approximate count of those patterns.
+The following are descriptions on how we detect each pattern.
+
+\begin{enumerate}
+	\item {\bf AMP Pattern}\\
+	To detect AMP pattern, for both pre-fix and post-fix version of a buggy file, we create a custom method call signature.
+This signature contains method name, literal parameter, and variable parameter.
+we consider parameter containing custom expression as OTHER.
+This is due to inexistence of function that can print Abstract Syntax Tree (AST) back to source code.
+we discard method signatures that appear both in pre-fix and post-fix version.
+We then find whether there exists method with the same name and the same number of parameters, but different parameter signatures in pre-fix and post-fix version.
+If it exists, we consider that AMP pattern is found.
+
+	\item {\bf MSM Pattern}\\
+	To detect MSM pattern, we create method signature similar like when detecting AMP pattern.
+This time, we find whether there exists method with the exact same parameter signature but different name in pre-fix and post-fix version.
+If it exists, we consider that MSM pattern is found.
+
+	\item {\bf COM Pattern}\\
+	To detect COM pattern, we create method signature similar like when detecting AMP and COM pattern.
+This time, we find whether there are exists method with the same name, but the number of parameters in pre-fix and post-fix version differs by one.
+If it exists, we consider that COM pattern is found.
+
+	\item {\bf CBC Pattern}\\ 
+	To detect CBC pattern, we count the number of { \em logical and} and {\em logical or} inside if conditional expression for both pre-fix and post-fix version.
+we assume that the addition/removal of logical operators indicate addition/removal of condition.
+If there are count differences between pre-fix and post-fix version, we consider that CBC pattern is found.
+
+	\item {\bf IAO Pattern}\\
+	To detect IAO pattern, we count the number of NEW expression in variable declaration for both pre-fix and post-fix version.
+If there are count differences between pre-fix and post-fix version, we consider that IAO pattern is found.
+
+	\item {\bf ANC Pattern}\\
+	To detect ANC pattern, we count the number of if conditional expression that contains {\em !=null} or {\em ==null} for both pre-fix and post-fix version.
+If there are count differences between pre-fix and post-fix version, we consider that ANC pattern is found.
+
+	\item {\bf AOB Pattern}\\
+	To detect AOB pattern, we count the number of if conditional expression that contains  {\em expr<var.length} or {\em var.length>expr} for both pre-fix and post-fix version.
+If there are count differences between pre-fix and post-fix version, we consider that AOB pattern is found.
+
+\end{enumerate}
+
+\subsection{Replace Query}
 The replace query is a query in which first we set the project that we are going to use, which is the Github dump of September 2015 provided by \cite{robert}.
@@
 
-%\begin{table}
-%\centering
-%\caption{Amount of appearances of replaces}
-%\begin{tabular}{ | c | c | c | }\hline
-% &Deleted&Appended
-%\\ \hline
-%\texttt{Assert} & &\\ \hline
-%\texttt{Break} &   & \\ \hline
-%\texttt{Continue} & & \\   \hline
-%\texttt{Do} & &  \\ \hline
-%\texttt{For} & & \\ \hline
-%\texttt{If} &  &  \\ \hline
-%\texttt{Label} & & \\ \hline
-%\texttt{Return} &  & \\ \hline
-%\texttt{Case} &  & \\ \hline
-%\texttt{Switch} &  & \\ \hline
-%\texttt{Synchronized} & & \\ \hline
-%\texttt{Throw} &  &\\ \hline
-%\texttt{Try} &   & \\ \hline
-%\texttt{TypeDecl} &&    \\ \hline
-%\texttt{While} &   &   \\ \hline
-%\end{tabular}
-%\end{table}
+\subsection{Delete/Append Query}
+The Delete/Append Query is similar to the Replace Query with some variations to count for the amount of times that a file was changed and a particular statement kind was ei- ther deleted or append, and the rest of the statement kinds remained the same.
+
+We created a Boa file in which first we create an output variable to count all the amount of files in which a statement kind was deleted or appended.
+Similar to the previous query, we visit all the files labeled as fixing revisions, then visit ev- ery node of the previous version of the revision, counting the amount of statement kinds of each one of the possible fifteen different ones.
+We then do the same for the later version of the revision, counting the different statement kinds.
+
+Finally, we compare the amounts of the previous version, with the new version.
+For each of the revisions, we ask if the amount of statements stays the same for all the statement kinds, except for X kind of statement.
+When the amount of statements is different in the previous version than the latest version for X kind of statement.
+Then we ask if X kinds of statement is greater in the previous version or the latest ver- sion.
+If the amount of appearances of X kind of statement is greater in the previous version than the latest version, and all the remaining fourteen statement kinds have the same amount in the previous than the latest version, then we say that one or more of the statements of kind X were deleted.
+Otherwise, if the latest version has a greater amount of ap- pearances of X kind of statement and the rest have the same amount of appearances in both the previous and the latest version, then we say that one or more statements of kind X were appended or added to the fixing revision.
 

### 2016-02-15 MSRChallenge2016.tex
high level todos

@@
 \usepackage{graphicx}
+\usepackage[usenames,dvipsnames]{color}
+\usepackage{soul} 
+\usepackage{booktabs}
+
+\newcommand{\todo}[1]
+  {{\scriptsize \textbf{\color{red} {#1}}}}
+
 \graphicspath{ {} }
@@
 Mauricio Soto\\
+       \affaddr{School of Computer Science}\\
        \affaddr{Carnegie Mellon University}\\
@@
 Claire Le Goues\\
+       \affaddr{School of Computer Science}\\
        \affaddr{Carnegie Mellon University}\\
@@
 \alignauthor
-David\\
+David Lo\\
        \affaddr{University}\\
@@
 \section{Introduction}
-Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software.
-There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an evolutionary program repair tool which applies four different kinds of possible edits to code in order to find a patch for a given bug.
-These changes are the following: Delete, Replace, Swap and Append.
+\todo{High level todo, probably for Mau since I think it's his bibtex: please
+  change the bibtex keys to take the form ``lastnameYear'', and then fix the
+  citations.}
+\todo{Also, please always include a non-breaking space (a tilde, look at the
+  latex for an example) between a word and the cite tag, and include multiple
+  references on a line in a single citation tag (again, look at the latex for an
+  example; I'll do this once, but would like you to fix the rest when appropriate.}
+Automatic bug repair is the branch of computer science that deals with automated
+ways to repair errors in software. There have been several approaches taken
+towards improving the different methodologies to repair bugs in software
+automatically \cite{dongsun,weimer,claire,kai}, one of the
+most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
+evolutionary program repair tool which applies four different kinds of possible
+edits to code in order to find a patch for a given bug. These changes are the
+following: Delete, Replace, Swap and Append.
 
-Another well known approach is PAR \cite{dongsun}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair it.
-In this paper we have taken 7 out of the 10 PAR templates and tested how common they are in the repairs made by programmers in the latest official data dump of Github as of September 2015 provided by \cite{robert}.
+Another well known approach is PAR \cite{dongsun}, which creates 10 different
+repair templates and applies them to the buggy code in an effort to repair
+it. In this paper we have taken 7 out of the 10 PAR templates and tested how
+common they are in the repairs made by programmers in the latest official data
+dump of Github as of September 2015 provided by \cite{robert}.
 
-Our research aims to provide guidelines to improve three out of four of these possible changes: Delete, Replace and Append.
-It will provide the data necessary for this tool and other approaches to have a guide on what is the way in which human programmers change their code when coding a fix for a bug.
-This way it will make it more likely for automatic error repair approaches to succeed in finding a patch for a particular error, and also, to provide automatic error repair software with heuristics to make the patches more human-like and therefore more readable and maintainable by human developers.
+Our research aims to provide guidelines to improve three out of four of these
+possible changes: Delete, Replace and Append. It will provide the data necessary
+for this tool and other approaches to have a guide on what is the way in which
+human programmers change their code when coding a fix for a bug. This way it
+will make it more likely for automatic error repair approaches to succeed in
+finding a patch for a particular error, and also, to provide automatic error
+repair software with heuristics to make the patches more human-like and
+therefore more readable and maintainable by human developers.
 
-In this article we study the frequency with which human programmers replace, delete and append different statements to their source code in order to fix a bug.
+In this article we study the frequency with which human programmers replace,
+delete and append different statements to their source code in order to fix a
+bug.
 
 \section{Methodology}
-Our methodology is applied to the latest official data dump of Github as of September 2015 provided by \cite{robert}.
-In the following subsections, we first describe data source and objective of our study.
-We then describe how we detect bug fixing patterns in PAR to find out how common they are the dataset.
-Last but not least, we describe our approach to detect Delete, Replace, and Append bug-fixing patterns.
+Our methodology is applied to the latest official data dump of Github as of
+September 2015 provided by \cite{robert}. In the following subsections, we first
+describe data source and objective of our study. We then describe how we detect
+bug fixing patterns in PAR to find out how common they are the dataset. Last but
+not least, we describe our approach to detect Delete, Replace, and Append
+bug-fixing patterns.
 
@@
 
-To analyze bug fixing patterns, we utilizes Boa's language infrastructure~\cite{robert}.
-It contains a large number of dataset and provide a domain specific language to perform analysis on source code.
-Despite this advantage, Boa still have limited capability that prevents us from performing precise detection of bug fixing patterns.
-For example, it is unable to perform a diff between two file versions, which is needed to compare the pre-fix and the post-fix version of a buggy file.
-Thus, rather than finding the exact count of bug fixing patterns, we will find an approximate count of those patterns.
-The following are descriptions on how we detect each pattern.
+To analyze bug fixing patterns, we utilizes Boa's language
+infrastructure~\cite{robert}. It contains a large number of dataset and provide
+a domain specific language to perform analysis on source code. Despite this
+advantage, Boa still have limited capability that prevents us from performing
+precise detection of bug fixing patterns. For example, it is unable to perform a
+diff between two file versions, which is needed to compare the pre-fix and the
+post-fix version of a buggy file. Thus, rather than finding the exact count of
+bug fixing patterns, we will find an approximate count of those patterns. The
+following are descriptions on how we detect each pattern.
 
@@
 \item {\bf AMP Pattern}\\
-	To detect AMP pattern, for both pre-fix and post-fix version of a buggy file, we create a custom method call signature.
-This signature contains method name, literal parameter, and variable parameter.
-we consider parameter containing custom expression as OTHER.
-This is due to inexistence of function that can print Abstract Syntax Tree (AST) back to source code.
-we discard method signatures that appear both in pre-fix and post-fix version.
-We then find whether there exists method with the same name and the same number of parameters, but different parameter signatures in pre-fix and post-fix version.
-If it exists, we consider that AMP pattern is found.
+  To detect AMP pattern, for both pre-fix and post-fix version of a buggy file,
+  we create a custom method call signature. This signature contains method name,
+  literal parameter, and variable parameter. we consider parameter containing
+  custom expression as OTHER. This is due to inexistence of function that can
+  print Abstract Syntax Tree (AST) back to source code. we discard method
+  signatures that appear both in pre-fix and post-fix version. We then find
+  whether there exists method with the same name and the same number of
+  parameters, but different parameter signatures in pre-fix and post-fix
+  version. If it exists, we consider that AMP pattern is found.
 
 \item {\bf MSM Pattern}\\
-	To detect MSM pattern, we create method signature similar like when detecting AMP pattern.
-This time, we find whether there exists method with the exact same parameter signature but different name in pre-fix and post-fix version.
-If it exists, we consider that MSM pattern is found.
+  To detect MSM pattern, we create method signature similar like when detecting
+  AMP pattern. This time, we find whether there exists method with the exact
+  same parameter signature but different name in pre-fix and post-fix
+  version. If it exists, we consider that MSM pattern is found.
 
 \item {\bf COM Pattern}\\
-	To detect COM pattern, we create method signature similar like when detecting AMP and COM pattern.
-This time, we find whether there are exists method with the same name, but the number of parameters in pre-fix and post-fix version differs by one.
-If it exists, we consider that COM pattern is found.
+  To detect COM pattern, we create method signature similar like when detecting
+  AMP and COM pattern. This time, we find whether there are exists method with
+  the same name, but the number of parameters in pre-fix and post-fix version
+  differs by one. If it exists, we consider that COM pattern is found.
 
 \item {\bf CBC Pattern}\\
-	To detect CBC pattern, we count the number of { \em logical and} and {\em logical or} inside if conditional expression for both pre-fix and post-fix version.
-we assume that the addition/removal of logical operators indicate addition/removal of condition.
-If there are count differences between pre-fix and post-fix version, we consider that CBC pattern is found.
+  To detect CBC pattern, we count the number of { \em logical and} and {\em
+    logical or} inside if conditional expression for both pre-fix and post-fix
+  version. we assume that the addition/removal of logical operators indicate
+  addition/removal of condition. If there are count differences between pre-fix
+  and post-fix version, we consider that CBC pattern is found.
 
 \item {\bf IAO Pattern}\\
-	To detect IAO pattern, we count the number of NEW expression in variable declaration for both pre-fix and post-fix version.
-If there are count differences between pre-fix and post-fix version, we consider that IAO pattern is found.
+  To detect IAO pattern, we count the number of NEW expression in variable
+  declaration for both pre-fix and post-fix version. If there are count
+  differences between pre-fix and post-fix version, we consider that IAO pattern
+  is found.
 
 \item {\bf ANC Pattern}\\
-	To detect ANC pattern, we count the number of if conditional expression that contains {\em !=null} or {\em ==null} for both pre-fix and post-fix version.
-If there are count differences between pre-fix and post-fix version, we consider that ANC pattern is found.
+  To detect ANC pattern, we count the number of if conditional expression that
+  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
+  version. If there are count differences between pre-fix and post-fix version,
+  we consider that ANC pattern is found.
 
 \item {\bf AOB Pattern}\\
-	To detect AOB pattern, we count the number of if conditional expression that contains  {\em expr<var.length} or {\em var.length>expr} for both pre-fix and post-fix version.
-If there are count differences between pre-fix and post-fix version, we consider that AOB pattern is found.
+  To detect AOB pattern, we count the number of if conditional expression that
+  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
+  post-fix version. If there are count differences between pre-fix and post-fix
+  version, we consider that AOB pattern is found.
 
@@
 \subsection{Replace Query}
-The replace query is a query in which first we set the project that we are going to use, which is the Github dump of September 2015 provided by \cite{robert}.
+The replace query is a query in which first we set the project that we are going
+to use, which is the Github dump of September 2015 provided by \cite{robert}.
 
-We then create a visitor to traverse all the nodes of this repository.
-First thing the visitor does is to ask weather the node is a Revision, and if it is, then it asks if it is a fixing revision.
-Therefore we are analyzing only files that were already committed and are now being reviewed to fix an error.
-We use Boa's infrastructure to do this by visiting the node they label as "Revision" and then calling the function defined by Boa "isfixingrevision()".
+We then create a visitor to traverse all the nodes of this repository. First
+thing the visitor does is to ask weather the node is a Revision, and if it is,
+then it asks if it is a fixing revision. Therefore we are analyzing only files
+that were already committed and are now being reviewed to fix an error. We use
+Boa's infrastructure to do this by visiting the node they label as "Revision"
+and then calling the function defined by Boa "isfixingrevision()".
 
-A replacement needs two statements, one that is deleted and another one that is inserted.
-We then go through all the files that have been changed in this data set asking for two conditions: it must be a fixing revision and there must have been a previous version of this file before.
-If these conditions are met then we initialize two counters: one for the first statement we are analyzing (the one that was deleted), and another one for the second statement we are analyzing (the one that was inserted).
+A replacement needs two statements, one that is deleted and another one that is
+inserted.  We then go through all the files that have been changed in this data
+set asking for two conditions: it must be a fixing revision and there must have
+been a previous version of this file before. If these conditions are met then we
+initialize two counters: one for the first statement we are analyzing (the one
+that was deleted), and another one for the second statement we are analyzing
+(the one that was inserted).
 
-At this point we visit each statement in the previous state of that changed file, before the change was applied and we count the amount of appearances of the first statement we are analyzing (the one that was deleted), and then we count the amount of appearances of the second statement we are analyzing (the one that was inserted).
-We save these values, and do the same for the latest version of the file and save these values as well.
+At this point we visit each statement in the previous state of that changed
+file, before the change was applied and we count the amount of appearances of
+the first statement we are analyzing (the one that was deleted), and then we
+count the amount of appearances of the second statement we are analyzing (the
+one that was inserted). We save these values, and do the same for the latest
+version of the file and save these values as well.
 
-We then compare these results to see if either the first and second statements being analyzed increased or decreased. Depending on these we have two conditionals:
+We then compare these results to see if either the first and second statements
+being analyzed increased or decreased. Depending on these we have two
+conditionals:
 
-If the amount of occurrences of the first statement decreased and the amount of occurrences  of the second statement increased on the same file, then we say that the first statement was replaced by the second statement in that file.
-Likewise, if the amount of occurrences of the first statement increased and the amount of occurrences  of the second statement decreased on the same file, we say that the second statement was replaced by the first statement in that file.
-We count the amount of files in which this happens for each of these two cases.
+If the amount of occurrences of the first statement decreased and the amount of
+occurrences of the second statement increased on the same file, then we say that
+the first statement was replaced by the second statement in that file. Likewise,
+if the amount of occurrences of the first statement increased and the amount of
+occurrences of the second statement decreased on the same file, we say that the
+second statement was replaced by the first statement in that file. We count the
+amount of files in which this happens for each of these two cases.
 
-We need to test this with all the possible combinations of two different statement types since we want to know what is the probability of an specific statement to be replaced by another specific statement.
-For example, we want to know how often does a For loop gets replaced by a While loop in a successful human written patch, or how often does a Break statement gets replaced by a Continue statement in a successful human written patch.
+We need to test this with all the possible combinations of two different
+statement types since we want to know what is the probability of an specific
+statement to be replaced by another specific statement. For example, we want to
+know how often does a For loop gets replaced by a While loop in a successful
+human written patch, or how often does a Break statement gets replaced by a
+Continue statement in a successful human written patch.
 

### 2016-02-15 MSRChallenge2016.tex
reorg and a bunch of todos

@@
   citations.}
+\todo{Please move the bibitems included explicitly in this document into sigproc.bib
+   and use bibtex.}
 \todo{Also, please always include a non-breaking space (a tilde, look at the
@@
 following: Delete, Replace, Swap and Append.
+
+\todo{We need to integrate the PAR and operator discussion a bit better.  Let's
+  take it up a level of abstraction: there is initial work in applying these
+  techniques to Java that propose a number of mutation operators, and we study
+  the degree to which they apply in practice and make recommendations based on
+  human-provided repairs.  Doing so is a good idea, because patches inspired by
+  human-created repairs are empirically demonstrated to be rated more highly by
+  developers (cite PAR).}
+\todo{I also thought we were doing Par first, and then the replacement studies?}
 
@@
 \subsection{Data Source and Research Objective}
-We used the Boa platform \cite{robert} to be able to query the Github repository looking for patterns that humans use to patch errors in the their code.
-Our main goal is to provide guidelines for automatic error fixing approaches by providing necessary information regarding historical replace, delete and append statements in human written patches.
+We used the Boa platform \cite{robert} to be able to query the Github repository
+looking for patterns that humans use to patch errors in the their code. Our main
+goal is to provide guidelines for automatic error fixing approaches by providing
+necessary information regarding historical replace, delete and append statements
+in human written patches.
 
 \subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
-The bug fixing patterns that we analyze in this work are adopted from Kim et al. paper~\cite{dongsun}. The following is the description of each considered pattern.
+The bug fixing patterns that we analyze in this work are adopted from Kim et
+al. paper~\cite{dongsun}. The following is the description of each considered
+pattern. 
+\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
+  but we need to explain why.}
   \begin{enumerate}
@@
 \end{enumerate}
+\todo{IMPORTANT: Ferdian, where did the results go?  Please add the results of
+  the Par study into results somewhere where it fits.}
 
@@
 \subsection{Delete/Append Query}
-The Delete/Append Query is similar to the Replace Query with some variations to count for the amount of times that a file was changed and a particular statement kind was ei- ther deleted or append, and the rest of the statement kinds remained the same.
+The Delete/Append Query is similar to the Replace Query with some variations to
+count for the amount of times that a file was changed and a particular statement
+kind was ei- ther deleted or append, and the rest of the statement kinds
+remained the same.
 
-We created a Boa file in which first we create an output variable to count all the amount of files in which a statement kind was deleted or appended.
-Similar to the previous query, we visit all the files labeled as fixing revisions, then visit ev- ery node of the previous version of the revision, counting the amount of statement kinds of each one of the possible fifteen different ones.
-We then do the same for the later version of the revision, counting the different statement kinds.
+We created a Boa file in which first we create an output variable to count all
+the amount of files in which a statement kind was deleted or appended. Similar
+to the previous query, we visit all the files labeled as fixing revisions, then
+visit ev- ery node of the previous version of the revision, counting the amount
+of statement kinds of each one of the possible fifteen different ones. We then
+do the same for the later version of the revision, counting the different
+statement kinds.
 
-Finally, we compare the amounts of the previous version, with the new version.
-For each of the revisions, we ask if the amount of statements stays the same for all the statement kinds, except for X kind of statement.
-When the amount of statements is different in the previous version than the latest version for X kind of statement.
-Then we ask if X kinds of statement is greater in the previous version or the latest ver- sion.
-If the amount of appearances of X kind of statement is greater in the previous version than the latest version, and all the remaining fourteen statement kinds have the same amount in the previous than the latest version, then we say that one or more of the statements of kind X were deleted.
-Otherwise, if the latest version has a greater amount of ap- pearances of X kind of statement and the rest have the same amount of appearances in both the previous and the latest version, then we say that one or more statements of kind X were appended or added to the fixing revision.
-
-\subsection{Data Analysis}
-Our queries were ran on the dump of Github of September 2015.
-In these real life projects we found 46,301,429 files being fixed.
-In these files, there is a total of 517,281 statement kinds being replaced, and 511,198 replacing these statements kinds.
-
-We analyzed each of these files looking for statement kinds being either replaced by other kinds, deleted or appended to the file.
-
-We found that the most common Replacer statement kind, meaning the statement kind that most commonly replaces others is the \textbf{If Statement} with 101,366 appearances.
-The least common Replacer, meaning the statement kind which is less likely to replace other statement kinds is the \textbf{Type Declaration Statement} with 447 appearances.
-
-The most common Replacee, which is the most likely statement kind to be replaced by another statement kind is the \textbf{Return Statement} with 111,938 appearances.
-The least common Replacee, which is the least common statement to be replaced by another statement kind is the \textbf{Type Declaration Statement} with 399 appearances.
-
-\subsubsection{Likeliness of replacement}
-This study is directly applicable to automatic software repair.
-Most common tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire} first find a faulty statement using several different fault localization techniques \cite{zach}, and once they have that faulty statement, they apply different kinds of edits to it, usually at random.
-Which makes it equally likely to replace an statement for another without looking at the kinds of statements being replaced.
-
-With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
-By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
-
-For example, if we have a faulty statement that happens to be a For Statement.
-Then we can look up in Table 1 the For Statement Column (6th column).
-If we add all the values in that column, we get 59,870 changes in which a For Statement was replaced by some other kind of statement.
-Then we calculate the percentage of each of the values in the column to see the likeliness of each of the statements to replace it for, and in this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.88\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.73\% of likeliness to replace a For Statement.
-
-\subsubsection{Most common replacements}
-Our results show that the most common replacement is when developers replace a Return statement for an If statement.
-This showed up in 30,489 files in the code database.
-The second most common replacement is an If statement being replaced by a Return statement, which had 28,536 appearances in the code database.
-Third to that, is a Return statement being replaced by a Throw statement.
-
-\includegraphics[scale=0.5]{g1.png}
-
-\subsubsection{Least common replacements}
-On the opposite side of the data, we can see that the least common replacement was an Assert statement replacing a Type Declaration statement.
-This was the only replacement to have zero appearances in our search through the 46,301,429 files being fixed.
-Close to it, as the second least common replacement was replacing a Do statement for a Type Declaration statement, with one appearance in our code database, and on third place, the replacement of a Label being replaced by a Type Declaration Statement had one appearance in our code database.
-
-\includegraphics[scale=0.5]{g2.png}
-
-\section{Related Work}
-A similar study was performed by Dongsun Kim et al.
-\cite{dongsun} in which they look for the most common ways in which programmers patch bugs in software.
-The researchers developed a variation of the tool Genprog \cite{weimer}\cite{claire} with several different templates resembling patters programmers use to patch bugs.
-
-A good complement for this paper is \cite{hao}, where they search additions and deletions in a smaller data set.
-In this paper, we focus on the replacements, which have been left out of the analysis of \cite{hao}.
-
-\section{Conclusions}
-The findings of our study provide a set of useful guidelines for automatic program repair tools with which their search for a patch can be now improved by having the knowledge of how likely it is to replace a faulty statement by the different kinds of statements available.
-
-%\end{document}  % This is where a 'short' article might terminate
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
+Finally, we compare the amounts of the previous version, with the new
+version. For each of the revisions, we ask if the amount of statements stays the
+same for all the statement kinds, except for X kind of statement. When the
+amount of statements is different in the previous version than the latest
+version for X kind of statement. Then we ask if X kinds of statement is greater
+in the previous version or the latest ver- sion. If the amount of appearances of
+X kind of statement is greater in the previous version than the latest version,
+and all the remaining fourteen statement kinds have the same amount in the
+previous than the latest version, then we say that one or more of the statements
+of kind X were deleted. Otherwise, if the latest version has a greater amount of
+ap- pearances of X kind of statement and the rest have the same amount of
+appearances in both the previous and the latest version, then we say that one or
+more statements of kind X were appended or added to the fixing revision.
 
 \section{Results}
+
+\todo{What is the dataset?}
 
@@
 
+\todo{Is there room/call to include any element of Chu Pan's replacement
+  analysis in here?}
+
+\subsection{Data Analysis}
+Our queries were ran on the dump of Github of September 2015. In these real life
+projects we found 46,301,429 files being fixed. In these files, there is a total
+of 517,281 statement kinds being replaced, and 511,198 replacing these
+statements kinds.
+
+We analyzed each of these files looking for statement kinds being either replaced by other kinds, deleted or appended to the file.
+
+We found that the most common Replacer statement kind, meaning the statement
+kind that most commonly replaces others is the \textbf{If Statement} with
+101,366 appearances. The least common Replacer, meaning the statement kind which
+is less likely to replace other statement kinds is the \textbf{Type Declaration
+  Statement} with 447 appearances.
+
+The most common Replacee, which is the most likely statement kind to be replaced
+by another statement kind is the \textbf{Return Statement} with 111,938
+appearances. The least common Replacee, which is the least common statement to
+be replaced by another statement kind is the \textbf{Type Declaration Statement}
+with 399 appearances.
+
+\subsubsection{Likeliness of replacement}
+This study is directly applicable to automatic software repair. Most common
+tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire}
+first find a faulty statement using several different fault localization
+techniques \cite{zach}, and once they have that faulty statement, they apply
+different kinds of edits to it, usually at random. Which makes it equally likely
+to replace an statement for another without looking at the kinds of statements
+being replaced.
+
+With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
+By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
+
+For example, if we have a faulty statement that happens to be a For Statement.
+Then we can look up in Table 1 the For Statement Column (6th column).
+If we add all the values in that column, we get 59,870 changes in which a For Statement was replaced by some other kind of statement.
+Then we calculate the percentage of each of the values in the column to see the likeliness of each of the statements to replace it for, and in this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.88\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.73\% of likeliness to replace a For Statement.
+
+\subsubsection{Most common replacements}
+Our results show that the most common replacement is when developers replace a Return statement for an If statement.
+This showed up in 30,489 files in the code database.
+The second most common replacement is an If statement being replaced by a Return statement, which had 28,536 appearances in the code database.
+Third to that, is a Return statement being replaced by a Throw statement.
+
+\includegraphics[scale=0.5]{g1.png}
+
+\subsubsection{Least common replacements}
+On the opposite side of the data, we can see that the least common replacement was an Assert statement replacing a Type Declaration statement.
+This was the only replacement to have zero appearances in our search through the 46,301,429 files being fixed.
+Close to it, as the second least common replacement was replacing a Do statement for a Type Declaration statement, with one appearance in our code database, and on third place, the replacement of a Label being replaced by a Type Declaration Statement had one appearance in our code database.
+
+\includegraphics[scale=0.5]{g2.png}
+
+\section{Related Work}
+A similar study was performed by Dongsun Kim et al. \cite{dongsun} in which they
+look for the most common ways in which programmers patch bugs in software. The
+researchers developed a variation of the tool Genprog \cite{weimer}\cite{claire}
+with several different templates resembling patters programmers use to patch
+bugs.
+
+A good complement for this paper is \cite{hao}, where they search additions and
+deletions in a smaller data set. In this paper, we focus on the replacements,
+which have been left out of the analysis of \cite{hao}.
+
+\section{Conclusions}
+The findings of our study provide a set of useful guidelines for automatic
+program repair tools with which their search for a patch can be now improved by
+having the knowledge of how likely it is to replace a faulty statement by the
+different kinds of statements available.
+\todo{Expand to include summary of actual conclusions}
+
+%\end{document}  % This is where a 'short' article might terminate
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
+
 \begin{thebibliography}{9}

### 2016-02-16 MSRChallenge2016.tex
add results for PAR

@@
 
+\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
+After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}.
+The result shows that AMC, MSM, COM, CBC, IAO, ANC, and AOB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, and 0.28\% of buggy files.
+We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB.
+If we assume that these patterns never appear together in the dataset, these patterns cover 14.21\% of buggy files.
+Kim et al.
+mentioned that the patterns that they use cover almost 30\% of real patches~\cite{dongsun}.
+Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together.
+Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound.
+This suggests that common bug fixing patterns might not be as common as it appeared to be.
+
+\begin{table}[!htb]
+	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
+	\centering
+	\begin{tabular}{lr} 
+		\hline
+		& \textbf{GitHub}\\
+		\hline
+		\#Buggy Files & 46,301,429 \\ 
+		\#AMP Pattern & 901,083 \\
+		\#MSM Pattern & 783,073 \\
+		\#COM Pattern & 270,128 \\ 
+		\#CBC Pattern & 1,959,377 \\  
+		\#IAO Pattern & 1,308,006 \\  
+		\#ANC Pattern & 1,340,561 \\  
+		\#AOB Pattern & 128,016 \\  
+		\hline
+	\end{tabular}
+\end{table}
+
 \subsection{Data Analysis}

### 2016-02-16 MSRChallenge2016.tex
Fixed the bibliography references

@@
        \affaddr{City}\\
-       \email{clegoues@cs.cmu.edu}       
+       \email{author@edu}       
 }
@@
 \section{Introduction}
-\todo{High level todo, probably for Mau since I think it's his bibtex: please
-  change the bibtex keys to take the form ``lastnameYear'', and then fix the
-  citations.}
-\todo{Please move the bibitems included explicitly in this document into sigproc.bib
-   and use bibtex.}
-\todo{Also, please always include a non-breaking space (a tilde, look at the
-  latex for an example) between a word and the cite tag, and include multiple
-  references on a line in a single citation tag (again, look at the latex for an
-  example; I'll do this once, but would like you to fix the rest when appropriate.}
+
 Automatic bug repair is the branch of computer science that deals with automated
@@
 towards improving the different methodologies to repair bugs in software
-automatically \cite{dongsun,weimer,claire,kai}, one of the
-most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
+automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}, one of the
+most accepted approaches so far has been GenProg~\cite{weimer2009,legoues2012}, an
 evolutionary program repair tool which applies four different kinds of possible
@@
 
-Another well known approach is PAR \cite{dongsun}, which creates 10 different
+Another well known approach is PAR~\cite{kim2013}, which creates 10 different
 repair templates and applies them to the buggy code in an effort to repair
@@
 common they are in the repairs made by programmers in the latest official data
-dump of Github as of September 2015 provided by \cite{robert}.
+dump of Github as of September 2015 provided by~\cite{dyer2013}.
 
@@
 Our methodology is applied to the latest official data dump of Github as of
-September 2015 provided by \cite{robert}. In the following subsections, we first
+September 2015 provided by~\cite{dyer2013}. In the following subsections, we first
 describe data source and objective of our study. We then describe how we detect
@@
 \subsection{Data Source and Research Objective}
-We used the Boa platform \cite{robert} to be able to query the Github repository
+We used the Boa platform~\cite{dyer2013} to be able to query the Github repository
 looking for patterns that humans use to patch errors in the their code. Our main
@@
 The bug fixing patterns that we analyze in this work are adopted from Kim et
-al. paper~\cite{dongsun}. The following is the description of each considered
+al. paper~\cite{kim2013}. The following is the description of each considered
 pattern. 
@@
 To analyze bug fixing patterns, we utilizes Boa's language
-infrastructure~\cite{robert}. It contains a large number of dataset and provide
+infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
 a domain specific language to perform analysis on source code. Despite this
@@
 The replace query is a query in which first we set the project that we are going
-to use, which is the Github dump of September 2015 provided by \cite{robert}.
+to use, which is the Github dump of September 2015 provided by~\cite{dyer2013}.
 
@@
 Kim et al.
-mentioned that the patterns that they use cover almost 30\% of real patches~\cite{dongsun}.
+mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}.
 Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together.
@@
 This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire}
+tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
 first find a faulty statement using several different fault localization
-techniques \cite{zach}, and once they have that faulty statement, they apply
+techniques~\cite{fry2010}, and once they have that faulty statement, they apply
 different kinds of edits to it, usually at random. Which makes it equally likely
@@
 \section{Related Work}
-A similar study was performed by Dongsun Kim et al. \cite{dongsun} in which they
+A similar study was performed by Dongsun Kim et al.~\cite{kim2013} in which they
 look for the most common ways in which programmers patch bugs in software. The
-researchers developed a variation of the tool Genprog \cite{weimer}\cite{claire}
+researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
 with several different templates resembling patters programmers use to patch
@@
 
-A good complement for this paper is \cite{hao}, where they search additions and
+A good complement for this paper is~\cite{zhong2015}, where they search additions and
 deletions in a smaller data set. In this paper, we focus on the replacements,
-which have been left out of the analysis of \cite{hao}.
+which have been left out of the analysis of~\cite{zhong2015}.
 
@@
 
-\begin{thebibliography}{9}
-
-\bibitem{robert}
-  Robert Dyer et al.,
-  \emph{Boa: A Language and Infrastructure for Analyzing Ultra-Large-Scale Software Repositories},
-35th International Conference on Software Engineering; ICSE 2013, San Francisco CA, USA
-
-\bibitem{hao}
-Hao Zhong, Zhendong Su
-\emph{An Empirical Study on Real Bug Fixes},
-In Proceedings of ICSE 2015, Firenze, Italy, May 16-24, 2015.
-
-\bibitem{kai}
-Kai Pan et al.
-\emph{Towards an understanding of bug fix patterns},
-Journal
-Empirical Software Engineering
-Volume 14 Issue 3, June 2009 
-Pages 286 - 315
-
-\bibitem{dongsun}
-Dongsun Kim et al.
-\emph{Automatic patch generation learned from human-written patches},
-Proceeding
-ICSE '13 Proceedings of the 2013 International Conference on Software Engineering
-
-\bibitem{zach}
-Zachary P.Fry and Westley Weimer
-\emph{A human study of fault localization accuracy},
-ICSM '10 Proceedings of the 2010 IEEE International Conference on Software Maintenance
-
-\bibitem{claire}
-Claire Le Goues, ThanhVu Nguyen, Stephanie Forrest, Westley Weimer
-\emph{GenProg: A Generic Method for Automated Software Repair.} 
-IEEE Trans. Software Engineering 38(1): 54-72 (January/February 2012)
-
-\bibitem{weimer}
-Westley Weimer, ThanVu Nguyen, Claire Le Goues, Stephanie Forrest
-\emph{Automatically Finding Patches Using Genetic Programming.}
-International Conference on Software Engineering (ICSE) 2009: 364-374
-
-\end{thebibliography}
-
 %\balancecolumns % GM June 2007

### 2016-02-17 MSRChallenge2016.tex
RElocating related work
Several changes
MSR paper
Mauricio Soto   9:02 PM
To: clegoues@cs.cmu.edu, chupanw@cs.cmu.edu, fthung@andrew.cmu.edu,
Mauricio Soto

- I changed the references to bibtex.
- I rewrote the intro to make it more high level
- I relocated the Related Work to be section 2, because that's what we
talked in the meeting, though I'm not super convinced it is working for
us over there.
- I removed my Append/Delete query section because that is not actually
the one that we ran. We ran Pan's. Pan: Maybe you can put something in
the methodology regarding the query you ran and your re

@@
        \affaddr{City}\\
-       \email{author@edu}       
+       \email{author@institution.edu}       
 }
@@
 \begin{abstract}
-\textbf{
+
 With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered.
 We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.
-}
 
-\textbf{
 We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other.
@@
 These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
-}
 
@@
 towards improving the different methodologies to repair bugs in software
-automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}, one of the
-most accepted approaches so far has been GenProg~\cite{weimer2009,legoues2012}, an
-evolutionary program repair tool which applies four different kinds of possible
-edits to code in order to find a patch for a given bug. These changes are the
-following: Delete, Replace, Swap and Append.
-
-\todo{We need to integrate the PAR and operator discussion a bit better.  Let's
-  take it up a level of abstraction: there is initial work in applying these
-  techniques to Java that propose a number of mutation operators, and we study
-  the degree to which they apply in practice and make recommendations based on
-  human-provided repairs.  Doing so is a good idea, because patches inspired by
-  human-created repairs are empirically demonstrated to be rated more highly by
-  developers (cite PAR).}
-\todo{I also thought we were doing Par first, and then the replacement studies?}
-
-Another well known approach is PAR~\cite{kim2013}, which creates 10 different
-repair templates and applies them to the buggy code in an effort to repair
+automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}.
+A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
 it. In this paper we have taken 7 out of the 10 PAR templates and tested how
@@
 
-Our research aims to provide guidelines to improve three out of four of these
-possible changes: Delete, Replace and Append. It will provide the data necessary
-for this tool and other approaches to have a guide on what is the way in which
-human programmers change their code when coding a fix for a bug. This way it
-will make it more likely for automatic error repair approaches to succeed in
+Some other well known approaches~\cite{weimer2009,legoues2012} have been based on the idea of applying a number of mutation operators to the buggy code in order to find a patch.
+In this opportunity, we study the degree to which these mutation operators apply in practice, taking as a subject of study several million human-made bug fixes from Github.
+This way it will make it more likely for automatic error repair approaches to succeed in
 finding a patch for a particular error, and also, to provide automatic error
-repair software with heuristics to make the patches more human-like and
-therefore more readable and maintainable by human developers.
+repair software with guidelines to make the patches more human-like and
+therefore more readable and maintainable by human developers, as studied empirically by~\cite{kim2013}.
 
-In this article we study the frequency with which human programmers replace,
-delete and append different statements to their source code in order to fix a
-bug.
+\section{Related Work}
+We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
+researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
+with several different templates resembling patters programmers use to patch
+bugs, and then perform an empirical study to evaluate which patches do human programmers prefer.
+
+A good complement for this paper is~\cite{zhong2015}, where they search additions and
+deletions in a smaller data set. In this paper, we focus on the replacements,
+which have been left out of the analysis of~\cite{zhong2015}.
 
@@
 bug-fixing patterns.
-
-\begin{table*}
-	\centering
-	\caption{Amount of appearances per replace kind}
-	\resizebox{\textwidth}{100pt}{
-		\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
-			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
-			\\ \hline
-			\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
-			\\ \hline
-			\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
-			\\ \hline
-			\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
-			\\   \hline
-			\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
-			\\ \hline
-			\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
-			\\ \hline
-			\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
-			\\ \hline
-			\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
-			\\ \hline
-			\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
-			\\ \hline
-			\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
-			\\ \hline
-			\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
-			\\ \hline
-			\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
-			\\ \hline
-			\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
-			\\ \hline
-			\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
-			\\ \hline
-			\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
-			\\ \hline
-			\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
-			\\ \hline
-		\end{tabular}
-	}
-\end{table*}
 
@@
 
+\begin{table*}
+	\centering
+	\resizebox{\textwidth}{100pt}{
+		\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
+			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
+			\\ \hline
+			\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
+			\\ \hline
+			\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
+			\\ \hline
+			\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
+			\\   \hline
+			\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
+			\\ \hline
+			\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
+			\\ \hline
+			\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
+			\\ \hline
+			\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
+			\\ \hline
+			\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
+			\\ \hline
+			\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
+			\\ \hline
+			\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
+			\\ \hline
+			\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
+			\\ \hline
+			\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
+			\\ \hline
+			\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
+			\\ \hline
+			\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
+			\\ \hline
+			\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
+			\\ \hline
+		\end{tabular}
+		}
+		\caption{Amount of appearances per replace kind}
+\end{table*}
+
 \subsection{Replace Query}
-The replace query is a query in which first we set the project that we are going
-to use, which is the Github dump of September 2015 provided by~\cite{dyer2013}.
+The replace query we designed, is a query in which we create a visitor to traverse all the fixing revisions in this repository~\cite{dyer2013}. Therefore we are analyzing only files
+that were already committed and are now being reviewed to fix an error.
 
-We then create a visitor to traverse all the nodes of this repository. First
-thing the visitor does is to ask weather the node is a Revision, and if it is,
-then it asks if it is a fixing revision. Therefore we are analyzing only files
-that were already committed and are now being reviewed to fix an error. We use
-Boa's infrastructure to do this by visiting the node they label as "Revision"
-and then calling the function defined by Boa "isfixingrevision()".
-
-A replacement needs two statements, one that is deleted and another one that is
-inserted.  We then go through all the files that have been changed in this data
-set asking for two conditions: it must be a fixing revision and there must have
-been a previous version of this file before. If these conditions are met then we
-initialize two counters: one for the first statement we are analyzing (the one
-that was deleted), and another one for the second statement we are analyzing
-(the one that was inserted).
-
-At this point we visit each statement in the previous state of that changed
+We visit each statement in the previous state of that changed
 file, before the change was applied and we count the amount of appearances of
@@
 
-We need to test this with all the possible combinations of two different
-statement types since we want to know what is the probability of an specific
-statement to be replaced by another specific statement. For example, we want to
-know how often does a For loop gets replaced by a While loop in a successful
-human written patch, or how often does a Break statement gets replaced by a
-Continue statement in a successful human written patch.
-
-Because of this we have created Table 1 which records the amount of replaces happening from one kind of statement to another.
-It is a matrix of fifteen by fifteen slots that describes which statements are being replaced by which other.
-
+\todo{Note to self (Mau): Change this paragraph to explain the table depending on how it is presented}
 The numbers in the slots represent the amount of files in which that replacement took place.
@@
 
-It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the statement kind, since it is counting the amount of appearances of each statement kind.
-So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file is going to remain the same
-
-\subsection{Delete/Append Query}
-The Delete/Append Query is similar to the Replace Query with some variations to
-count for the amount of times that a file was changed and a particular statement
-kind was ei- ther deleted or append, and the rest of the statement kinds
-remained the same.
-
-We created a Boa file in which first we create an output variable to count all
-the amount of files in which a statement kind was deleted or appended. Similar
-to the previous query, we visit all the files labeled as fixing revisions, then
-visit ev- ery node of the previous version of the revision, counting the amount
-of statement kinds of each one of the possible fifteen different ones. We then
-do the same for the later version of the revision, counting the different
-statement kinds.
-
-Finally, we compare the amounts of the previous version, with the new
-version. For each of the revisions, we ask if the amount of statements stays the
-same for all the statement kinds, except for X kind of statement. When the
-amount of statements is different in the previous version than the latest
-version for X kind of statement. Then we ask if X kinds of statement is greater
-in the previous version or the latest ver- sion. If the amount of appearances of
-X kind of statement is greater in the previous version than the latest version,
-and all the remaining fourteen statement kinds have the same amount in the
-previous than the latest version, then we say that one or more of the statements
-of kind X were deleted. Otherwise, if the latest version has a greater amount of
-ap- pearances of X kind of statement and the rest have the same amount of
-appearances in both the previous and the latest version, then we say that one or
-more statements of kind X were appended or added to the fixing revision.
+It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the same statement kind, since it is counting the amount of appearances of each statement kind.
+So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file will remain the same.
 
@@
 
+\todo{Note to self (Mau): Change this depending on the table}
 With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
@@
 
+\begin{figure}[!ht]
+  \centering
       \includegraphics[scale=0.5]{g1.png}
+  \caption{Most common replacements}
+\end{figure}
 
@@
 
+\begin{figure}
+  \centering
 \includegraphics[scale=0.5]{g2.png}
-
-\section{Related Work}
-A similar study was performed by Dongsun Kim et al.~\cite{kim2013} in which they
-look for the most common ways in which programmers patch bugs in software. The
-researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
-with several different templates resembling patters programmers use to patch
-bugs.
-
-A good complement for this paper is~\cite{zhong2015}, where they search additions and
-deletions in a smaller data set. In this paper, we focus on the replacements,
-which have been left out of the analysis of~\cite{zhong2015}.
+\caption{Least common replacements}
+\end{figure}
 

### 2016-02-17 MSRChallenge2016.tex
update PAR method and result

@@
 	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
+	\item {\bf Adding a collection out of bound checker (COB)}\\
+	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
+	{\bf Description:} This pattern inserts a condition to check that a collection index is within bound before it is used.
 \end{enumerate}
 
-To analyze bug fixing patterns, we utilizes Boa's language
+The above patterns only cover 8 out of 10 bug fixing patterns in PAR.
+The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope.
+Pattern (1) cannot be analyzed because Boa does not support {\em instanceof} expression.
+Similarly, pattern (2) requires us to track scope between pre-fix and post-fix version, which is not supported by Boa.
+Implementing them ourselves might be possible, but it might require too much effort than necessary.
+Investigating 8 out of 10 patterns should give us a good idea on how common the patterns actually are.
+
+As mentioned before, we analyze bug fixing patterns by utilizing Boa's language
 infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
@@
   version, we consider that AOB pattern is found.
+
+\item {\bf COB Pattern}\\
+To detect COB pattern, we count the number of if conditional expression that
+contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
+post-fix version. If there are count differences between pre-fix and post-fix
+version, we consider that COB pattern is found.
 
@@
 After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}.
-The result shows that AMC, MSM, COM, CBC, IAO, ANC, and AOB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, and 0.28\% of buggy files.
+The result shows that AMC, MSM, COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files.
 We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB.
-If we assume that these patterns never appear together in the dataset, these patterns cover 14.21\% of buggy files.
+If we assume that these patterns never appear together in the dataset, these patterns cover 14.78\% of buggy files.
 Kim et al.
 mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}.
-Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together.
+Although we only detect 8 out of 10 bug fixing patterns, it is hard to believe that the remaining two patterns cover 15\% of buggy files, especially 14.78\% is a number we get when we assume that the patterns that we detect never appear together.
 Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound.
@@
 		\#AOB Pattern & 128,016 \\  
+		\#COB Pattern & 262,915 \\   
 		\hline

### 2016-02-17 MSRChallenge2016.tex
Revise results section and threats to validity
* Slightly changed the story in results section
* Added threats to validity section
* Integrate CPW's replacement results
* Added some todos (mostly for CPW)
* Fixed a few typos
* Missing conclusion

@@
 % 2nd. author
-\alignauthor Chu Pan Wong   \\
+\alignauthor Chu-Pan Wong   \\
        \affaddr{Carnegie Mellon University}\\
@@
 researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
-with several different templates resembling patters programmers use to patch
-bugs, and then perform an empirical study to evaluate which patches do human programmers prefer.
+with several different templates resembling patterns programmers use to patch
+bugs, and then performed an empirical study to evaluate which patches do human programmers prefer.
 
@@
 
-The above patterns only cover 8 out of 10 bug fixing patterns in PAR.
+The above patterns only cover 8 \todo{inconsistent with intro} out of 10 bug fixing patterns in PAR.
 The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope.
@@
   custom expression as OTHER. This is due to inexistence of function that can
-  print Abstract Syntax Tree (AST) back to source code. we discard method
+  print Abstract Syntax Tree (AST) back to source code in Boa. We discard method
   signatures that appear both in pre-fix and post-fix version. We then find
@@
 
-\todo{What is the dataset?}
+% (This is the old version)
+% This section investigates how do developer fix bugs from three different
+% perspectives. To begin with, we show some characteristics of real-world bug
+% fixes.  Afterwards, we look deeper to find out what kinds of statements are
+% usually added, modified or deleted by human developers to fix bugs. Lastly, we
+% show how common PAR's fixing templates are in our dataset.
 
-This section investigates how do developer fix bugs from three different
-perspectives. To begin with, we show some characteristics of real-world bug
-fixes.  Afterwards, we look deeper to find out what kinds of statements are
-usually added, modified or deleted by human developers to fix bugs. Lastly, we
-show how common PAR's fixing templates are in our dataset.
+This section shows our analysis results. To begin with, we discuss the dataset
+we are using, and some characteristics of real-world bug fixes. Afterwards, we
+provide insights for two main categories of automatic program repair approaches.
+On the one hand, many approaches \todo{citation} rely on mutation operators to
+modify the source code, but we have limited knowledge about what kinds of
+statements are usually modified. Our analysis results will fill in this
+knowledge gap. On the other hand, some automatic program repair approaches
+\todo{citation} search for specific patterns and modify source code according to
+predefined templates. Our results provide evidence of how common those
+patterns are in practice.
 
-\subsection{Characteristics}
+\subsection{Dataset and Characteristics}
 
-This subsection shows a bird's-eye view of real-world bug fixes at
-ultra-large-scale. We did our analysis on the \emph{2015 September/Github}
-dataset on Boa. This dataset includes $7,830,023$ Java projects with
-$23,229,406$ revisions. Among all the revisions, $4,590,679$ revisions are
-identified by Boa as bug fixing revisions. Our analysis in this subsection
-focuses on these bug fixing revisions. We hope that this population
-is big enough to reflect the bug fixing practice.
+We did our analysis on the \emph{2015 September/Github} dataset on Boa. This
+dataset includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
+all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
+revisions. We hope that this population is big enough to reflect the bug fixing
+practice.
 
+The rest of this subsection shows some characteristics of real-world bug fixes.
 To begin with, we are interested in:
@@
 
-To answer this question, we identified all the bug fixing revisions in our
-dataset and count the number of changed files. In total, $52,052,571$ files got
-changed. Thus, on average each bug fixing revision changes 11.3 files.  This
-number is surprisingly high because most automatic program repair techniques
-assume that bugs are local in most cases. There could be several reasons behind
-this number. It could be the case that other software artifacts (e.g.
-documentation) are updated after bug fixing. It could also be the case that bug
-fixing commit also contains changes that are not related to fixing bug (e.g. new
-features, refactoring). To better understand why so many files are changed, we
-continue to ask:
+To answer this question, we identify all the bug fixing revisions in our dataset
+and count the number of changed files. A file was changed if (1) it was a new
+file; (2) or it was modified; (3) or it was deleted. In total, $52,052,571$
+files got changed. Thus, on average each bug fixing revision changes 11.3 files.
+This number is surprisingly high because most automatic program repair
+techniques assume that bugs are local in most cases. There could be several
+reasons behind this number. It could be the case that other software artifacts
+(e.g.  documentation) are updated after bug fixing. It could also be the case
+that bug fixing commit also contains changes that are not related to fixing bug
+(e.g. refactoring, adding new features by creating new files). To better
+understand why so many files are changed, we continue to ask:
 
@@
 In Boa, each changed file is represented by a \emph{ChangedFile} node, and it
-has a field called \emph{FileKind}, describing the type of each file.
+has a field called \emph{FileKind}, describing the type of each file. As
+mentioned earlier, a \emph{ChangedFile} could be either a new file or an
+existing file (if the bug fixing revision modified or deleted the file).
 Table~\ref{tbl:fileType} shows the file types that Boa could identify. To answer
@@
   XML & 6,818,299 & 1.49 \\ \hline
-  UNKNOWN & 23426568 & 5.10 \\ \hline
+  UNKNOWN & 23,426,568 & 5.10 \\ \hline
   \end{tabular}
@@
 This research question is interesting because most automatic program repair
-approaches could not create new classes/methods/fields/variables to fix bugs.
+approaches often do not create new classes/methods/fields/variables to fix bugs.
 Most approaches guess and synthesize the patches based on existing source code.
@@
 
-\todo{Is there room/call to include any element of Chu Pan's replacement
-  analysis in here?}
+% \todo{Is there room/call to include any element of Chu Pan's replacement
+%   analysis in here?}
 
-\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
-After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}.
-The result shows that AMC, MSM, COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files.
-We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB.
-If we assume that these patterns never appear together in the dataset, these patterns cover 14.78\% of buggy files.
-Kim et al.
-mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}.
-Although we only detect 8 out of 10 bug fixing patterns, it is hard to believe that the remaining two patterns cover 15\% of buggy files, especially 14.78\% is a number we get when we assume that the patterns that we detect never appear together.
-Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound.
-This suggests that common bug fixing patterns might not be as common as it appeared to be.
+\subsection{What changes are common in real-world bug fixes?}
 
-\begin{table}[!htb]
-	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
-	\centering
-	\begin{tabular}{lr} 
-		\hline
-		& \textbf{GitHub}\\
-		\hline
-		\#Buggy Files & 46,301,429 \\ 
-		\#AMP Pattern & 901,083 \\
-		\#MSM Pattern & 783,073 \\
-		\#COM Pattern & 270,128 \\ 
-		\#CBC Pattern & 1,959,377 \\  
-		\#IAO Pattern & 1,308,006 \\  
-		\#ANC Pattern & 1,340,561 \\  
-		\#AOB Pattern & 128,016 \\  
-		\#COB Pattern & 262,915 \\   
-		\hline
-	\end{tabular}
-\end{table}
+Most automatic program repair approaches mutate source code using predefined
+mutation operators, which represent different ways of modifying source code. In
+order to generate patches that make more sense to human developers, it would be
+beneficial to first investigate how developers mutate source code to fix bugs.
 
-\subsection{Data Analysis}
-Our queries were ran on the dump of Github of September 2015. In these real life
-projects we found 46,301,429 files being fixed. In these files, there is a total
-of 517,281 statement kinds being replaced, and 511,198 replacing these
+For each bug fixing revision $r$ and each statement kind $k$, we count how many
+statements of kind $k$ are there in revision $r$ and $r-1$ ($r-1$ means the
+revision before revision $r$), and then compare the two numbers. For example, if
+the number of if statements in revision $r$ is more than the number in revision
+$r-1$, we say bug fixing revision $r$ introduce new if statements. Note that
+``introducing new if statements'' does not necessarily mean human developers
+introduce them to fix bugs. However, our hope is that this analysis could still
+provide us some hints, given the large number of bug fixing revisions we are
+analyzing.
+
+\begin{figure*}[!t] \centering
+	\includegraphics[width=0.95\textwidth]{StmtType} \caption{For each kind
+	of statement, how many bug fixing revisions add/delete statements of the
+same kind?} \label{fig:StmtType} \end{figure*}
+
+From Figure~\ref{fig:StmtType} \todo{fix the small fonts in this graph}, we can
+see that expression, if, return, for and try catch statements are added most
+often. On the other hand, the same types of statements are also deleted most
+often. This finding indicates that most bugs were fixed by changing the control
+flow of the program using if, return, for, while, and try catch statements.
+
+For each bug fixing revision, the results discussed above consider both newly
+added files and existing files. Since most automatic program repair approaches
+do not generate new files to fix bugs, the rest of this section only considers
+files that were already in the repositories when developers fixed bugs. Our
+analysis shows that there are 46,301,429 of them. In these files, there is a
+total of 517,281 statement kinds being replaced, and 511,198 replacing these
 statements kinds.
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[!t]
   \centering
@@
 \end{figure}
+
+\subsection{How common are the fixing templates of PAR?}\label{sec:freqfixpattern}
+After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}.
+The result shows that AMC, MSM, COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files.
+We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB.
+If we assume that these patterns never appear together in the dataset, these patterns cover 14.78\% of buggy files.
+Kim et al.
+mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}.
+Although we only detect 8 out of 10 bug fixing patterns, it is hard to believe that the remaining two patterns cover 15\% of buggy files, especially 14.78\% is a number we get when we assume that the patterns that we detect never appear together.
+Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound.
+This suggests that common bug fixing patterns might not be as common as it appeared to be.
+
+\begin{table}[!htb]
+	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
+	\centering
+	\begin{tabular}{lr} 
+		\hline
+		& \textbf{GitHub}\\
+		\hline
+		\#Buggy Files & 46,301,429 \\ 
+		\#AMP Pattern & 901,083 \\
+		\#MSM Pattern & 783,073 \\
+		\#COM Pattern & 270,128 \\ 
+		\#CBC Pattern & 1,959,377 \\  
+		\#IAO Pattern & 1,308,006 \\  
+		\#ANC Pattern & 1,340,561 \\  
+		\#AOB Pattern & 128,016 \\  
+		\#COB Pattern & 262,915 \\   
+		\hline
+	\end{tabular}
+\end{table}
+
+\section{Threats to Validity}
+
+Since we are using a DSL provided by Boa to implement our analysis, the
+correctness of our analysis depends on our programs as well as Boa itself. To
+prevent errors from our side, we open source our implementation on
+Github~\footnote{\url{https://github.com/}}.\todo{update
+this}
+
+Some threats to our study are due to the limitation of Boa. For example, we rely
+on Boa to identify bug fixing revisions, but it is unclear whether those
+identified revisions are actually related to bug fixing. Chances are that there
+exist some other bug fixing revisions, but Boa could not identify them. It is
+also possible that bug fixing revisions identified by Boa actually include other
+code changes, such as implementing new features, refactoring the code base.
+After all, identifying bug fixing revisions from revision history is still an
+open problem. Another big limitation of Boa is that there is no easy to get a
+precise statement-level diff between two revisions. Thus, our template matching
+and analysis of code changes (by counting each statement kind) could be
+inaccurate. However, our results should provide upper bounds for the questions
+we investigated.
 
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+\todo{Fix the BibTeX}
+
 \bibliographystyle{abbrv}

### 2016-02-17 MSRChallenge2016.tex
Removed graphs
Several changes
Mixed Related Work and Intro
Explained what the charts do, and removed the pie charts
Fixed the InProceedings thing in the Bibtex
Transposed the table
Put the java table instead of the All Languages table
Modified the parts of the article, talking about the table
Rephrased the abstract

@@
 
-\title{A deeper look into bug fixes: patterns, replacements, deletions, and additions}
+\title{A deeper look into bug fixes: Patterns, replacements, deletions, and additions}
 
@@
 With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered.
-We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.
+We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements, additions and deletions made to these files from real life projects in Github.
 
-We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other.
-We also analyzed, once you have a statement that you want to replace (a faulty statement), what are the most likely statements to replace it for.
-These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
+We found valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we also analyzed what are the most likely statements to replace others.
+
+This information will help automatic program repair tools to be more likely to find a patch and also to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
 
@@
 
-\section{Related Work}
 We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
@@
 
-A good complement for this paper is~\cite{zhong2015}, where they search additions and
-deletions in a smaller data set. In this paper, we focus on the replacements,
-which have been left out of the analysis of~\cite{zhong2015}.
+Since automatic program repair has been well studied in the programming language C.
+We are now focusing on the programming language Java, and analyzing the behavior of programmers in this particular language.
+
+A good complement for this paper is~\cite{zhong2015}, where they look for additions and
+deletions in a smaller data set. In this paper, we focus more on the replacements,
+which have been left out of the analysis of~\cite{zhong2015}, and expand their results of the deletions and additions in a broader dataset~\cite{dyer2013}.
 
@@
 	\resizebox{\textwidth}{100pt}{
-		\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
+		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
 			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
 			\\ \hline
-			\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
+
+\texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
 \\ \hline
-			\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
+\texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
 \\ \hline
-			\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
+\texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
 \\   \hline
-			\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
+\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
 \\ \hline
-			\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
+\texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
 \\ \hline
-			\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
+\texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
 \\ \hline
-			\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
+\texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
 \\ \hline
-			\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
+\texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
 \\ \hline
-			\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
+\texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
 \\ \hline
-			\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
+\texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
 \\ \hline
-			\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
+\texttt{Synchronized} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
 \\ \hline
-			\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
+\texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
 \\ \hline
-			\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
+\texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
 \\ \hline
-			\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
+\texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
 \\ \hline
-			\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
+\texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
 			\\ \hline
@@
 		}
-		\caption{Amount of appearances per replace kind}
+		\caption{Likelyness to replace the statement in the first column for the statement in the top row, in Java}
 \end{table*}
@@
 
-\todo{Note to self (Mau): Change this paragraph to explain the table depending on how it is presented}
-The numbers in the slots represent the amount of files in which that replacement took place.
-In the first column we have the list of statements that are being replaced, and on the top row we have the list of statements for which that statement was replaced for.
-For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column), we have a 32, which means that from the 46,301,429 files categorized by Boa as fixing revisions in Github in the month of September 2015, only 32 of them replaced a DoStatement for an AssertStatement.
+The numbers in the slots of Table 1, represent the percentage rate at which the elements of the leftmost column were replaced by the elements of the top row.
+In the first column we have the list of statements that are being replaced (faulty statements that were removed), and on the top row we have the list of statements for which that statement was replaced for (the new statement put instead).
+For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column) of the data, we have a 0.81, which means that if we take all the instances in which a Do statement was replaced by something else, the amount of times that it was replaced by an Assert statement, represent a 0.81% of the times.
 
@@
 
-\todo{Note to self (Mau): Change this depending on the table}
 With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
-By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
+By taking a look at the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
 
-For example, if we have a faulty statement that happens to be a For Statement.
-Then we can look up in Table 1 the For Statement Column (6th column).
-If we add all the values in that column, we get 59,870 changes in which a For Statement was replaced by some other kind of statement.
-Then we calculate the percentage of each of the values in the column to see the likeliness of each of the statements to replace it for, and in this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.88\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.73\% of likeliness to replace a For Statement.
+For example, if we are fixing a Java program, and we have a faulty statement that happens to be a For Statement.
+Then we can look up in Table 1 the For Statement Row (6th row), and take a look at the probability of that statement to be replaced by other kinds of statement.
+In this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.89\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.79\% of likeliness to replace a For Statement.
+This way we know that it is more likely for a programmer to replace a For Statement for those three different kinds of statements and this provides guidelines to the automatic bug repair approaches to consider this on their effort to find a patch.
 
 \subsubsection{Most common replacements}
-Our results show that the most common replacement is when developers replace a Return statement for an If statement.
+Our results show that the most common replacement is when developers remove a Return statement and insert an If statement.
 This showed up in 30,489 files in the code database.
-The second most common replacement is an If statement being replaced by a Return statement, which had 28,536 appearances in the code database.
-Third to that, is a Return statement being replaced by a Throw statement.
-
-\begin{figure}[!t]
-  \centering
-      \includegraphics[scale=0.5]{g1.png}
-  \caption{Most common replacements}
-\end{figure}
+The second most common replacement is removing an If statement and insert a Return statement instead, which had 28,536 appearances in the code database.
+Third to that, is to remove a Return statement and insert a Throw statement.
 
@@
 This was the only replacement to have zero appearances in our search through the 46,301,429 files being fixed.
-Close to it, as the second least common replacement was replacing a Do statement for a Type Declaration statement, with one appearance in our code database, and on third place, the replacement of a Label being replaced by a Type Declaration Statement had one appearance in our code database.
-
-\begin{figure}[!t]
-  \centering
-\includegraphics[scale=0.5]{g2.png}
-\caption{Least common replacements}
-\end{figure}
+Close to it, as the second least common replacement was removing a Do statement and insert a Type Declaration statement, with one appearance in our code database, and on third place, removing a Label and insert a Type Declaration Statement had one appearance in our code database.
 
@@
 
-\todo{Fix the BibTeX}
-
 \bibliographystyle{abbrv}

### 2016-02-17 MSRChallenge2016.tex
update author info
Minor details

@@
 \alignauthor Ferdian Thung\\
-       \affaddr{University}\\
-       \affaddr{City}\\
-       \email{email@domain.com}
+       \affaddr{Singapore Management University}\\
+       \affaddr{Singapore}\\
+       \email{ferdiant.2013@smu.edu.sg}
 % 2nd. author
@@
 David Lo\\
-       \affaddr{University}\\
-       \affaddr{City}\\
-       \email{author@institution.edu}       
+\affaddr{Singapore Management University}\\
+\affaddr{Singapore}\\
+\email{davidlo@smu.edu.sg}       
 }
@@
 A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
-it. In this paper we have taken 7 out of the 10 PAR templates and tested how
+it. In this paper we have taken 8 out of the 10 PAR templates and tested how
 common they are in the repairs made by programmers in the latest official data
@@
 
-The above patterns only cover 8 \todo{inconsistent with intro} out of 10 bug fixing patterns in PAR.
+The above patterns only cover 8 out of 10 bug fixing patterns in PAR.
 The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope.
@@
 		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
-			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
+			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
 			\\ \hline
@@
 \\ \hline
-\texttt{Synchronized} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
+\texttt{Synch} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
 \\ \hline
@@
 provide insights for two main categories of automatic program repair approaches.
-On the one hand, many approaches \todo{citation} rely on mutation operators to
-modify the source code, but we have limited knowledge about what kinds of
+On the one hand, some approaches rely on mutation operators to
+modify the source code~\cite{legoues2012,weimer2009}, but we have limited knowledge about what kinds of
 statements are usually modified. Our analysis results will fill in this
-knowledge gap. On the other hand, some automatic program repair approaches
-\todo{citation} search for specific patterns and modify source code according to
+knowledge gap. On the other hand, some automatic program repair approaches~\cite{kim2013} search for specific patterns and modify source code according to
 predefined templates. Our results provide evidence of how common those

### 2016-02-17 MSRChallenge2016.tex
Update email and table 3

--- 2016-02-17 MSRChallenge2016.tex
@@
        \affaddr{Pittsburgh, PA}\\
-       \email{email@domain.com}       
+       \email{chupanw@cs.cmu.edu}       
 \and  % use '\and' if you need 'another row' of author names
@@
   Introducing & Total Number & Average \\ \hline \hline
-  Class & 729201 & 0.16 \\ \hline
-  Methods & 3186867 & 0.69 \\ \hline
-  Fields & 6076646 & 1.32 \\ \hline
-  Variables & 924259 & 0.2 \\ \hline
+  Class & 729,201 & 0.16 \\ \hline
+  Methods & 3,186,867 & 0.69 \\ \hline
+  Fields & 6,076,646 & 1.32 \\ \hline
+  Variables & 924,259 & 0.2 \\ \hline
   \end{tabular}
-  \caption{File Types of Changed Files}
+  \caption{Introducing new classes, methods, fields, variables to fix bugs}
   \label{tbl:new}

### 2016-02-17 MSRChallenge2016.tex
Moved some text from sec.5 to sec.1

@@
 
-Automatic bug repair is the branch of computer science that deals with automated
-ways to repair errors in software. There have been several approaches taken
-towards improving the different methodologies to repair bugs in software
-automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}.
-A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
-it. In this paper we have taken 8 out of the 10 PAR templates and tested how
-common they are in the repairs made by programmers in the latest official data
-dump of Github as of September 2015 provided by~\cite{dyer2013}.
+Automatic bug repair is the branch of computer science that deals with
+automated ways to repair errors in software. There have been several approaches
+taken towards improving the different methodologies to repair bugs in software
+automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. Roughly speaking,
+there are two main categories of approaches.
 
-Some other well known approaches~\cite{weimer2009,legoues2012} have been based on the idea of applying a number of mutation operators to the buggy code in order to find a patch.
-In this opportunity, we study the degree to which these mutation operators apply in practice, taking as a subject of study several million human-made bug fixes from Github.
-This way it will make it more likely for automatic error repair approaches to succeed in
-finding a patch for a particular error, and also, to provide automatic error
-repair software with guidelines to make the patches more human-like and
-therefore more readable and maintainable by human developers, as studied empirically by~\cite{kim2013}.
+On the one hand, some approaches rely on mutation operators to modify the source
+code~\cite{legoues2012,weimer2009}. However, we have limited knowledge about
+what kinds of statements are usually modified. In this opportunity, we study the
+degree to which these mutation operators apply in practice, taking as a subject
+of study several million human-made bug fixes from Github. This way it will make
+it more likely for automatic error repair approaches to succeed in finding a
+patch for a particular error, and also, to provide automatic error repair
+software with guidelines to make the patches more human-like and therefore more
+readable and maintainable by human developers, as studied empirically
+by~\cite{kim2013}.
 
-We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
-researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
-with several different templates resembling patterns programmers use to patch
-bugs, and then performed an empirical study to evaluate which patches do human programmers prefer.
+On the other hand, some approaches~\cite{kim2013} search for specific patterns
+and modify source code according to predefined templates. A well known approach
+is PAR~\cite{kim2013}, which creates 10 different repair templates and applies
+them to the buggy code in an effort to repair it. In this paper we have taken 8
+out of the 10 PAR templates and tested how common they are in the repairs made
+by programmers in the latest official data dump of Github as of September 2015
+provided by~\cite{dyer2013}.  Our results provide evidence of how common those
+patterns are in practice. We take as reference the study performed by Dongsun
+Kim et al.~\cite{kim2013} in which they look for the most common ways in which
+programmers patch bugs in software. The researchers developed a variation of the
+tool Genprog~\cite{weimer2009,legoues2012} with several different templates
+resembling patterns programmers use to patch bugs, and then performed an
+empirical study to evaluate which patches do human programmers prefer.
 
-Since automatic program repair has been well studied in the programming language C.
-We are now focusing on the programming language Java, and analyzing the behavior of programmers in this particular language.
+Although automatic program repair has been well studied in the programming language
+C, not much study has been done on Java. Since the programming practice between
+C and Java is not trivial, we will also show some characteristics of how human
+developers fix bugs in Java.
 
-A good complement for this paper is~\cite{zhong2015}, where they look for additions and
-deletions in a smaller data set. In this paper, we focus more on the replacements,
-which have been left out of the analysis of~\cite{zhong2015}, and expand their results of the deletions and additions in a broader dataset~\cite{dyer2013}.
+A good complement for this paper is~\cite{zhong2015}, where they look for
+additions and deletions in a smaller data set. In this paper, we focus more on
+the replacements, which have been left out of the analysis of~\cite{zhong2015},
+and expand their results of the deletions and additions in a broader
+dataset~\cite{dyer2013}.
 

### 2016-02-18 MSRChallenge2016.tex

--- 2016-02-17 MSRChallenge2016.tex
@@
 \begin{abstract}
-
-With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered.
-We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements, additions and deletions made to these files from real life projects in Github.
-
-We found valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we also analyzed what are the most likely statements to replace others.
-
-This information will help automatic program repair tools to be more likely to find a patch and also to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
-
+  Many implementations of recent work to automatically repair bugs in software
+  target programs written in C. Work that targets Java often begins from, or at
+  least compares to, direct translations of such techniques to a Java context.
+  However, Java and C are very different languages, and these differences should be
+  studied and understood if existing approaches are to be profitably translated
+  from one to another.  We conducted a large-scale study of bug-fixing commits
+  to Java projects, focusing on assumptions underlying common
+  search-based repair approaches.  We make a number of observations that can be
+  leveraged to guide automatic software repair to target Java specifically,
+  including common and uncommon statement replacements as conducted by human
+  developers and the applicability of previously-proposed patch construction
+  operators in the Java context.  We anticipate that these observations can
+  inform more effective patch construction techniques for Java, both in raw
+  numbers of bugs fixed and the usability and maintainability of the resulting
+  patches. 
 \end{abstract}
@@
 
-Automatic bug repair is the branch of computer science that deals with automated
-ways to repair errors in software. There have been several approaches taken
-towards improving the different methodologies to repair bugs in software
-automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}.
-A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
-it. In this paper we have taken 8 out of the 10 PAR templates and tested how
-common they are in the repairs made by programmers in the latest official data
-dump of Github as of September 2015 provided by~\cite{dyer2013}.
+Research in automatic bug repair seeks to develop techniques that can
+automatically construct patches to repair software bugs, which are prevalent in
+practice. There has been considerable attention paid to this problem in recent
+years~\cite{kim2013,weimer2009,legoues2012,pan2009,so,many,more}.
+Mutation-based, or generate-and-validate approaches, typically operate by
+generating a large number of candidate patches using a pre-defined set of
+mutation operators, and then validating their correctness with respect to a set
+of test cases.  These mutation operators range from simple, coarse granularity
+statement-level mutations~\cite{examples} to human-constructed templates learned
+from a large corpus of previous human bug-fixing commits~\cite{kim2013}.
 
-Some other well known approaches~\cite{weimer2009,legoues2012} have been based on the idea of applying a number of mutation operators to the buggy code in order to find a patch.
-In this opportunity, we study the degree to which these mutation operators apply in practice, taking as a subject of study several million human-made bug fixes from Github.
-This way it will make it more likely for automatic error repair approaches to succeed in
-finding a patch for a particular error, and also, to provide automatic error
-repair software with guidelines to make the patches more human-like and
-therefore more readable and maintainable by human developers, as studied empirically by~\cite{kim2013}.
+A considerable proportion of this previous work is implemented to target
+programs written in C, with only limited attention paid to programs in other
+languages, like Java~\cite{kim2013}.  At least partially as a result,
+researchers targeting Java must either start from or at least compare against
+imperfect baselines, that is, Java-based implementations of techniques
+originally implemented for C~\cite{nopol}. %  Even PAR~\cite{kim2013}, perhaps the
+% best-known previously-proposed Java-based program repair technique, both starts
+% from and is directly compared to a Java implementation of GenProg~\cite{genprog}, which
+% targets the C programming language.  
+This C focus extends to empirical studies
+of bug fixing practice, used to inform research questions in automatic
+repair~\cite{zhong2015}.
 
-We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
-researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
-with several different templates resembling patterns programmers use to patch
-bugs, and then performed an empirical study to evaluate which patches do human programmers prefer.
+This is an oversight, because, to put it simply: Java and C are very different
+languages.  Consider GenProg~\cite{genprog,cites}, a well-known technique in
+this space: GenProg uses a genetic programming heuristic to combine
+statement-level mutations into patches to address a particular defect.
+``Statement'' is a well-defined semantic unit in the C programming
+language~\cite{cspec}; to which semantic unit in Java does this concept map?
+Can we learn more
+intelligent rules to inform candidate modifications
+(cf. Prophet~\cite{rinardPopl2016}, for C)?  What types of
+semantic scoping rules should be used to limit mutations, given the relative
+stringence of the Java compilers?
 
-Since automatic program repair has been well studied in the programming language C.
-We are now focusing on the programming language Java, and analyzing the behavior of programmers in this particular language.
+In this paper, we study bug-fixing commits to Java programs, taking as a subject
+of study several million human-made bug fixes from Github. We study broad
+characteristics of changes to fix bugs; the applicability of previously-proposed
+templates to repairing defects in Java programs~\cite{kim2013}; and the nature
+of additions, replacements, of statements in bug-fixing commits. We make
+observations to directly guide future research in automatic repair to Java
+programs, to increase the success rate of such techniques and the degree to
+which the patches are human-like and therefore more readable and maintainable by
+human developers; this is important, because patch quality is an important
+concern in this research area~\cite{Qi2013}.
 
-A good complement for this paper is~\cite{zhong2015}, where they look for additions and
-deletions in a smaller data set. In this paper, we focus more on the replacements,
-which have been left out of the analysis of~\cite{zhong2015}, and expand their results of the deletions and additions in a broader dataset~\cite{dyer2013}.
+% On the other hand, some approaches~\cite{kim2013} search for specific patterns
+% and modify source code according to predefined templates. A well known approach
+% is PAR~\cite{kim2013}, which creates 10 different repair templates and applies
+% them to the buggy code in an effort to repair it. In this paper we have taken 8
+% out of the 10 PAR templates and tested how common they are in the repairs made
+% by programmers in the latest official data dump of Github as of September 2015
+% provided by~\cite{dyer2013}.  Our results provide evidence of how common those
+% patterns are in practice. We take as reference the study performed by Dongsun
+% Kim et al.~\cite{kim2013} in which they look for the most common ways in which
+% programmers patch bugs in software. The researchers developed a variation of the
+% tool Genprog~\cite{weimer2009,legoues2012} with several different templates
+% resembling patterns programmers use to patch bugs, and then performed an
+% empirical study to evaluate which patches do human programmers prefer.
 
-\section{Methodology}
-Our methodology is applied to the latest official data dump of Github as of
-September 2015 provided by~\cite{dyer2013}. In the following subsections, we first
-describe data source and objective of our study. We then describe how we detect
-bug fixing patterns in PAR to find out how common they are the dataset. Last but
-not least, we describe our approach to detect Delete, Replace, and Append
-bug-fixing patterns.
+A good complement for this paper is~\cite{zhong2015}, where they look for
+additions and deletions in a smaller data set. In this paper, we focus more on
+the replacements, which have been left out of the analysis of~\cite{zhong2015},
+and expand their results of the deletions and additions in a broader
+dataset~\cite{dyer2013}.
+\todo{note to self (CLG) should mention the work from Earl, Yuriy, and others
+  that looked at the redundancy assumption.}
 
-\subsection{Data Source and Research Objective}
-We used the Boa platform~\cite{dyer2013} to be able to query the Github repository
-looking for patterns that humans use to patch errors in the their code. Our main
-goal is to provide guidelines for automatic error fixing approaches by providing
-necessary information regarding historical replace, delete and append statements
-in human written patches.
+\todo{roadmap}
 
-\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
-The bug fixing patterns that we analyze in this work are adopted from Kim et
-al. paper~\cite{kim2013}. The following is the description of each considered
-pattern. 
-\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
-  but we need to explain why.}
-  \begin{enumerate}
-	\item {\bf Altering method parameters (AMP)}\\
-	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
-	{\bf Description:} This pattern changes the input for method parameters.
-	\item {\bf Calling another method with the same parameters (MSM)}\\
-	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
-	{\bf Description:} This pattern changes the method name.
-	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
-	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
-	{\bf Description:} This pattern adds one more parameter to the method.
-	\item {\bf Changing a branch condition (CBC)}\\
-	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
-	{\bf Description:} This pattern adds or removes condition.
-	\item {\bf Initializing an object (IAO)}\\
-	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
-	{\bf Description:} This pattern adds a initialization to object declaration.
-	\item {\bf Adding a null checker (ANC)}\\
-	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
-	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
-	\item {\bf Adding an array out of bound checker (AOB)}\\
-	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
-	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
-	\item {\bf Adding a collection out of bound checker (COB)}\\
-	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
-	{\bf Description:} This pattern inserts a condition to check that a collection index is within bound before it is used.
-\end{enumerate}
+\section{Dataset and Characteristics}
 
-The above patterns only cover 8 out of 10 bug fixing patterns in PAR.
-The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope.
-Pattern (1) cannot be analyzed because Boa does not support {\em instanceof} expression.
-Similarly, pattern (2) requires us to track scope between pre-fix and post-fix version, which is not supported by Boa.
-Implementing them ourselves might be possible, but it might require too much effort than necessary.
-Investigating 8 out of 10 patterns should give us a good idea on how common the patterns actually are.
+We begin by broadly characterizing the bug-fixing changes to Java code in our
+dataset. 
+We perform our analysis on the \emph{2015 September/Github} dataset on Boa, 
+which includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
+all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
+revisions.
 
-As mentioned before, we analyze bug fixing patterns by utilizing Boa's language
-infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
-a domain specific language to perform analysis on source code. Despite this
-advantage, Boa still have limited capability that prevents us from performing
-precise detection of bug fixing patterns. For example, it is unable to perform a
-diff between two file versions, which is needed to compare the pre-fix and the
-post-fix version of a buggy file. Thus, rather than finding the exact count of
-bug fixing patterns, we will find an approximate count of those patterns. The
-following are descriptions on how we detect each pattern.
-
-\begin{enumerate}
-\item {\bf AMP Pattern}\\
-  To detect AMP pattern, for both pre-fix and post-fix version of a buggy file,
-  we create a custom method call signature. This signature contains method name,
-  literal parameter, and variable parameter. we consider parameter containing
-  custom expression as OTHER. This is due to inexistence of function that can
-  print Abstract Syntax Tree (AST) back to source code in Boa. We discard method
-  signatures that appear both in pre-fix and post-fix version. We then find
-  whether there exists method with the same name and the same number of
-  parameters, but different parameter signatures in pre-fix and post-fix
-  version. If it exists, we consider that AMP pattern is found.
-
-\item {\bf MSM Pattern}\\
-  To detect MSM pattern, we create method signature similar like when detecting
-  AMP pattern. This time, we find whether there exists method with the exact
-  same parameter signature but different name in pre-fix and post-fix
-  version. If it exists, we consider that MSM pattern is found.
-
-\item {\bf COM Pattern}\\
-  To detect COM pattern, we create method signature similar like when detecting
-  AMP and COM pattern. This time, we find whether there are exists method with
-  the same name, but the number of parameters in pre-fix and post-fix version
-  differs by one. If it exists, we consider that COM pattern is found.
-
-\item {\bf CBC Pattern}\\
-  To detect CBC pattern, we count the number of { \em logical and} and {\em
-    logical or} inside if conditional expression for both pre-fix and post-fix
-  version. we assume that the addition/removal of logical operators indicate
-  addition/removal of condition. If there are count differences between pre-fix
-  and post-fix version, we consider that CBC pattern is found.
-
-\item {\bf IAO Pattern}\\
-  To detect IAO pattern, we count the number of NEW expression in variable
-  declaration for both pre-fix and post-fix version. If there are count
-  differences between pre-fix and post-fix version, we consider that IAO pattern
-  is found.
-
-\item {\bf ANC Pattern}\\
-  To detect ANC pattern, we count the number of if conditional expression that
-  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
-  version. If there are count differences between pre-fix and post-fix version,
-  we consider that ANC pattern is found.
-
-\item {\bf AOB Pattern}\\
-  To detect AOB pattern, we count the number of if conditional expression that
-  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
-  post-fix version. If there are count differences between pre-fix and post-fix
-  version, we consider that AOB pattern is found.
-
-\item {\bf COB Pattern}\\
-To detect COB pattern, we count the number of if conditional expression that
-contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
-post-fix version. If there are count differences between pre-fix and post-fix
-version, we consider that COB pattern is found.
-
-\end{enumerate}
-\todo{IMPORTANT: Ferdian, where did the results go?  Please add the results of
-  the Par study into results somewhere where it fits.}
-
-\begin{table*}
-	\centering
-	\resizebox{\textwidth}{100pt}{
-		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
-			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
-			\\ \hline
-
-\texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
-\\ \hline
-\texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
-\\ \hline
-\texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
-\\   \hline
-\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
-\\ \hline
-\texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
-\\ \hline
-\texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
-\\ \hline
-\texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
-\\ \hline
-\texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
-\\ \hline
-\texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
-\\ \hline
-\texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
-\\ \hline
-\texttt{Synch} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
-\\ \hline
-\texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
-\\ \hline
-\texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
-\\ \hline
-\texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
-\\ \hline
-\texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
-			\\ \hline
-		\end{tabular}
-		}
-		\caption{Likelyness to replace the statement in the first column for the statement in the top row, in Java}
-\end{table*}
-
-\subsection{Replace Query}
-The replace query we designed, is a query in which we create a visitor to traverse all the fixing revisions in this repository~\cite{dyer2013}. Therefore we are analyzing only files
-that were already committed and are now being reviewed to fix an error.
-
-We visit each statement in the previous state of that changed
-file, before the change was applied and we count the amount of appearances of
-the first statement we are analyzing (the one that was deleted), and then we
-count the amount of appearances of the second statement we are analyzing (the
-one that was inserted). We save these values, and do the same for the latest
-version of the file and save these values as well.
-
-We then compare these results to see if either the first and second statements
-being analyzed increased or decreased. Depending on these we have two
-conditionals:
-
-If the amount of occurrences of the first statement decreased and the amount of
-occurrences of the second statement increased on the same file, then we say that
-the first statement was replaced by the second statement in that file. Likewise,
-if the amount of occurrences of the first statement increased and the amount of
-occurrences of the second statement decreased on the same file, we say that the
-second statement was replaced by the first statement in that file. We count the
-amount of files in which this happens for each of these two cases.
-
-The numbers in the slots of Table 1, represent the percentage rate at which the elements of the leftmost column were replaced by the elements of the top row.
-In the first column we have the list of statements that are being replaced (faulty statements that were removed), and on the top row we have the list of statements for which that statement was replaced for (the new statement put instead).
-For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column) of the data, we have a 0.81, which means that if we take all the instances in which a Do statement was replaced by something else, the amount of times that it was replaced by an Assert statement, represent a 0.81% of the times.
-
-It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the same statement kind, since it is counting the amount of appearances of each statement kind.
-So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file will remain the same.
-
-\section{Results}
-
-% (This is the old version)
-% This section investigates how do developer fix bugs from three different
-% perspectives. To begin with, we show some characteristics of real-world bug
-% fixes.  Afterwards, we look deeper to find out what kinds of statements are
-% usually added, modified or deleted by human developers to fix bugs. Lastly, we
-% show how common PAR's fixing templates are in our dataset.
-
-This section shows our analysis results. To begin with, we discuss the dataset
-we are using, and some characteristics of real-world bug fixes. Afterwards, we
-provide insights for two main categories of automatic program repair approaches.
-On the one hand, some approaches rely on mutation operators to
-modify the source code~\cite{legoues2012,weimer2009}, but we have limited knowledge about what kinds of
-statements are usually modified. Our analysis results will fill in this
-knowledge gap. On the other hand, some automatic program repair approaches~\cite{kim2013} search for specific patterns and modify source code according to
-predefined templates. Our results provide evidence of how common those
-patterns are in practice.
-
-\subsection{Dataset and Characteristics}
-
-We did our analysis on the \emph{2015 September/Github} dataset on Boa. This
-dataset includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
-all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
-revisions. We hope that this population is big enough to reflect the bug fixing
-practice.
-
-The rest of this subsection shows some characteristics of real-world bug fixes.
-To begin with, we are interested in:
-
-\begin{quote}
-	How many files are changed to fix a bug?
-\end{quote}
-
+\paragraph{How many files are changed to fix a bug?}
 To answer this question, we identify all the bug fixing revisions in our dataset
@@
 
-\begin{quote}
-	What are the file types of those changed files?
-\end{quote}
-
+\paragraph{What are the file types of those changed files?}
 In Boa, each changed file is represented by a \emph{ChangedFile} node, and it
@@
 
-\begin{quote}
+\paragraph{
 How often do developers introduce new classes, methods, fields, variables in
-	bug fixing commits?
-\end{quote}
-
+	bug fixing commits?}
 This research question is interesting because most automatic program repair
 approaches often do not create new classes/methods/fields/variables to fix bugs.
-Most approaches guess and synthesize the patches based on existing source code.
+Most approaches guess and synthesize the patches based on existing source code,
+and direct translations of approaching from C to Java do not naturally consider
+object-oriented concerns, like fields or classes.
 
@@
 
-\subsection{What changes are common in real-world bug fixes?}
+\section{PAR Bug Fixing Patterns}\label{sec:method}
 
-Most automatic program repair approaches mutate source code using predefined
-mutation operators, which represent different ways of modifying source code. In
-order to generate patches that make more sense to human developers, it would be
-beneficial to first investigate how developers mutate source code to fix bugs.
+Par is a well-known technique for patch generation that 
+On the other hand, some approaches~\cite{kim2013} searches for specific patterns
+and modifies java code according to predefined templates, constructed by humans
+to cover a large set of bug fixes from an existing corpus.  As one of the only
+techniques to directly target Java, it is an important source of possible
+mutations to study to inform future directions. 
+We therefore search for and analyze most of the bug fixing patterns proposed by
+Kim et al.~\cite{kim2013} and assess their prevalence on this distinct
+dataset by using Boa's language infrastructure~\cite{dyer2013} to identify the patterns
+in the commits in the dataset.
 
-For each bug fixing revision $r$ and each statement kind $k$, we count how many
-statements of kind $k$ are there in revision $r$ and $r-1$ ($r-1$ means the
-revision before revision $r$), and then compare the two numbers. For example, if
-the number of if statements in revision $r$ is more than the number in revision
-$r-1$, we say bug fixing revision $r$ introduce new if statements. Note that
-``introducing new if statements'' does not necessarily mean human developers
-introduce them to fix bugs. However, our hope is that this analysis could still
-provide us some hints, given the large number of bug fixing revisions we are
-analyzing.
+% A well known approach
+% is PAR~\cite{kim2013}, which creates 10 different repair templates and applies
+% them to the buggy code in an effort to repair it. In this paper we have taken 8
+% out of the 10 PAR templates and tested how common they are in the repairs made
+% by programmers in the latest official data dump of Github as of September 2015
+% provided by~\cite{dyer2013}.  Our results provide evidence of how common those
+% patterns are in practice. We take as reference the study performed by Dongsun
+% Kim et al.~\cite{kim2013} in which they look for the most common ways in which
+% programmers patch bugs in software. The researchers developed a variation of the
+% tool Genprog~\cite{weimer2009,legoues2012} with several different templates
+% resembling patterns programmers use to patch bugs, and then performed an
+% empirical study to evaluate which patches do human programmers prefer.
 
-\begin{figure*}[!t] \centering
-	\includegraphics[width=0.95\textwidth]{StmtType} \caption{For each kind
-	of statement, how many bug fixing revisions add/delete statements of the
-same kind?} \label{fig:StmtType} \end{figure*}
+\subsection{Detecting PAR patterns in Boa}
 
-From Figure~\ref{fig:StmtType} \todo{fix the small fonts in this graph}, we can
-see that expression, if, return, for and try catch statements are added most
-often. On the other hand, the same types of statements are also deleted most
-often. This finding indicates that most bugs were fixed by changing the control
-flow of the program using if, return, for, while, and try catch statements.
+Boa's capabilities are powerful, but are limited in the precision it enables in
+our detection of these patterns. For example, it is unable to directly perform a
+diff between two file versions. Thus, rather than finding the exact count of
+bug fixing patterns, we will find an approximate count by processing pre- and
+post- fix files separately.  Additionally, there are
+two of the originally proposed 10 patterns that cannot be easily detected by
+Boa, as we describe below.
 
-For each bug fixing revision, the results discussed above consider both newly
-added files and existing files. Since most automatic program repair approaches
-do not generate new files to fix bugs, the rest of this section only considers
-files that were already in the repositories when developers fixed bugs. Our
-analysis shows that there are 46,301,429 of them. In these files, there is a
-total of 517,281 statement kinds being replaced, and 511,198 replacing these
-statements kinds.
+The patterns we search for are as follows, including our mechanism for
+detecting them using Boa:
 
-We analyzed each of these files looking for statement kinds being either replaced by other kinds, deleted or appended to the file.
+\vspace{1ex}
+\noindent {\bf Altering method parameters (AMP)}.  This pattern changes the
+input for method parameters.  {\bf Example:} obj.method(v1,v2) $\rightarrow$
+obj.method(v1,v3). To detect this pattern, for both pre-fix and post-fix version
+of a buggy file, we create a custom method call signature. This signature
+contains method name, literal parameter, and variable parameter. we consider
+parameter containing custom expression as OTHER. This is due to inexistence of
+function that can print Abstract Syntax Tree (AST) back to source code in
+Boa. We discard method signatures that appear both in pre-fix and post-fix
+version. We then find whether there exists method with the same name and the
+same number of parameters, but different parameter signatures in pre-fix and
+post-fix version. If it exists, we consider that AMP pattern is found.
 
-We found that the most common Replacer statement kind, meaning the statement
-kind that most commonly replaces others is the \textbf{If Statement} with
-101,366 appearances. The least common Replacer, meaning the statement kind which
-is less likely to replace other statement kinds is the \textbf{Type Declaration
-  Statement} with 447 appearances.
+\vspace{1ex}
+\noindent {\bf Calling another method with the same parameters (MSM)}.  This
+pattern changes a method name.  {\bf Example:} obj.method1(param) $\rightarrow$
+obj.method2(param).  To detect this pattern, we create method signature similar
+like when detecting AMP pattern. This time, we find whether there exists method
+with the exact same parameter signature but different name in pre-fix and
+post-fix version. If it exists, we consider that MSM pattern is found.
 
-The most common Replacee, which is the most likely statement kind to be replaced
-by another statement kind is the \textbf{Return Statement} with 111,938
-appearances. The least common Replacee, which is the least common statement to
-be replaced by another statement kind is the \textbf{Type Declaration Statement}
-with 399 appearances.
+\vspace{1ex}
+\noindent
+{\bf Calling another overloaded method with one more parameter (COM)}. This
+pattern adds one more parameter to a method. 
+	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2).
+  To detect COM pattern, we create method signature similar like when detecting
+  AMP and COM pattern. This time, we find whether there are exists method with
+  the same name, but the number of parameters in pre-fix and post-fix version
+  differs by one. If it exists, we consider that COM pattern is found.
 
-\subsubsection{Likeliness of replacement}
-This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
-first find a faulty statement using several different fault localization
-techniques~\cite{fry2010}, and once they have that faulty statement, they apply
-different kinds of edits to it, usually at random. Which makes it equally likely
-to replace an statement for another without looking at the kinds of statements
-being replaced.
+\vspace{1ex}
+\noindent
+ {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
+	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0).
+  To detect CBC pattern, we count the number of { \em logical and} and {\em
+    logical or} inside if conditional expression for both pre-fix and post-fix
+  version. we assume that the addition/removal of logical operators indicate
+  addition/removal of condition. If there are count differences between pre-fix
+  and post-fix version, we consider that CBC pattern is found.
 
-With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for.
-By taking a look at the data of Table 1, we can find the most likely replacements that will end up being a successful patch.
+\vspace{1ex}
+\noindent
+ {\bf Initializing an object (IAO)}. This pattern adds a initialization to object declaration.
+  To detect IAO pattern, we count the number of NEW expression in variable
+  declaration for both pre-fix and post-fix version. If there are count
+  differences between pre-fix and post-fix version, we consider that IAO pattern
+  is found.
+	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type().
 
-For example, if we are fixing a Java program, and we have a faulty statement that happens to be a For Statement.
-Then we can look up in Table 1 the For Statement Row (6th row), and take a look at the probability of that statement to be replaced by other kinds of statement.
-In this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.89\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.79\% of likeliness to replace a For Statement.
-This way we know that it is more likely for a programmer to replace a For Statement for those three different kinds of statements and this provides guidelines to the automatic bug repair approaches to consider this on their effort to find a patch.
+\vspace{1ex}
+\noindent
+ {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
+    object is null or not in order to prevent unexpected state.
+	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
+  To detect ANC pattern, we count the number of if conditional expression that
+  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
+  version. If there are count differences between pre-fix and post-fix version,
+  we consider that ANC pattern is found.
 
-\subsubsection{Most common replacements}
-Our results show that the most common replacement is when developers remove a Return statement and insert an If statement.
-This showed up in 30,489 files in the code database.
-The second most common replacement is removing an If statement and insert a Return statement instead, which had 28,536 appearances in the code database.
-Third to that, is to remove a Return statement and insert a Throw statement.
+\vspace{1ex}
+\noindent
+ {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
+    index is within bound right before the index is used.
+	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
+  To detect AOB pattern, we count the number of if conditional expression that
+  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
+  post-fix version. If there are count differences between pre-fix and post-fix
+  version, we consider that AOB pattern is found.
 
-\subsubsection{Least common replacements}
-On the opposite side of the data, we can see that the least common replacement was an Assert statement replacing a Type Declaration statement.
-This was the only replacement to have zero appearances in our search through the 46,301,429 files being fixed.
-Close to it, as the second least common replacement was removing a Do statement and insert a Type Declaration statement, with one appearance in our code database, and on third place, removing a Label and insert a Type Declaration Statement had one appearance in our code database.
+\vspace{1ex}
+\noindent
+ {\bf Adding a collection out of bound checker (COB)}.  This pattern inserts a condition to check that a
+    collection index is within bound before it is used.
+	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
+To detect COB pattern, we count the number of if conditional expression that
+contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
+post-fix version. If there are count differences between pre-fix and post-fix
+version, we consider that COB pattern is found.
 
-\subsection{How common are the fixing templates of PAR?}\label{sec:freqfixpattern}
-After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}.
-The result shows that AMC, MSM, COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files.
-We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB.
-If we assume that these patterns never appear together in the dataset, these patterns cover 14.78\% of buggy files.
-Kim et al.
-mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}.
-Although we only detect 8 out of 10 bug fixing patterns, it is hard to believe that the remaining two patterns cover 15\% of buggy files, especially 14.78\% is a number we get when we assume that the patterns that we detect never appear together.
-Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound.
-This suggests that common bug fixing patterns might not be as common as it appeared to be.
+\vspace{1ex} The above patterns only cover 8 out of 10 bug fixing patterns in
+PAR. The other two patterns are: (1) checking that an object is an instance of a
+target class before casting it; and (2) replacing expression in an if condition
+by another expression in the same scope. Pattern (1) cannot be analyzed because
+Boa does not support the {\em instanceof} expression. Similarly, pattern (2)
+requires us to track scope between pre-fix and post-fix version, which is not
+supported by Boa. Implementing them ourselves might be possible, but it might
+require too much effort than necessary. We speculate that investigating 8 out of
+10 patterns should give us a good idea on how common the patterns actually are.
+
+\subsection{Results} \label{sec:freqfixpattern}
 
@@
 \end{table}
+\todo{Ferdian: please add a column that shows the number sin terms of
+  percentages, not just raw numbers.}
+
+After running the bug pattern detection approach on Boa's dataset, I obtained
+the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM,
+COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%,
+4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files. We can see that the
+most common pattern among these patterns is CBC and the least common pattern is
+AOB. If we assume that these patterns never appear together in the dataset,
+these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
+patterns that they use cover almost 30\% of real
+patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
+it is hard to believe that the remaining two patterns cover 15\% of buggy files,
+especially 14.78\% is a number we get when we assume that the patterns that we
+detect never appear together. Moreover, the percentage of each pattern is based
+on imprecise approximation which is likely to represent an upper bound rather
+than a lower bound. This suggests that common bug fixing patterns might not be
+as common as it appeared to be.
+
+\section{Statement-level mutations}
+
+\begin{table*}
+	\centering
+	\resizebox{\textwidth}{100pt}{
+		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
+			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
+			\\ \hline
+
+\texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
+\\ \hline
+\texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
+\\ \hline
+\texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
+\\   \hline
+\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
+\\ \hline
+\texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
+\\ \hline
+\texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
+\\ \hline
+\texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
+\\ \hline
+\texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
+\\ \hline
+\texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
+\\ \hline
+\texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
+\\ \hline
+\texttt{Synch} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
+\\ \hline
+\texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
+\\ \hline
+\texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
+\\ \hline
+\texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
+\\ \hline
+\texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
+			\\ \hline
+		\end{tabular}
+		}
+		\caption{Likeliness to replace the statement in the first column for the statement in the top row, in Java}
+\end{table*}
+
+Most automatic program repair approaches mutate source code using predefined
+mutation operators, which represent different ways of modifying source code. In
+order to generate patches that make more sense to human developers, it would be
+beneficial to first investigate how developers mutate source code to fix bugs. 
+Thus, beyond characterizing the degree to which previously-proposed Java-specific
+operators apply in our dataset, we further characterized the nature of
+coarser-grained replacement operators, which are also commonly translated from C
+techniques to Java.  We did this via a query that visits all fixing revisions in
+the repository; as a result, we analyze files to which changes have been made
+and thuswere already committed and are now being reviewed to fix an error.
+
+\subsection{Replacements}
+\todo{The biggest problem right now is the lack of integration between this
+  study and Chu Pan's.  Please work together to find a way to unify it.  One of
+  you will need to cut some of your text.  I don't care who, but we need to find
+  a way to tell one story.}
+
+Because direct diffs are difficult to identify, we heuristically approximate the
+extent to which one statement type appears to be ``replaced'' by another across
+this dataset.  To do this, for each modified file, we count the number of
+appearances of each statement type in the file pre- and post-commit.  We then
+compare the results to see how many of each statement type was removed, and how
+many inserted, to roughly characterize the types of replacement that happen at a
+per-file level.  For each statement type (as tagged by the Boa infrastructure
+for Java), we process the results as follows: 
+if number occurrences of one statement type decreased post-fix and the number of
+another type increased, we say that
+the first statement type was replaced by the second statement type for that
+file.  We collate these results over all statement types and all files modified
+in bug fixing commits in the dataset.
+
+It is important to notice that this analysis doesn't consider replacing an
+statement kind for a different version of the same statement kind, since it is
+counting the amount of appearances of each statement kind. So, if for example,
+the developer modifies the condition inside of an if statement, the amount of if
+statements in the file will remain the same.
+
+The numbers in the slots of Table 1, represent the percentage rate at which the
+elements of the leftmost column were replaced by the elements of the top row. In
+the first column we have the list of statements that are being replaced (faulty
+statements that were removed), and on the top row we have the list of statements
+for which that statement was replaced for (the new statement put instead). For
+example, if we take the intersection of row 5 (DoStatement row) and column 2
+(AsserStatement column) of the data, we have a 0.81, which means that if we take
+all the instances in which a Do statement was replaced by something else, the
+amount of times that it was replaced by an Assert statement, represent a
+0.81% of the times.
+
+This study is directly applicable to automatic software repair. Most common
+tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
+first find a faulty statement using several different fault localization
+techniques~\cite{fry2010}, and once they have that faulty statement, they apply
+different kinds of edits to it, usually at random. Which makes it equally likely
+to replace an statement for another without looking at the kinds of statements
+being replaced.
+
+With this study, we are able to make a more accurate guess, when having a known
+faulty statement, to which statement it is more likely to replace it for. By
+taking a look at the data of Table 1, we can find the most likely replacements
+that will end up being a successful patch.
+
+For example, if we are fixing a Java program, and we have a faulty statement
+that happens to be a For Statement. Then we can look up in Table 1 the For
+Statement Row (6th row), and take a look at the probability of that statement to
+be replaced by other kinds of statement. In this example we see that the top 3
+most likely statements to replace a For Statement are an If statement with a
+22.89\% likeliness, followed by a return statement with a 21.08\%, and third is
+a While statement with a 13.79\% of likeliness to replace a For Statement. This
+way we know that it is more likely for a programmer to replace a For Statement
+for those three different kinds of statements and this provides guidelines to
+the automatic bug repair approaches to consider this on their effort to find a
+patch.
+
+\subsubsection{Most common replacements}
+Our results show that the most common replacement is when developers remove a
+Return statement and insert an If statement. This showed up in 30,489 files in
+the code database. The second most common replacement is removing an If
+statement and insert a Return statement instead, which had 28,536 appearances in
+the code database. Third to that, is to remove a Return statement and insert a
+Throw statement.
+
+\subsubsection{Least common replacements}
+On the opposite side of the data, we can see that the least common replacement
+was an Assert statement replacing a Type Declaration statement. This was the
+only replacement to have zero appearances in our search through the 46,301,429
+files being fixed. Close to it, as the second least common replacement was
+removing a Do statement and insert a Type Declaration statement, with one
+appearance in our code database, and on third place, removing a Label and insert
+a Type Declaration Statement had one appearance in our code database.
+
+\subsection{Deletions and insertions}
+
+\begin{figure*}[!t] \centering
+	\includegraphics[width=0.95\textwidth]{StmtType} \caption{For each kind
+	of statement, how many bug fixing revisions add/delete statements of the
+same kind?} \label{fig:StmtType} \end{figure*}
+
+For each bug fixing revision $r$ and each statement kind $k$, we count how many
+statements of kind $k$ are there in revision $r$ and $r-1$ ($r-1$ means the
+revision before revision $r$), and then compare the two numbers. For example, if
+the number of if statements in revision $r$ is more than the number in revision
+$r-1$, we say bug fixing revision $r$ introduce new if statements. Note that
+``introducing new if statements'' does not necessarily mean human developers
+introduce them to fix bugs. However, our hope is that this analysis could still
+provide us some hints, given the large number of bug fixing revisions we are
+analyzing.
+
+From Figure~\ref{fig:StmtType} \todo{fix the small fonts in this graph}, we can
+see that expression, if, return, for and try catch statements are added most
+often. On the other hand, the same types of statements are also deleted most
+often. This finding indicates that most bugs were fixed by changing the control
+flow of the program using if, return, for, while, and try catch statements.
+
+For each bug fixing revision, the results discussed above consider both newly
+added files and existing files. Since most automatic program repair approaches
+do not generate new files to fix bugs, the rest of this section only considers
+files that were already in the repositories when developers fixed bugs. Our
+analysis shows that there are 46,301,429 of them. In these files, there is a
+total of 517,281 statement kinds being replaced, and 511,198 replacing these
+statements kinds.
+
+We analyzed each of these files looking for statement kinds being either
+replaced by other kinds, deleted or appended to the file.
+
+We found that the most common Replacer statement kind, meaning the statement
+kind that most commonly replaces others is the \textbf{If Statement} with
+101,366 appearances. The least common Replacer, meaning the statement kind which
+is less likely to replace other statement kinds is the \textbf{Type Declaration
+  Statement} with 447 appearances.
+
+The most common Replacee, which is the most likely statement kind to be replaced
+by another statement kind is the \textbf{Return Statement} with 111,938
+appearances. The least common Replacee, which is the least common statement to
+be replaced by another statement kind is the \textbf{Type Declaration Statement}
+with 399 appearances.
 

### 2016-02-18 MSRChallenge2016.tex
Minor changes

--- 2016-02-17 MSRChallenge2016.tex
@@
        \affaddr{Pittsburgh, PA}\\
-       \email{chupanw@cs.cmu.edu}       
+       \email{email@domain.com}       
 \and  % use '\and' if you need 'another row' of author names
@@
 
-We did our analysis on the \emph{2015 September/Github} dataset on Boa. This
+We performed our analysis on the \emph{2015 September/Github} dataset provided by~\cite{dyer2013}. This
 dataset includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
@@
 methods that annotated by @Test if JUnit is used), this number is not that
-scary. However, what surprises us is that $1.32$ fields are created per bug fix.
+scary. However, something to notice is that $1.32$ fields are created per bug fix.
 This indicates that automatic program repair approaches should pay attention to
@@
   Introducing & Total Number & Average \\ \hline \hline
-  Class & 729,201 & 0.16 \\ \hline
-  Methods & 3,186,867 & 0.69 \\ \hline
-  Fields & 6,076,646 & 1.32 \\ \hline
-  Variables & 924,259 & 0.2 \\ \hline
+  Class & 729201 & 0.16 \\ \hline
+  Methods & 3186867 & 0.69 \\ \hline
+  Fields & 6076646 & 1.32 \\ \hline
+  Variables & 924259 & 0.2 \\ \hline
   \end{tabular}
-  \caption{Introducing new classes, methods, fields, variables to fix bugs}
+  \caption{File Types of Changed Files}
   \label{tbl:new}
@@
 
-\subsection{What changes are common in real-world bug fixes?}
+\subsection{Statement level changes}
 
@@
 \begin{table}[!htb]
-	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
 	\centering
@@
 	\end{tabular}
+	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
+
 \end{table}

### 2016-02-18 MSRChallenge2016.tex
Revert "Minor changes"
This reverts commit 852719faa3b9e4fcbac144a287481316ec3db88d.

--- 2016-02-18 MSRChallenge2016.tex
@@
 	\centering
-	\begin{tabular}{lr} 
+	\begin{tabular}{lrr} 
 		\hline
-		& \textbf{GitHub}\\
+		& \textbf{\#Appearance} & \textbf{Percentage}\\
 		\hline
-		\#Buggy Files & 46,301,429 \\ 
-		\#AMP Pattern & 901,083 \\
-		\#MSM Pattern & 783,073 \\
-		\#COM Pattern & 270,128 \\ 
-		\#CBC Pattern & 1,959,377 \\  
-		\#IAO Pattern & 1,308,006 \\  
-		\#ANC Pattern & 1,340,561 \\  
-		\#AOB Pattern & 128,016 \\  
-		\#COB Pattern & 262,915 \\   
+		%Buggy Files & 46,301,429 \\ 
+		AMP Pattern & 901,083 & 1.95\%\\
+		MSM Pattern & 783,073 & 1.69\%\\
+		COM Pattern & 270,128 & 0.58\%\\ 
+		CBC Pattern & 1,959,377 & 4.23\%\\  
+		IAO Pattern & 1,308,006 & 2.82\%\\  
+		ANC Pattern & 1,340,561 & 2.90\%\\  
+		AOB Pattern & 128,016 & 0.28\%\\  
+		COB Pattern & 262,915 & 0.57\%\\   
 		\hline
@@
 \end{table}
-\todo{Ferdian: please add a column that shows the number sin terms of
-  percentages, not just raw numbers.}
 
-After running the bug pattern detection approach on Boa's dataset, I obtained
-the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM,
-COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%,
-4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files. We can see that the
+After running the bug pattern detection approach on Boa's dataset, we obtained
+the result shown in Table~\ref{tab:freqpattern}. It shows that the
 most common pattern among these patterns is CBC and the least common pattern is

### 2016-02-18 MSRChallenge2016.tex
Merged my part and Pan's, removed a lot of text

@@
 	\end{tabular}
+	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
+
 \end{table}
-
-After running the bug pattern detection approach on Boa's dataset, we obtained
-the result shown in Table~\ref{tab:freqpattern}. It shows that the
-most common pattern among these patterns is CBC and the least common pattern is
-AOB. If we assume that these patterns never appear together in the dataset,
-these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
-patterns that they use cover almost 30\% of real
-patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
-it is hard to believe that the remaining two patterns cover 15\% of buggy files,
-especially 14.78\% is a number we get when we assume that the patterns that we
-detect never appear together. Moreover, the percentage of each pattern is based
-on imprecise approximation which is likely to represent an upper bound rather
-than a lower bound. This suggests that common bug fixing patterns might not be
-as common as it appeared to be.
-
-\section{Statement-level mutations}
 
@@
 		}
-		\caption{Likeliness to replace the statement in the first column for the statement in the top row, in Java}
+		\caption{Likeliness to replace the statement in the first column for the statement in the top row, in Java}\label{tab:likeliness}
 \end{table*}
 
-Most automatic program repair approaches mutate source code using predefined
-mutation operators, which represent different ways of modifying source code. In
+After running the bug pattern detection approach on Boa's dataset, we obtained
+the result shown in Table~\ref{tab:freqpattern}. It shows that the
+most common pattern among these patterns is CBC and the least common pattern is
+AOB. If we assume that these patterns never appear together in the dataset,
+these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
+patterns that they use cover almost 30\% of real
+patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
+it is hard to believe that the remaining two patterns cover 15\% of buggy files,
+especially 14.78\% is a number we get when we assume that the patterns that we
+detect never appear together. Moreover, the percentage of each pattern is based
+on imprecise approximation which is likely to represent an upper bound rather
+than a lower bound. This suggests that common bug fixing patterns might not be
+as common as it appeared to be.
+
+\section{Statement-level mutations}
+Some automatic program repair approaches mutate source code using predefined
+mutation operators such as addition, deletion and replacement. In
 order to generate patches that make more sense to human developers, it would be
-beneficial to first investigate how developers mutate source code to fix bugs. 
-Thus, beyond characterizing the degree to which previously-proposed Java-specific
-operators apply in our dataset, we further characterized the nature of
-coarser-grained replacement operators, which are also commonly translated from C
-techniques to Java.  We did this via a query that visits all fixing revisions in
-the repository; as a result, we analyze files to which changes have been made
-and thuswere already committed and are now being reviewed to fix an error.
+beneficial to analyze how developers mutate source code to fix bugs.
 
 \subsection{Replacements}
-\todo{The biggest problem right now is the lack of integration between this
-  study and Chu Pan's.  Please work together to find a way to unify it.  One of
-  you will need to cut some of your text.  I don't care who, but we need to find
-  a way to tell one story.}
-
 Because direct diffs are difficult to identify, we heuristically approximate the
@@
 for Java), we process the results as follows: 
-if number occurrences of one statement type decreased post-fix and the number of
+if number of occurrences of one statement type decreased post-fix and the number of
 another type increased, we say that
 the first statement type was replaced by the second statement type for that
-file.  We collate these results over all statement types and all files modified
-in bug fixing commits in the dataset.
+file.
 
@@
 
-The numbers in the slots of Table 1, represent the percentage rate at which the
+The numbers in the slots of Table~\ref{tab:likeliness}, represent the percentage rate at which the
 elements of the leftmost column were replaced by the elements of the top row. In
@@
 example, if we take the intersection of row 5 (DoStatement row) and column 2
-(AsserStatement column) of the data, we have a 0.81, which means that if we take
-all the instances in which a Do statement was replaced by something else, the
-amount of times that it was replaced by an Assert statement, represent a
-0.81% of the times.
-
-This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
-first find a faulty statement using several different fault localization
-techniques~\cite{fry2010}, and once they have that faulty statement, they apply
-different kinds of edits to it, usually at random. Which makes it equally likely
-to replace an statement for another without looking at the kinds of statements
-being replaced.
-
-With this study, we are able to make a more accurate guess, when having a known
-faulty statement, to which statement it is more likely to replace it for. By
-taking a look at the data of Table 1, we can find the most likely replacements
-that will end up being a successful patch.
-
-For example, if we are fixing a Java program, and we have a faulty statement
-that happens to be a For Statement. Then we can look up in Table 1 the For
-Statement Row (6th row), and take a look at the probability of that statement to
-be replaced by other kinds of statement. In this example we see that the top 3
-most likely statements to replace a For Statement are an If statement with a
-22.89\% likeliness, followed by a return statement with a 21.08\%, and third is
-a While statement with a 13.79\% of likeliness to replace a For Statement. This
-way we know that it is more likely for a programmer to replace a For Statement
-for those three different kinds of statements and this provides guidelines to
-the automatic bug repair approaches to consider this on their effort to find a
-patch.
+(AsserStatement column) of the data, we have a 0.81, which means that Do statements were replaced by Assert statements 0.81\% of the times.
 
@@
 On the opposite side of the data, we can see that the least common replacement
-was an Assert statement replacing a Type Declaration statement. This was the
-only replacement to have zero appearances in our search through the 46,301,429
-files being fixed. Close to it, as the second least common replacement was
+was an Assert statement replacing a Type Declaration statement, which has zero appearances. The second least common replacement was
 removing a Do statement and insert a Type Declaration statement, with one
-appearance in our code database, and on third place, removing a Label and insert
-a Type Declaration Statement had one appearance in our code database.
+appearance in our search, and on third place, removing a Label and insert
+a Type Declaration Statement had one appearance in our search.
 
@@
 \begin{figure*}[!t] \centering
-	\includegraphics[width=0.95\textwidth]{StmtType} \caption{For each kind
+	\includegraphics[height=0.3\textheight, width=1\textwidth]{StmtType} \caption{For each kind
 	of statement, how many bug fixing revisions add/delete statements of the
 same kind?} \label{fig:StmtType} \end{figure*}
-
+\todo{I'm not sure the percentages in Figure~\ref{fig:StmtType} are visible, maybe moving the numbers so they don't overlap with the bars?}
 For each bug fixing revision $r$ and each statement kind $k$, we count how many
 statements of kind $k$ are there in revision $r$ and $r-1$ ($r-1$ means the
-revision before revision $r$), and then compare the two numbers. For example, if
-the number of if statements in revision $r$ is more than the number in revision
-$r-1$, we say bug fixing revision $r$ introduce new if statements. Note that
-``introducing new if statements'' does not necessarily mean human developers
-introduce them to fix bugs. However, our hope is that this analysis could still
-provide us some hints, given the large number of bug fixing revisions we are
-analyzing.
+revision before revision $r$), and then compare the two numbers.
 
@@
 files that were already in the repositories when developers fixed bugs. Our
-analysis shows that there are 46,301,429 of them. In these files, there is a
-total of 517,281 statement kinds being replaced, and 511,198 replacing these
-statements kinds.
+analysis shows that there are 46,301,429 of them.
 
-We analyzed each of these files looking for statement kinds being either
-replaced by other kinds, deleted or appended to the file.
-
-We found that the most common Replacer statement kind, meaning the statement
-kind that most commonly replaces others is the \textbf{If Statement} with
-101,366 appearances. The least common Replacer, meaning the statement kind which
-is less likely to replace other statement kinds is the \textbf{Type Declaration
+We found that the most common $Replacer$ statement kind (the statement
+kind that most commonly replaces others) is the \textbf{If Statement} with
+101,366 appearances; and the least common $Replacer$, is the \textbf{Type Declaration
   Statement} with 447 appearances.
 
-The most common Replacee, which is the most likely statement kind to be replaced
-by another statement kind is the \textbf{Return Statement} with 111,938
-appearances. The least common Replacee, which is the least common statement to
-be replaced by another statement kind is the \textbf{Type Declaration Statement}
+The most common $Replacee$ (the most likely statement kind to be replaced
+by another statement kind) is the \textbf{Return Statement} with 111,938
+appearances; and the least common $Replacee$ is the \textbf{Type Declaration Statement}
 with 399 appearances.
+
+\subsection{Applicability to Automatic Error Repair}
+This study is directly applicable to automatic software repair. Most common
+tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
+first find a faulty statement using several different fault localization
+techniques~\cite{fry2010}, and once they have that faulty statement, they apply
+different kinds of edits to it, usually at random. Which makes it equally likely
+to replace an statement for another without looking at the kinds of statements
+being replaced.
+
+With this study, we are able to make a more accurate guess, when having a known
+faulty statement, of which statements more commonly replace that faulty one to build a successful patch based on the data from Table~\ref{tab:likeliness}.
+Similarly with Figure~\ref{fig:StmtType}, we can have an informed guess of how often programmers insert or delete that particular kind of statement.
+
+For example, if we are fixing a Java program, and we have a faulty statement
+that happens to be a For Statement.
+Then we can look for the most likely statements to replace a For Statement (row 6): If statement (22.89\% likeliness), Return statement (21.08\%), and a While statement (13.79\% of likeliness to replace a For Statement).
+We also know that there is a 7.9\% of cases in which human programmers deleted this kind of statement, and in 10.6\% of the cases, a For statement was added to patch a bug.
+This
+way we provide guidelines to
+the automatic bug repair approaches to consider this on their effort to find a
+patch.
 

### 2016-02-18 MSRChallenge2016.tex
modify conclusion and PAR content

@@
   To detect COM pattern, we create method signature similar like when detecting
-  AMP and COM pattern. This time, we find whether there are exists method with
+  AMP and COM pattern. This time, we find whether there exists method with
   the same name, but the number of parameters in pre-fix and post-fix version
@@
   version. we assume that the addition/removal of logical operators indicate
-  addition/removal of condition. If there are count differences between pre-fix
-  and post-fix version, we consider that CBC pattern is found.
+  addition/removal of condition. If there is a larger count in post-fix version, we consider that CBC pattern is found.
 
@@
   To detect IAO pattern, we count the number of NEW expression in variable
-  declaration for both pre-fix and post-fix version. If there are count
-  differences between pre-fix and post-fix version, we consider that IAO pattern
+  declaration for both pre-fix and post-fix version. If there is a larger count in post-fix version, we consider that IAO pattern
   is found.
@@
   contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
-  version. If there are count differences between pre-fix and post-fix version,
+  version. If there is a larger count in post-fix version,
   we consider that ANC pattern is found.
@@
   contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
-  post-fix version. If there are count differences between pre-fix and post-fix
-  version, we consider that AOB pattern is found.
+  post-fix version. If there is a larger count in post-fix version, we consider that AOB pattern is found.
 
@@
 by another expression in the same scope. Pattern (1) cannot be analyzed because
-Boa does not support the {\em instanceof} expression. Similarly, pattern (2)
+Boa does not support {\em instanceof} expression. Similarly, pattern (2)
 requires us to track scope between pre-fix and post-fix version, which is not
@@
 most common pattern among these patterns is CBC and the least common pattern is
-AOB. If we assume that these patterns never appear together in the dataset,
-these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
+AOB. If we assume that these patterns never appear together,
+they cover 14.78\% of buggy files. Kim et al. mentioned that the
 patterns that they use cover almost 30\% of real
@@
 it is hard to believe that the remaining two patterns cover 15\% of buggy files,
-especially 14.78\% is a number we get when we assume that the patterns that we
-detect never appear together. Moreover, the percentage of each pattern is based
+especially considering that 14.78\% is a number that we get when we assume that the patterns never appear together. Moreover, the percentage of each pattern is based
 on imprecise approximation which is likely to represent an upper bound rather
@@
 \section{Conclusions}
-The findings of our study provide a set of useful guidelines for automatic
-program repair tools with which their search for a patch can be now improved by
-having the knowledge of how likely it is to replace a faulty statement by the
-different kinds of statements available.
-\todo{Expand to include summary of actual conclusions}
+We have characterized bug fixing changes in Java.
+On average, a bug fixing revision changes 11.3 files and often introduces new
+fields and methods. We have also showed that 8 out of 10 bug fixing patterns in
+PAR cover only 15\% of bug fixes. Last but not least, we investigated statement
+level mutations and summarized the likelihood of statement insertion, deletion,
+and replacement.
+
+The findings of our study provide a set of useful insights for automatic
+program repair tools in Java. It suggests that patterns in PAR are not enough to
+cover the entirety of bug fixes in Java. Adding more patterns is one solution,
+but may not be a permanent one. Our finding on Java bug fixes characteristic suggests that mutation based program repair may need to add new fields or methods
+to fix bugs in Java and achieve a human-like written patch. A deeper look suggests
+that it can also improve its search for a patch by having the knowledge of how
+likely it is to replace a faulty statement by the different kinds of statements
+available. Overall, our findings demonstrate that our knowledge of bug fixing
+properties in Java is still lacking and therefore more research on it are
+warranted.
 

### 2016-02-19 MSRChallenge2016.tex
Revised Sec.4

@@
 \alignauthor Chu-Pan Wong   \\
+       \affaddr{School of Computer Science}\\
        \affaddr{Carnegie Mellon University}\\
@@
 We begin by broadly characterizing the bug-fixing changes to Java code in our
-dataset. 
-We perform our analysis on the \emph{2015 September/Github} dataset on Boa, 
-which includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
+dataset.  We perform our analysis on the \emph{2015 September/Github} dataset on
+Boa, which includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
 all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
@@
 
-\paragraph{How many files are changed to fix a bug?}
-To answer this question, we identify all the bug fixing revisions in our dataset
-and count the number of changed files. A file was changed if (1) it was a new
-file; (2) or it was modified; (3) or it was deleted. In total, $52,052,571$
-files got changed. Thus, on average each bug fixing revision changes 11.3 files.
-This number is surprisingly high because most automatic program repair
-techniques assume that bugs are local in most cases. There could be several
-reasons behind this number. It could be the case that other software artifacts
-(e.g.  documentation) are updated after bug fixing. It could also be the case
-that bug fixing commit also contains changes that are not related to fixing bug
-(e.g. refactoring, adding new features by creating new files). To better
-understand why so many files are changed, we continue to ask:
+\subsubsection*{How many files are changed to fix a bug?} \vspace{-0.3em}
 
-\paragraph{What are the file types of those changed files?}
-In Boa, each changed file is represented by a \emph{ChangedFile} node, and it
-has a field called \emph{FileKind}, describing the type of each file. As
-mentioned earlier, a \emph{ChangedFile} could be either a new file or an
-existing file (if the bug fixing revision modified or deleted the file).
-Table~\ref{tbl:fileType} shows the file types that Boa could identify. To answer
-this question, we iterate all the changed files in each bug fixing revision and
-count the total number for each file type. Results are shown in
+A file was changed if (1) it was a new file; (2) or it was modified; (3) or it
+was deleted. In total, $52,052,571$ files got changed. Thus, on average each bug
+fixing revision changes $11.3$ files.  This number is surprisingly high because
+most automatic program repair techniques assume that bugs are local in most
+cases. There could be several reasons behind this number. It could be the case
+that other software artifacts (e.g.  documentation) are updated after bug
+fixing. It could also be the case that bug fixing commit also contains changes
+that are not related to fixing bug (e.g. refactoring, adding new features by
+creating new files). To better understand why so many files are changed, we
+continue to ask:
+
+\subsubsection*{What are the file types of those changed files?} \vspace{-0.3em}
+
+To answer this question, we iterate all the changed files in each bug fixing
+revision and count the total number for each file type. Results are shown in
 Table~\ref{tbl:fileType}.
@@
 
-\emph{SOURCE\_JAVA\_ERROR} file kind represents files that Boa failed to parse.
-\emph{JLS2} refers to Java files that are written in all versions of Java
-languages up to and including J2SE 1.4. \emph{JLS3} refers to J2SE 1.5, and JLS4
-refers to J2SE 1.6 and 1.7. Boa documentation does not explicitly explain what
-is \emph{TEXT} and what is \emph{UNKNOWN}. Our assumption is that \emph{TEXT}
-refers to files whose file name ends with ``.txt'', and \emph{UNKNOWN} refers to
-all other kinds of files (e.g. .c file, .cpp files).
+SOURCE\_JAVA\_ERROR file kind represents files that Boa failed to parse. JLS2,
+JLS3, and JLS4 represent Java files written in different J2SE version. Boa
+documentation does not explicitly explain what is TEXT and what is UNKNOWN. From
+Table~\ref{tbl:fileType}, we can see that TEXT files and BINARY files are
+changed least frequently. This is not surprising because TEXT files are usually
+documentation files, and BINARY files should only be changed in rare case (e.g.
+milestone, new release, dependency update). If we consider all 4 kinds of Java
+files as one kind, then on average each bug fixing revision changes $4.47$ Java
+files. But still, it does not conform to our assumption of bug locality. XML
+files in Java projects usually represents build files, thus changing one build
+file after each bug fixing is not surprising.  What surprises us is that UNKNOWN
+files are changed most frequently. Note that all the projects in our dataset are
+Java projects, so it is reasonable to assume that these files are not source
+files that written in other programming languages.  One possible explanation is
+that they are test resources. However, due to the limitations of Boa, we can not
+look into the content of these files.
 
-From Table~\ref{tbl:fileType}, we can see that \emph{TEXT} files and
-\emph{BINARY} files are changed least frequently. This is not surprising because
-\emph{TEXT} files are usually documentation files, and \emph{BINARY} files
-should only be changed in rare case (e.g.  milestone, new release, dependency
-update). If we consider all 4 kinds of Java files as one kind, then on average
-each bug fixing revision changes $4.47$ Java files. But still, it does not
-conform to our assumption of bug locality. \emph{XML} files in Java projects
-usually represents build files, thus changing one build file after each bug
-fixing is not surprising.  What surprises us is that \emph{UNKNOWN} files are
-changed most frequently. Note that all the projects in our dataset are Java
-projects, so it is reasonable to assume that these files are not source files
-that written in other programming languages.  One possible explanation is that
-they are test resources. However, due to the limitations of Boa, we can not look
-into the content of these \emph{UNKNOWN} files.
+It could be the case that among those $4.47$ changed Java files, some of them
+are related to testing, such as modifying the test cases and creating new test
+classes. To better understand what changes are usually made to Java source code
+files, we continue to ask:
 
-Since Boa does not distinguish Java files that related to functionality and Java
-files that related to testing, it could be the case that among those $4.47$
-changed Java files, some of them are related to testing, such as modifying the
-test cases and creating new test classes. To better understand what changes are
-usually made to Java source code files, we continue to ask:
+\subsubsection*{How often do developers introduce new classes, methods, fields,
+	local variables in
+bug fixing commits?} \vspace{-0.3em}
 
-\paragraph{
-How often do developers introduce new classes, methods, fields, variables in
-	bug fixing commits?}
-This research question is interesting because most automatic program repair
-approaches often do not create new classes/methods/fields/variables to fix bugs.
+This question is interesting because most automatic program repair approaches
+often do not create new classes/methods/fields/local variables to fix bugs.
 Most approaches guess and synthesize the patches based on existing source code,
-and direct translations of approaching from C to Java do not naturally consider
+and direct translations of approaches from C to Java do not naturally consider
 object-oriented concerns, like fields or classes.
 
-Table~\ref{tbl:new} shows our analysis results. This table shows that
-introducing new classes and new variables are rare. This is good news for
-automatic program repair approaches. On average, we still have $0.69$ new method
-per bug fix. If we consider the possibility of creating new test method (i.e.
-methods that annotated by @Test if JUnit is used), this number is not that
-scary. However, what surprises us is that $1.32$ fields are created per bug fix.
-This indicates that automatic program repair approaches should pay attention to
-the state of the class when fixing Java programs.
+Table~\ref{tbl:new} shows our analysis results. It shows that introducing new
+classes and new variables are rare, which is good news for automatic program
+repair approaches. On average, we still have $0.69$ new method per bug fix. If
+we consider the possibility of creating new test method (i.e.  methods that
+annotated by @Test if JUnit is used), this number is not that scary. However,
+what surprises us is that $1.32$ fields are created per bug fix.  This indicates
+that automatic program repair approaches should pay attention to the state of
+the class when fixing Java programs.
 
@@
   \end{tabular}
-  \caption{Introducing new classes, methods, fields, variables to fix bugs}
+  \caption{Introducing new classes, methods, fields, local variables to fix bugs}
   \label{tbl:new}
@@
 \subsection{Replacements}
+
 Because direct diffs are difficult to identify, we heuristically approximate the
@@
 per-file level.  For each statement type (as tagged by the Boa infrastructure
-for Java), we process the results as follows: 
-if number of occurrences of one statement type decreased post-fix and the number of
-another type increased, we say that
-the first statement type was replaced by the second statement type for that
-file.
+for Java), we process the results as follows: if number of occurrences of one
+statement type decreased post-fix and the number of another type increased, we
+say that the first statement type was replaced by the second statement type for
+that file. It is important to notice that this analysis doesn't distinguish the
+replacement of the same statement kind, since we are counting the amount of
+appearances of each statement kind.
 
-It is important to notice that this analysis doesn't consider replacing an
-statement kind for a different version of the same statement kind, since it is
-counting the amount of appearances of each statement kind. So, if for example,
-the developer modifies the condition inside of an if statement, the amount of if
-statements in the file will remain the same.
+The numbers in the slots of Table~\ref{tab:likeliness} \todo{shall we add \% in
+this table?}, represent the percentage rate at which the elements of the
+leftmost column were replaced by the elements of the top row. In the first
+column we have the list of statements that are being replaced (faulty statements
+that were removed), and on the top row we have the list of statements for which
+that statement was replaced for (the new statement put instead). For example, if
+we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement
+column) of the data, we have a 0.81, which means that Do statements were
+replaced by Assert statements 0.81\% of the times.
 
-The numbers in the slots of Table~\ref{tab:likeliness}, represent the percentage rate at which the
-elements of the leftmost column were replaced by the elements of the top row. In
-the first column we have the list of statements that are being replaced (faulty
-statements that were removed), and on the top row we have the list of statements
-for which that statement was replaced for (the new statement put instead). For
-example, if we take the intersection of row 5 (DoStatement row) and column 2
-(AsserStatement column) of the data, we have a 0.81, which means that Do statements were replaced by Assert statements 0.81\% of the times.
+Our results show that the most common replacement is replacing Return statement
+with If statement, which showed up in 30,489 files. The second most common
+replacement is replacing an If statement with a Return statement, which had
+28,536 appearances. We found that the most common \emph{Replacer} statement kind
+(the statement kind that most commonly replaces others) is the \textbf{If
+Statement} with 101,366 appearances; and the least common \emph{Replacer} is the
+\textbf{Type Declaration Statement} with 447 appearances.
 
-\subsubsection{Most common replacements}
-Our results show that the most common replacement is when developers remove a
-Return statement and insert an If statement. This showed up in 30,489 files in
-the code database. The second most common replacement is removing an If
-statement and insert a Return statement instead, which had 28,536 appearances in
-the code database. Third to that, is to remove a Return statement and insert a
-Throw statement.
+On the opposite side of the data, the least common replacement was an Assert
+statement replacing a Type Declaration statement, which had zero appearances.
+The second least common replacement were replacing a Do statement with a Type
+Declaration statement and replacing a Label with a Type Declaration, both of
+which had one appearance respectively in our search. The most common $Replacee$
+(the most likely statement kind to be replaced by another statement kind) is the
+\textbf{Return Statement} with 111,938 appearances; and the least common
+$Replacee$ is the \textbf{Type Declaration Statement} with 399 appearances.
 
-\subsubsection{Least common replacements}
-On the opposite side of the data, we can see that the least common replacement
-was an Assert statement replacing a Type Declaration statement, which has zero appearances. The second least common replacement was
-removing a Do statement and insert a Type Declaration statement, with one
-appearance in our search, and on third place, removing a Label and insert
-a Type Declaration Statement had one appearance in our search.
+\subsection{Deletions and Insertions}
 
-\subsection{Deletions and insertions}
+\begin{figure*}[!t] \centering \includegraphics[height=0.3\textheight,
+	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
+	bug fixing revisions add/delete statements of the same kind?}
+	\label{fig:StmtType} \end{figure*}
 
-\begin{figure*}[!t] \centering
-	\includegraphics[height=0.3\textheight, width=1\textwidth]{StmtType} \caption{For each kind
-	of statement, how many bug fixing revisions add/delete statements of the
-same kind?} \label{fig:StmtType} \end{figure*}
-\todo{I'm not sure the percentages in Figure~\ref{fig:StmtType} are visible, maybe moving the numbers so they don't overlap with the bars?}
 For each bug fixing revision $r$ and each statement kind $k$, we count how many
@@
 
-From Figure~\ref{fig:StmtType} \todo{fix the small fonts in this graph}, we can
-see that expression, if, return, for and try catch statements are added most
-often. On the other hand, the same types of statements are also deleted most
-often. This finding indicates that most bugs were fixed by changing the control
-flow of the program using if, return, for, while, and try catch statements.
-
-For each bug fixing revision, the results discussed above consider both newly
-added files and existing files. Since most automatic program repair approaches
-do not generate new files to fix bugs, the rest of this section only considers
-files that were already in the repositories when developers fixed bugs. Our
-analysis shows that there are 46,301,429 of them.
-
-We found that the most common $Replacer$ statement kind (the statement
-kind that most commonly replaces others) is the \textbf{If Statement} with
-101,366 appearances; and the least common $Replacer$, is the \textbf{Type Declaration
-  Statement} with 447 appearances.
-
-The most common $Replacee$ (the most likely statement kind to be replaced
-by another statement kind) is the \textbf{Return Statement} with 111,938
-appearances; and the least common $Replacee$ is the \textbf{Type Declaration Statement}
-with 399 appearances.
+From Figure~\ref{fig:StmtType}, we can see that, expression, if, return, for and
+try catch statements are added most often. Meanwhile, the same types of
+statements are also deleted most often. This finding indicates that most bugs
+were fixed by changing the control flow of the program.
 
 \subsection{Applicability to Automatic Error Repair}
+
 This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
-first find a faulty statement using several different fault localization
+tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012} first
+find a faulty statement using several different fault localization
 techniques~\cite{fry2010}, and once they have that faulty statement, they apply
@@
 to replace an statement for another without looking at the kinds of statements
-being replaced.
-
-With this study, we are able to make a more accurate guess, when having a known
-faulty statement, of which statements more commonly replace that faulty one to build a successful patch based on the data from Table~\ref{tab:likeliness}.
-Similarly with Figure~\ref{fig:StmtType}, we can have an informed guess of how often programmers insert or delete that particular kind of statement.
+being replaced. With this study, we are able to make a more accurate guess based
+on the phenomenon we observed from Table~\ref{tab:likeliness} and
+Figure~\ref{fig:StmtType}.
 
 For example, if we are fixing a Java program, and we have a faulty statement
-that happens to be a For Statement.
-Then we can look for the most likely statements to replace a For Statement (row 6): If statement (22.89\% likeliness), Return statement (21.08\%), and a While statement (13.79\% of likeliness to replace a For Statement).
-We also know that there is a 7.9\% of cases in which human programmers deleted this kind of statement, and in 10.6\% of the cases, a For statement was added to patch a bug.
-This
-way we provide guidelines to
-the automatic bug repair approaches to consider this on their effort to find a
-patch.
+that happens to be a For Statement. Then we can look for the most likely
+statements to replace a For Statement (row 6): If statement (22.89\%
+likeliness), Return statement (21.08\%), and a While statement (13.79\% of
+likeliness to replace a For Statement). We also know that there is a 7.9\% of
+cases in which human programmers deleted this kind of statement, and in 10.6\%
+of the cases, a For statement was added to patch a bug. This way we provide
+guidelines to the automatic bug repair approaches to consider this on their
+effort to find a patch.
 
@@
 on Boa to identify bug fixing revisions, but it is unclear whether those
-identified revisions are actually related to bug fixing. Chances are that there
-exist some other bug fixing revisions, but Boa could not identify them. It is
-also possible that bug fixing revisions identified by Boa actually include other
-code changes, such as implementing new features, refactoring the code base.
-After all, identifying bug fixing revisions from revision history is still an
-open problem. Another big limitation of Boa is that there is no easy to get a
-precise statement-level diff between two revisions. Thus, our template matching
-and analysis of code changes (by counting each statement kind) could be
-inaccurate. However, our results should provide upper bounds for the questions
-we investigated.
+identified revisions are actually related to bug fixing. After all, identifying
+bug fixing revisions from revision history is still an open problem. Another big
+limitation of Boa is that there is no easy way to get a precise statement-level
+diff between two revisions. Thus, our template matching and analysis of code
+changes (by counting each statement kind) could be inaccurate. However, our
+results should provide upper bounds for the questions we investigated.
 

### 2016-02-19 MSRChallenge2016.tex
shorten author info

@@
 
-\numberofauthors{3} %  in this sample file, there are a *total*
+\numberofauthors{1} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \alignauthor
-Mauricio Soto\\
-       \affaddr{School of Computer Science}\\
-       \affaddr{Carnegie Mellon University}\\
-       \affaddr{Pittsburgh, PA}\\
-       \email{mauriciosoto@cmu.edu}
-       % 3rd. author
-\alignauthor Ferdian Thung\\
-       \affaddr{Singapore Management University}\\
-       \affaddr{Singapore}\\
-       \email{ferdiant.2013@smu.edu.sg}
-% 2nd. author
-\alignauthor Chu-Pan Wong   \\
-       \affaddr{School of Computer Science}\\
-       \affaddr{Carnegie Mellon University}\\
-       \affaddr{Pittsburgh, PA}\\
-       \email{chupanw@cs.cmu.edu}       
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor
-Claire Le Goues\\
-       \affaddr{School of Computer Science}\\
-       \affaddr{Carnegie Mellon University}\\
-       \affaddr{Pittsburgh, PA}\\
-       \email{clegoues@cs.cmu.edu}
-% 5th. author
-\alignauthor
-David Lo\\
-\affaddr{Singapore Management University}\\
-\affaddr{Singapore}\\
-\email{davidlo@smu.edu.sg}       
+Mauricio Soto$^1$, Ferdian Thung$^2$, Chu-Pan Wong$^1$, Claire Le Goues$^1$, and David Lo$^2$\\
+       \affaddr{$^1$School of Computer Science, Carnegie Mellon University, Pittsburgh, PA\\
+       $^2$Singapore Management University, Singapore}\\
+       \email{mauriciosoto@cmu.edu, \{ferdiant.2013,davidlo\}@smu.edu.sg, \{chupanw,clegoues\}@cs.cmu.edu} 
 }

### 2016-02-19 MSRChallenge2016.tex
intro, related work

--- 2016-02-19 MSRChallenge2016.tex
@@
 \begin{abstract}
-  Many implementations of recent work to automatically repair bugs in software
-  target programs written in C. Work that targets Java often begins from, or at
+  Many implementations of research techniques that automatically repair software
+  bugs target programs written in C. Work that targets Java often begins from, or at
   least compares to, direct translations of such techniques to a Java context.
@@
   studied and understood if existing approaches are to be profitably translated
-  from one to another.  We conducted a large-scale study of bug-fixing commits
+  between them.  We conducted a large-scale study of bug-fixing commits
   to Java projects, focusing on assumptions underlying common
-  search-based repair approaches.  We make a number of observations that can be
-  leveraged to guide automatic software repair to target Java specifically,
+  search-based repair approaches.  We make observations that can be
+  leveraged to guide high quality automatic software repair to target Java specifically,
   including common and uncommon statement replacements as conducted by human
   developers and the applicability of previously-proposed patch construction
-  operators in the Java context.  We anticipate that these observations can
-  inform more effective patch construction techniques for Java, both in raw
-  numbers of bugs fixed and the usability and maintainability of the resulting
-  patches. 
+  operators in the Java context. 
 \end{abstract}
@@
 
-Research in automatic bug repair seeks to develop techniques that can
-automatically construct patches to repair software bugs, which are prevalent in
-practice. There has been considerable attention paid to this problem in recent
-years~\cite{kim2013,weimer2009,legoues2012,pan2009,so,many,more}.
-Mutation-based, or generate-and-validate approaches, typically operate by
-generating a large number of candidate patches using a pre-defined set of
-mutation operators, and then validating their correctness with respect to a set
-of test cases.  These mutation operators range from simple, coarse granularity
-statement-level mutations~\cite{examples} to human-constructed templates learned
-from a large corpus of previous human bug-fixing commits~\cite{kim2013}.
+There has been considerable attention paid to the problem of automatic
+program repair in recent
+years~\cite{kim2013,legoues2012,pan2009,Weimer13, Qi13,
+  Mechtaev15,prophet}, among many others),
+%
+One broad class of techniques in this space take a generate-and-validate
+approach, which involves generating a large number of candidate patches using a
+pre-defined set of mutation operators, and then validating correctness with
+respect to a set of test cases.  Mutation operators range from simple, coarse
+granularity statement-level mutations to human-constructed templates learned
+from a large corpus of previous human bug-fixing commits.
 
-A considerable proportion of this previous work is implemented to target
-programs written in C, with only limited attention paid to programs in other
-languages, like Java~\cite{kim2013}.  At least partially as a result,
-researchers targeting Java must either start from or at least compare against
-imperfect baselines, that is, Java-based implementations of techniques
-originally implemented for C~\cite{nopol}. %  Even PAR~\cite{kim2013}, perhaps the
+A considerable proportion of this works targets programs written in C.
+Researchers targeting Java often start from or compare against imperfect
+baselines, that is, Java-based implementations of techniques originally
+implemented for C~\cite{nopol,kim2013}. % Even PAR~\cite{kim2013}, perhaps the
 % best-known previously-proposed Java-based program repair technique, both starts
@@
 % targets the C programming language.  
-This C focus extends to empirical studies
-of bug fixing practice, used to inform research questions in automatic
-repair~\cite{zhong2015}.
-
-This is an oversight, because, to put it simply: Java and C are very different
-languages.  Consider GenProg~\cite{genprog,cites}, a well-known technique in
-this space: GenProg uses a genetic programming heuristic to combine
-statement-level mutations into patches to address a particular defect.
-``Statement'' is a well-defined semantic unit in the C programming
-language~\cite{cspec}; to which semantic unit in Java does this concept map?
-Can we learn more
+%
+This is an oversight, because, frankly Java and C are very different languages.
+Consider GenProg~\cite{legoues2012}, which
+combines statement-level mutations into patches to address a particular
+defect. Which ``Statements'' (a semantic unit in C) should be manipulated in Java?
+Can we learn
 intelligent rules to inform candidate modifications
-(cf. Prophet~\cite{rinardPopl2016}, for C)?  What types of
-semantic scoping rules should be used to limit mutations, given the relative
-stringence of the Java compilers?
+(cf. Prophet~\cite{Long2016}, for C)?  What types of semantic scoping
+should limit mutations, given the relative stringence of the Java
+compiler?
 
@@
 of study several million human-made bug fixes from Github. We study broad
-characteristics of changes to fix bugs; the applicability of previously-proposed
-templates to repairing defects in Java programs~\cite{kim2013}; and the nature
-of additions, replacements, of statements in bug-fixing commits. We make
-observations to directly guide future research in automatic repair to Java
+characteristics of these changes; the applicability of previously-proposed
+Java repair templates~\cite{kim2013}; and the nature
+of additions and replacements of Java statements in bug-fixing commits. We make
+observations to directly guide future research in automatic repair of Java
 programs, to increase the success rate of such techniques and the degree to
 which the patches are human-like and therefore more readable and maintainable by
-human developers; this is important, because patch quality is an important
-concern in this research area~\cite{Qi2013}.
+human developers. This is important, because patch quality is an important
+concern in this research area~\cite{Qi15}.
 
@@
 
-A good complement for this paper is~\cite{zhong2015}, where they look for
-additions and deletions in a smaller data set. In this paper, we focus more on
-the replacements, which have been left out of the analysis of~\cite{zhong2015},
-and expand their results of the deletions and additions in a broader
-dataset~\cite{dyer2013}.
-\todo{note to self (CLG) should mention the work from Earl, Yuriy, and others
-  that looked at the redundancy assumption.}
-
-\todo{roadmap}
+\noindent\textbf{Related work.} A good complement to this paper is~\cite{zhong2015}, which studies 
+a similar set of questions in C.  Beyond focusing on Java, we focus more on
+replacements, ommitted from that previous analysis, and otherwise target a
+larger dataset~\cite{dyer2013}.  Barr et al.~\cite{Barr14fse} studied changes to
+Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
+certain types of program repair techniques, an important but orthogonal
+concern. Kim et al.~\cite{kim2013} manually analyze 
+changes to Java programs to inform an automated repair
+technique and show that doing so results in higher-quality repairs; 
+we attempt to validate their learned templates heuristically on
+a different dataset, and take their results as
+motivation for understanding human repairs (as it may result in better patches).
+Long and Rinard learn probabilistic models from bug fixes to C
+code~\cite{Long2016}. Our analysis is significantly less precise and does not
+inform a new repair technique.  Rather, it serves as a starting
+point for research investigating the repair of bugs in Java code.
 

### 2016-02-19 MSRChallenge2016.tex
characteristics, related work

@@
 
-We begin by broadly characterizing the bug-fixing changes to Java code in our
+We begin by broadly characterizing the bug-fixing changes to Java code in the
 dataset.  We perform our analysis on the \emph{2015 September/Github} dataset on
-Boa, which includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
-all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
-revisions.
+Boa, including $7,830,023$ Java projects with $23,229,406$ revisions. Boa
+identifies $4,590,679$ as bug fixing.
 
-\subsubsection*{How many files are changed to fix a bug?} \vspace{-0.3em}
-
-A file was changed if (1) it was a new file; (2) or it was modified; (3) or it
-was deleted. In total, $52,052,571$ files got changed. Thus, on average each bug
-fixing revision changes $11.3$ files.  This number is surprisingly high because
-most automatic program repair techniques assume that bugs are local in most
-cases. There could be several reasons behind this number. It could be the case
-that other software artifacts (e.g.  documentation) are updated after bug
+\vspace{1ex}
+\noindent\textbf{How many files are changed to fix a bug?}
+%
+We consider a file changed if it is new, modified, or
+deleted in a commit. In total, $52,052,571$ files were changed. Thus, on average each bug
+fixing revision changes $11.3$ files.  This is surprisingly high:
+most automatic program repair techniques assume that bugs are local.
+We hypothesize several explanations. Other
+software artifacts (e.g.  documentation) may be updated after bug  
 fixing. It could also be the case that bug fixing commit also contains changes
 that are not related to fixing bug (e.g. refactoring, adding new features by
-creating new files). To better understand why so many files are changed, we
-continue to ask:
+creating new files). To better understand this
+phenomenon, we ask:
 
-\subsubsection*{What are the file types of those changed files?} \vspace{-0.3em}
-
-To answer this question, we iterate all the changed files in each bug fixing
+\vspace{1ex}
+\noindent\textbf{What are the file types of those changed files?}
+%
+To answer this question, we iterate over all changed files in each bug fixing
 revision and count the total number for each file type. Results are shown in
@@
 \centering
-  \begin{tabular}{| c | r | r |}
-  \hline
-  File Kind & Total Number & Average \\ \hline \hline
-  BINARY & 752,945 & 0.16 \\ \hline
-  SOURCE\_JAVA\_ERROR & 2,073,558 & 0.45 \\ \hline
-  SOURCE\_JAVA\_JLS2 & 2,607,413 & 0.57 \\ \hline
-  SOURCE\_JAVA\_JLS3 & 15,748,967 & 3.43 \\ \hline
-  SOURCE\_JAVA\_JLS4 & 83,798 & 0.02 \\ \hline
-  TEXT & 541,023 & 0.12 \\ \hline
-  XML & 6,818,299 & 1.49 \\ \hline
-  UNKNOWN & 23,426,568 & 5.10 \\ \hline
+  \begin{tabular}{ l | r  r }
+  \toprule
+  File Kind & Total & Average \\ 
+  \midrule
+  Binary & 752,945 & 0.16 \\ 
+  Java (ERROR) & 2,073,558 & 0.45 \\ 
+  Java (JLS2) & 2,607,413 & 0.57 \\ 
+  Java (JLS3) & 15,748,967 & 3.43 \\
+  Java (JLS4)  & 83,798 & 0.02 \\ 
+  Text & 541,023 & 0.12 \\ 
+  XML & 6,818,299 & 1.49 \\ 
+  UNKNOWN & 23,426,568 & 5.10 \\ 
   \end{tabular}
@@
 
-SOURCE\_JAVA\_ERROR file kind represents files that Boa failed to parse. JLS2,
-JLS3, and JLS4 represent Java files written in different J2SE version. Boa
-documentation does not explicitly explain what is TEXT and what is UNKNOWN. From
-Table~\ref{tbl:fileType}, we can see that TEXT files and BINARY files are
-changed least frequently. This is not surprising because TEXT files are usually
-documentation files, and BINARY files should only be changed in rare case (e.g.
-milestone, new release, dependency update). If we consider all 4 kinds of Java
-files as one kind, then on average each bug fixing revision changes $4.47$ Java
-files. But still, it does not conform to our assumption of bug locality. XML
-files in Java projects usually represents build files, thus changing one build
-file after each bug fixing is not surprising.  What surprises us is that UNKNOWN
-files are changed most frequently. Note that all the projects in our dataset are
-Java projects, so it is reasonable to assume that these files are not source
-files that written in other programming languages.  One possible explanation is
+JAVA (ERROR) files are those that Boa failed to parse. JLS2,
+JLS3, and JLS4 represent Java files written in different J2SE versions. From
+Table~\ref{tbl:fileType}, we see that Text and Binary files are
+changed least frequently. This is unsurprising, since text are often
+documentation files, and binaries should only be changed rarely. If we consider all 4 kinds of Java
+files as one kind, on average, each bug fixing revision changes $4.47$ Java
+files. This still does not conform to our assumption of bug locality. XML
+files in Java projects usually represents build files; changing a build
+file is unsurprising.  Rather more surprising is how frequently UNKNOWN files
+are changed. Given that all the projects are Java projects, 
+it is unclear whether these are written in other proramming
+languages; One possibility is
 that they are test resources. However, due to the limitations of Boa, we can not
 look into the content of these files. 
+\todo{Possibly mention median.} 
+To better understand what changes are usually made to Java source code
+files, we next ask:
 
-It could be the case that among those $4.47$ changed Java files, some of them
-are related to testing, such as modifying the test cases and creating new test
-classes. To better understand what changes are usually made to Java source code
-files, we continue to ask:
-
-\subsubsection*{How often do developers introduce new classes, methods, fields,
+\vspace{1ex}
+\noindent\textbf{How often do developers introduce new classes, methods, fields,
 	local variables in
-bug fixing commits?} \vspace{-0.3em}
-
+bug fixing commits?} 
+%
 This question is interesting because most automatic program repair approaches
-often do not create new classes/methods/fields/local variables to fix bugs.
+often do not create new methods or variables to fix bugs in C.
 Most approaches guess and synthesize the patches based on existing source code,
@@
 
-Table~\ref{tbl:new} shows our analysis results. It shows that introducing new
-classes and new variables are rare, which is good news for automatic program
-repair approaches. On average, we still have $0.69$ new method per bug fix. If
-we consider the possibility of creating new test method (i.e.  methods that
-annotated by @Test if JUnit is used), this number is not that scary. However,
+Table~\ref{tbl:new} shows that introducing new
+classes and new variables is rare. On average, we still have $0.69$ new methods
+per bug fix. These methods naturally contain new test methods (annotated by
+@Test, for example), which is not too alarming. However,
 what surprises us is that $1.32$ fields are created per bug fix.  This indicates
@@
 \centering
-  \begin{tabular}{| c | r | r |}
-  \hline
-  Introducing & Total Number & Average \\ \hline \hline
-  Class & 729,201 & 0.16 \\ \hline
-  Methods & 3,186,867 & 0.69 \\ \hline
-  Fields & 6,076,646 & 1.32 \\ \hline
-  Variables & 924,259 & 0.2 \\ \hline
+  \begin{tabular}{l | r  r }
+  \toprule
+  Introducing & Total Number & Average \\ \midrule
+  Class & 729,201 & 0.16 \\ 
+  Methods & 3,186,867 & 0.69 \\ 
+  Fields & 6,076,646 & 1.32 \\ 
+  Variables & 924,259 & 0.2 \\ 
   \end{tabular}
@@
 This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012} first
+tools for automatic software repair~\cite{kim2013,legoues2012} first
 find a faulty statement using several different fault localization

### 2016-02-19 MSRChallenge2016.tex
through par approach

@@
 software artifacts (e.g.  documentation) may be updated after bug  
-fixing. It could also be the case that bug fixing commit also contains changes
-that are not related to fixing bug (e.g. refactoring, adding new features by
+fixing, or fixing commits may contain changes
+unrelated to fixing bug (e.g. refactoring, adding new features by
 creating new files). To better understand this
@@
   UNKNOWN & 23,426,568 & 5.10 \\ 
+\bottomrule
   \end{tabular}
@@
   Variables & 924,259 & 0.2 \\ 
+\bottomrule
   \end{tabular}
@@
 
-\section{PAR Bug Fixing Patterns}\label{sec:method}
+\section{Bug Fixing Patterns}\label{sec:method}
 
-Par is a well-known technique for patch generation that 
-On the other hand, some approaches~\cite{kim2013} searches for specific patterns
+One of the best-known program repair techniques to target Java is
+PAR~\cite{kim2013}.  Par searches for specific patterns
 and modifies java code according to predefined templates, constructed by humans
-to cover a large set of bug fixes from an existing corpus.  As one of the only
-techniques to directly target Java, it is an important source of possible
+to cover a large set of bug fixes from an existing corpus.  Par serves as an
+important source of possible 
 mutations to study to inform future directions. 
 We therefore search for and analyze most of the bug fixing patterns proposed by
-Kim et al.~\cite{kim2013} and assess their prevalence on this distinct
-dataset by using Boa's language infrastructure~\cite{dyer2013} to identify the patterns
-in the commits in the dataset.
+Kim et al. and estimate their prevalence in this
+dataset.
 
@@
 
-Boa's capabilities are powerful, but are limited in the precision it enables in
-our detection of these patterns. For example, it is unable to directly perform a
+Boa's capabilities are powerful, butlimited in the precision it enables in
+our detection of Par bug-fixing patterns. For example, it is unable to directly perform a
 diff between two file versions. Thus, rather than finding the exact count of
-bug fixing patterns, we will find an approximate count by processing pre- and
+bug fixing patterns, we find an approximate count by processing pre- and
 post- fix files separately.  Additionally, there are
@@
 Boa, as we describe below. 
-
+%
 The patterns we search for are as follows, including our mechanism for
@@
 \vspace{1ex}
-\noindent {\bf Altering method parameters (AMP)}.  This pattern changes the
-input for method parameters.  {\bf Example:} obj.method(v1,v2) $\rightarrow$
-obj.method(v1,v3). To detect this pattern, for both pre-fix and post-fix version
-of a buggy file, we create a custom method call signature. This signature
-contains method name, literal parameter, and variable parameter. we consider
-parameter containing custom expression as OTHER. This is due to inexistence of
-function that can print Abstract Syntax Tree (AST) back to source code in
-Boa. We discard method signatures that appear both in pre-fix and post-fix
-version. We then find whether there exists method with the same name and the
-same number of parameters, but different parameter signatures in pre-fix and
-post-fix version. If it exists, we consider that AMP pattern is found.
+\noindent {\bf Altering method parameters (AMP)}.  This pattern changes 
+input method parameters. %(\texttt{obj.method(v1,v2) $\rightarrow$
+%obj.method(v1,v3)}). 
+To detect this pattern, for both pre-fix and post-fix version
+of a buggy file, we create a custom method call signature that
+contains the name, literal parameters, and variable parameters (more complex
+expressions are listed as OTHER).
+%  This is due to inexistence of
+% function that can print Abstract Syntax Tree (AST) back to source code in
+% Boa. 
+We discard method signatures that appear both in pre-fix and post-fix
+versions, and then identify methods with the same name and the
+same number of parameters, but different parameter signatures in pre- and
+post-fix versions.% If it exists, we consider that AMP pattern is found.
 
@@
 \noindent {\bf Calling another method with the same parameters (MSM)}.  This
-pattern changes a method name.  {\bf Example:} obj.method1(param) $\rightarrow$
-obj.method2(param).  To detect this pattern, we create method signature similar
-like when detecting AMP pattern. This time, we find whether there exists method
-with the exact same parameter signature but different name in pre-fix and
-post-fix version. If it exists, we consider that MSM pattern is found.
+pattern changes a method name. % (\texttt{obj.method1(param) $\rightarrow$
+%obj.method2(param)}).  
+To detect this pattern, we create method signature similar
+to the above for the AMP pattern, looking for methods
+with the exact same parameter signature but different names in pre- and
+post-fix versions. %If it exists, we consider that MSM pattern is found.
 
@@
 {\bf Calling another overloaded method with one more parameter (COM)}. This
-pattern adds one more parameter to a method. 
-	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2).
-  To detect COM pattern, we create method signature similar like when detecting
-  AMP and COM pattern. This time, we find whether there exists method with
-  the same name, but the number of parameters in pre-fix and post-fix version
-  differs by one. If it exists, we consider that COM pattern is found.
+pattern adds one more parameter to a method. %(\texttt{obj.method(v1) $\rightarrow$ obj.method(v1,v2)}).
+We create method signature similar to the above, seeking methods with
+  the same name, one more parameter in the post-fix version.
 
@@
  {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
-	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0).
+%(e.g., \texttt{if(a != b) $\rightarrow$ if(a != b \&\& c == 0)}).
   To detect CBC pattern, we count the number of { \em logical and} and {\em
-    logical or} inside if conditional expression for both pre-fix and post-fix
-  version. we assume that the addition/removal of logical operators indicate
-  addition/removal of condition. If there is a larger count in post-fix version, we consider that CBC pattern is found.
+    logical or} inside if conditional expression sfor both pre-fix and post-fix
+  version. We assume that the addition/removal of logical operators indicate
+  addition/removal of condition. If there is a larger count in post-fix version,
+  we consider the CBC pattern is found.
 
@@
 \noindent
- {\bf Initializing an object (IAO)}. This pattern adds a initialization to object declaration.
-  To detect IAO pattern, we count the number of NEW expression in variable
-  declaration for both pre-fix and post-fix version. If there is a larger count in post-fix version, we consider that IAO pattern
-  is found.
-	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type().
+{\bf Initializing an object (IAO)}. This pattern adds a initialization to object
+declaration.  We count the number of NEW expressions in variable declarations
+for both pre- and post-fix versions. If there is a larger count in post-fix
+version, we consider that IAO pattern is found.
 
@@
  {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
-    object is null or not in order to prevent unexpected state.
-	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
-  To detect ANC pattern, we count the number of if conditional expression that
+    object is null.
+%	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
+  To detect ANC pattern, we count the number of if conditional expressions that
   contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
   version. If there is a larger count in post-fix version,
-  we consider that ANC pattern is found.
+  we consider that ANC pattern found.
 
@@
     index is within bound right before the index is used.
-	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
-  To detect AOB pattern, we count the number of if conditional expression that
+%	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
+ We count the number of if conditional expression that
   contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
@@
     collection index is within bound before it is used.
-	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
 To detect COB pattern, we count the number of if conditional expression that
@@
 post-fix version. If there are count differences between pre-fix and post-fix
-version, we consider that COB pattern is found.
+version, we consider the COB pattern found.
 
-\vspace{1ex} The above patterns only cover 8 out of 10 bug fixing patterns in
-PAR. The other two patterns are: (1) checking that an object is an instance of a
+\vspace{1ex} The above patterns cover 8 out of 10 bug fixing patterns in
+PAR. The other two patterns are (1) checking that an object is an instance of a
 target class before casting it; and (2) replacing expression in an if condition
 by another expression in the same scope. Pattern (1) cannot be analyzed because
-Boa does not support {\em instanceof} expression. Similarly, pattern (2)
+Boa does not support the {\em instanceof} expression. Pattern (2)
 requires us to track scope between pre-fix and post-fix version, which is not
-supported by Boa. Implementing them ourselves might be possible, but it might
-require too much effort than necessary. We speculate that investigating 8 out of
-10 patterns should give us a good idea on how common the patterns actually are.
+easily supported by Boa.  Investigating 8 out of the
+10 patterns should still provide a good idea on how common the patterns actually are.
 

### 2016-02-19 MSRChallenge2016.tex
half a column over

@@
 program repair in recent
-years~\cite{kim2013,legoues2012,pan2009,Weimer13, Qi13,
+years~\cite{kim2013,legoues2012,pan2009,
   Mechtaev15,prophet}, among many others),
@@
 
-\noindent\textbf{Related work.} A good complement to this paper is~\cite{zhong2015}, which studies 
+\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
 a similar set of questions in C.  Beyond focusing on Java, we focus more on
-replacements, ommitted from that previous analysis, and otherwise target a
+replacements, ommitted from that previous analysis, and target a
 larger dataset~\cite{dyer2013}.  Barr et al.~\cite{Barr14fse} studied changes to
 Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
-certain types of program repair techniques, an important but orthogonal
+certain types of program repair, an important but orthogonal
 concern. Kim et al.~\cite{kim2013} manually analyze 
@@
 technique and show that doing so results in higher-quality repairs; 
-we attempt to validate their learned templates heuristically on
+we attempt to validate their templates heuristically on
 a different dataset, and take their results as
@@
 contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
-post-fix version. If there are count differences between pre-fix and post-fix
+post-fix version. If the count is different between pre- and post-fix
 version, we consider the COB pattern found.
@@
 
+Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
+Java dataset. The most common pattern we observed is CBC; and the least common
+pattern is AOB. If we assume that these patterns never appear together, they
+cover 14.78\% of buggy files. Kim et al. mentioned that the patterns that they
+use cover almost 30\% of real patches~\cite{kim2013}. Although we only detect 8
+out of 10 bug fixing patterns, it is unlikely the final two will cover the
+difference. Moreover, our detection is imprecise, and likely represents an upper
+bound;  This suggests that common bug fixing patterns might not generalize
+beyond an initial dataset, and that more work remains to identify a sufficiently
+expressive set of mutations for high-quality automated repair of Java.
+
+\section{Statement-level mutations}
 \begin{table*}
@@
 
-After running the bug pattern detection approach on Boa's dataset, we obtained
-the result shown in Table~\ref{tab:freqpattern}. It shows that the
-most common pattern among these patterns is CBC and the least common pattern is
-AOB. If we assume that these patterns never appear together,
-they cover 14.78\% of buggy files. Kim et al. mentioned that the
-patterns that they use cover almost 30\% of real
-patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
-it is hard to believe that the remaining two patterns cover 15\% of buggy files,
-especially considering that 14.78\% is a number that we get when we assume that the patterns never appear together. Moreover, the percentage of each pattern is based
-on imprecise approximation which is likely to represent an upper bound rather
-than a lower bound. This suggests that common bug fixing patterns might not be
-as common as it appeared to be.
+\begin{figure*}[!t] \centering \includegraphics[height=0.3\textheight,
+	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
+	bug fixing revisions add/delete statements of the same kind?}
+	\label{fig:StmtType} \end{figure*}
 
-\section{Statement-level mutations}
 Some automatic program repair approaches mutate source code using predefined
-mutation operators such as addition, deletion and replacement. In
-order to generate patches that make more sense to human developers, it would be
+mutation operators such as addition, deletion and replacement. In order to
+generate patches that make more sense to human developers, it would be
 beneficial to analyze how developers mutate source code to fix bugs.
 
-\subsection{Replacements}
-
+\vspace{1ex}\textbf{Approach.}
 Because direct diffs are difficult to identify, we heuristically approximate the
@@
 many inserted, to roughly characterize the types of replacement that happen at a
-per-file level.  For each statement type (as tagged by the Boa infrastructure
-for Java), we process the results as follows: if number of occurrences of one
-statement type decreased post-fix and the number of another type increased, we
-say that the first statement type was replaced by the second statement type for
-that file. It is important to notice that this analysis doesn't distinguish the
+per-file level.
+%   For each statement type (as tagged by the Boa infrastructure
+% for Java), we process the results as follows: if number of occurrences of one
+% statement type decreased post-fix and the number of another type increased, we
+% say that the first statement type was replaced by the second statement type for
+% that file. 
+Note that this analysis doesn't distinguish the
 replacement of the same statement kind, since we are counting the amount of
@@
 
-The numbers in the slots of Table~\ref{tab:likeliness} \todo{shall we add \% in
-this table?}, represent the percentage rate at which the elements of the
-leftmost column were replaced by the elements of the top row. In the first
-column we have the list of statements that are being replaced (faulty statements
-that were removed), and on the top row we have the list of statements for which
-that statement was replaced for (the new statement put instead). For example, if
-we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement
-column) of the data, we have a 0.81, which means that Do statements were
-replaced by Assert statements 0.81\% of the times.
-
-Our results show that the most common replacement is replacing Return statement
-with If statement, which showed up in 30,489 files. The second most common
-replacement is replacing an If statement with a Return statement, which had
-28,536 appearances. We found that the most common \emph{Replacer} statement kind
-(the statement kind that most commonly replaces others) is the \textbf{If
-Statement} with 101,366 appearances; and the least common \emph{Replacer} is the
-\textbf{Type Declaration Statement} with 447 appearances.
-
-On the opposite side of the data, the least common replacement was an Assert
-statement replacing a Type Declaration statement, which had zero appearances.
-The second least common replacement were replacing a Do statement with a Type
-Declaration statement and replacing a Label with a Type Declaration, both of
-which had one appearance respectively in our search. The most common $Replacee$
-(the most likely statement kind to be replaced by another statement kind) is the
-\textbf{Return Statement} with 111,938 appearances; and the least common
-$Replacee$ is the \textbf{Type Declaration Statement} with 399 appearances.
-
-\subsection{Deletions and Insertions}
-
-\begin{figure*}[!t] \centering \includegraphics[height=0.3\textheight,
-	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
-	bug fixing revisions add/delete statements of the same kind?}
-	\label{fig:StmtType} \end{figure*}
-
+We follow a similar approach to approximate a count of deletions and
+insertions. 
 For each bug fixing revision $r$ and each statement kind $k$, we count how many
@@
 
-From Figure~\ref{fig:StmtType}, we can see that, expression, if, return, for and
-try catch statements are added most often. Meanwhile, the same types of
-statements are also deleted most often. This finding indicates that most bugs
-were fixed by changing the control flow of the program.
+\vspace{1ex}
+\noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
+the replacement likelihood for our dataset 
+(each cell shows the percent of the time that the statement in the \emph{row}
+was replaced by a statement of the type in the \emph{column}). For example, if
+the cell in the DoStatement row (row 5) and AssertStatement column (column 2)
+shows 0.81, meaning that Do statements were
+replaced by Assert statements 0.81\% of the times.
 
-\subsection{Applicability to Automatic Error Repair}
+Additional results (raw numbers not shown) show that the most common replacement
+is replacing Return statement with If statement (appearing in 30,489 files). The
+second most common replacement is replacing an If statement with a Return
+statement, which had 28,536 appearances. 
+By contrast, the least common replacement was an Assert
+statement replacing a Type Declaration statement, which we did not observe. 
+The second least common replacement was a Do statement for a Type
+Declaration or a Label with a Type; we observed these once each.
 
-This study is directly applicable to automatic software repair. Most common
-tools for automatic software repair~\cite{kim2013,legoues2012} first
-find a faulty statement using several different fault localization
-techniques~\cite{fry2010}, and once they have that faulty statement, they apply
-different kinds of edits to it, usually at random. Which makes it equally likely
-to replace an statement for another without looking at the kinds of statements
-being replaced. With this study, we are able to make a more accurate guess based
-on the phenomenon we observed from Table~\ref{tab:likeliness} and
-Figure~\ref{fig:StmtType}.
+The most common
+\emph{replacer} statement kind (the statement kind that most commonly replaces
+others) is the \texttt{If Statement} (101,366 appearances). The least
+common \emph{replacer} is the \texttt{Type Declaration Statement} with 447
+appearances.
+The most common \emph{replacee} was the
+\texttt{Return Statement} with 111,938 appearances; and the least common
+\emph{replacee} was the \texttt{Type Declaration}, with 399 appearances.
 
-For example, if we are fixing a Java program, and we have a faulty statement
-that happens to be a For Statement. Then we can look for the most likely
-statements to replace a For Statement (row 6): If statement (22.89\%
-likeliness), Return statement (21.08\%), and a While statement (13.79\% of
-likeliness to replace a For Statement). We also know that there is a 7.9\% of
-cases in which human programmers deleted this kind of statement, and in 10.6\%
-of the cases, a For statement was added to patch a bug. This way we provide
-guidelines to the automatic bug repair approaches to consider this on their
-effort to find a patch.
+\vspace{1ex}
+\noindent \textbf{Potential deletions and insertions} From Figure~\ref{fig:StmtType}, we
+can see that, expression, if, return, for and try catch statements are added
+most often. Meanwhile, the same types of statements are also deleted most
+often. This finding indicates that most bugs were fixed by changing the control
+flow of the program.
 
-\section{Threats to Validity}
+\section{Discussion}
 
-Since we are using a DSL provided by Boa to implement our analysis, the
-correctness of our analysis depends on our programs as well as Boa itself. To
-prevent errors from our side, we open source our implementation on
-Github~\footnote{\url{https://github.com/}}.\todo{update
-this}
+There exist threats to the validity of our study. Since we are using a DSL
+provided by Boa to implement our analysis, the correctness of our analysis
+depends on our programs as well as Boa itself. To mitigate the risk of errors in
+implementation, we open source our implementation on
+Github~\footnote{\url{https://github.com/}}.\todo{FIX THIS NOW.}  Some threats
+to our study arise from limitations of Boa. For example, we rely on Boa to
+identify bug fixing revisions; however, precisely accomplishing this is an open
+problem. Another big limitation is that Boa does not provide an easy mechanism
+to identify precise, statement-level diffs between revisions. Thus, our template
+matching and analysis of code changes (by counting each statement kind) could be
+inaccurate. However, our results should provide upper bounds.
 
-Some threats to our study are due to the limitation of Boa. For example, we rely
-on Boa to identify bug fixing revisions, but it is unclear whether those
-identified revisions are actually related to bug fixing. After all, identifying
-bug fixing revisions from revision history is still an open problem. Another big
-limitation of Boa is that there is no easy way to get a precise statement-level
-diff between two revisions. Thus, our template matching and analysis of code
-changes (by counting each statement kind) could be inaccurate. However, our
-results should provide upper bounds for the questions we investigated.
+We have characterized bug fixing changes in Java.
+The findings of our study provide a set of useful insights for automatic
+program repair tools in Java. It suggests that patterns proposed by the
+state-of-the-art in generate and validate bug report for Java are not enough to
+cover the entirety of bug fixes in Java. Adding more patterns is one solution,
+but may not be a permanent one. Our finding on Java bug fixes characteristic
+suggests that mutation based program repair may need to add new fields or
+methods to fix bugs in Java and achieve a human-like written patch. A deeper
+look suggests that it can also improve its search for a patch by having the knowledge of how
+likely it is to replace a faulty statement by the different kinds of statements
+available. Overall, our findings motivate additional study of the problem of
+repair in Java, as assumptions that underlie approaches that target C are
+unlikely to translate directly to this domain. 
+% demonstrate that our knowledge of bug fixing
+% properties in Java is still lacking and therefore more research on it are
+% warranted.
 
-\section{Conclusions}
-We have characterized bug fixing changes in Java.
-On average, a bug fixing revision changes 11.3 files and often introduces new
-fields and methods. We have also showed that 8 out of 10 bug fixing patterns in
-PAR cover only 15\% of bug fixes. Last but not least, we investigated statement
-level mutations and summarized the likelihood of statement insertion, deletion,
-and replacement.
+%   We studied the applicability of the state-of-the-art in
+% mutation operators to this dataset, 
+% showing that 8 out of 10 bug fixing patterns in PAR cover only 15\% of bug
+% fixes in this dataset.  Finally, investigated statement level mutations and
+% summarized the likelihood of statement insertion, deletion, and replacement.
+% These results suggest
 
-The findings of our study provide a set of useful insights for automatic
-program repair tools in Java. It suggests that patterns in PAR are not enough to
-cover the entirety of bug fixes in Java. Adding more patterns is one solution,
-but may not be a permanent one. Our finding on Java bug fixes characteristic suggests that mutation based program repair may need to add new fields or methods
-to fix bugs in Java and achieve a human-like written patch. A deeper look suggests
-that it can also improve its search for a patch by having the knowledge of how
-likely it is to replace a faulty statement by the different kinds of statements
-available. Overall, our findings demonstrate that our knowledge of bug fixing
-properties in Java is still lacking and therefore more research on it are
-warranted.
+% This study is directly applicable to automatic software repair. Most common
+% tools for automatic software repair~\cite{kim2013,legoues2012} first localize a
+% defect and then randomly select edits to 
+% find a faulty statement using several different fault localization
+% techniques~\cite{fry2010}, and once they have that faulty statement, they apply
+% different kinds of edits to it, usually at random. Which makes it equally likely
+% to replace an statement for another without looking at the kinds of statements
+% being replaced. With this study, we are able to make a more accurate guess based
+% on the phenomenon we observed from Table~\ref{tab:likeliness} and
+% Figure~\ref{fig:StmtType}.
+
+% For example, if we are fixing a Java program, and we have a faulty statement
+% that happens to be a For Statement. Then we can look for the most likely
+% statements to replace a For Statement (row 6): If statement (22.89\%
+% likeliness), Return statement (21.08\%), and a While statement (13.79\% of
+% likeliness to replace a For Statement). We also know that there is a 7.9\% of
+% cases in which human programmers deleted this kind of statement, and in 10.6\%
+% of the cases, a For statement was added to patch a bug. This way we provide
+% guidelines to the automatic bug repair approaches to consider this on their
+% effort to find a patch.
 

### 2016-02-19 MSRChallenge2016.tex
4 pages!!!

@@
 	\centering
-	\resizebox{\textwidth}{100pt}{
+	\resizebox{17cm}{!}{
 		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
@@
 
-\begin{figure*}[!t] \centering \includegraphics[height=0.3\textheight,
+\begin{figure*}[!t] \centering \includegraphics[height=0.25\textheight,
 	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many

### 2016-02-19 MSRChallenge2016.tex
Ok, now really 4 pages... I didn't see all the new references last time

@@
 years~\cite{kim2013,legoues2012,pan2009,
-  Mechtaev15,prophet}, among many others),
+  Mechtaev15,Long2016}, among many others),
 %
@@
 %
-This is an oversight, because, frankly Java and C are very different languages.
+This is an oversight because Java and C are very different languages.
 Consider GenProg~\cite{legoues2012}, which
@@
 it is unclear whether these are written in other proramming
-languages; One possibility is
-that they are test resources. However, due to the limitations of Boa, we can not
-look into the content of these files. 
-\todo{Possibly mention median.} 
+languages. We hypothesize they might be test resources.
 To better understand what changes are usually made to Java source code
@@
 This question is interesting because most automatic program repair approaches
-often do not create new methods or variables to fix bugs in C.
-Most approaches guess and synthesize the patches based on existing source code,
-and direct translations of approaches from C to Java do not naturally consider
+target C, and do not consider
 object-oriented concerns, like fields or classes.
@@
 
-Boa's capabilities are powerful, butlimited in the precision it enables in
+Boa's capabilities are powerful, but limited in the precision it enables in
 our detection of Par bug-fixing patterns. For example, it is unable to directly perform a
@@
 \vspace{1ex} The above patterns cover 8 out of 10 bug fixing patterns in
-PAR. The other two patterns are (1) checking that an object is an instance of a
-target class before casting it; and (2) replacing expression in an if condition
-by another expression in the same scope. Pattern (1) cannot be analyzed because
-Boa does not support the {\em instanceof} expression. Pattern (2)
-requires us to track scope between pre-fix and post-fix version, which is not
-easily supported by Boa.  Investigating 8 out of the
-10 patterns should still provide a good idea on how common the patterns actually are.
+PAR. The other two patterns are (1) Class Cast Checker (cannot be analyzed because
+Boa does not support the {\em instanceof} expression); and (2) Expression Changer (requires us to track scope between pre-fix and post-fix version; not
+easily supported by Boa). Investigating 8 out of
+10 patterns still shows us how common the patterns actually are.
 
@@
 difference. Moreover, our detection is imprecise, and likely represents an upper
-bound;  This suggests that common bug fixing patterns might not generalize
-beyond an initial dataset, and that more work remains to identify a sufficiently
-expressive set of mutations for high-quality automated repair of Java.
+bound.  This suggests that these fixing patterns might not generalize
+beyond an initial dataset, and that more work remains to categorize the programmer's fixing behavior.
 
@@
 	\centering
-	\resizebox{17cm}{!}{
+	\resizebox{15cm}{!}{
+	%\renewcommand{\arraystretch}{0.9}% Tighter
 		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
@@
 
-\begin{figure*}[!t] \centering \includegraphics[height=0.25\textheight,
+\begin{figure*}[!t] \centering \includegraphics[height=0.23\textheight,
 	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many

### 2016-02-19 MSRChallenge2016.tex
four pages, legible figures

@@
   least compares to, direct translations of such techniques to a Java context.
-  However, Java and C are very different languages, and these differences should be
-  studied and understood if existing approaches are to be profitably translated
-  between them.  We conducted a large-scale study of bug-fixing commits
+  However, Java and C are very different languages, and so Java should be
+  studied to inform understanding of how to translate existing approaches to target it.
+  We conduct a large-scale study of bug-fixing commits
   to Java projects, focusing on assumptions underlying common
@@
 
-There has been considerable attention paid to the problem of automatic
+There has been considerable attention paid to automatic
 program repair in recent
@@
 One broad class of techniques in this space take a generate-and-validate
-approach, which involves generating a large number of candidate patches using a
-pre-defined set of mutation operators, and then validating correctness with
+approach: \emph{generating} a large number of candidate patches using a
+pre-defined set of mutation operators, and then \emph{validating} correctness with
 respect to a set of test cases.  Mutation operators range from simple, coarse
@@
 A considerable proportion of this works targets programs written in C.
-Researchers targeting Java often start from or compare against imperfect
-baselines, that is, Java-based implementations of techniques originally
+Indeed, researchers targeting Java often start from or compare against
+Java-based implementations of techniques originally
 implemented for C~\cite{nopol,kim2013}. % Even PAR~\cite{kim2013}, perhaps the
@@
 
-In this paper, we study bug-fixing commits to Java programs, taking as a subject
-of study several million human-made bug fixes from Github. We study broad
+In this paper, we study bug-fixing commits to Java programs, 
+taken from several million human-made bug fixes from Github. We study broad
 characteristics of these changes; the applicability of previously-proposed
@@
 human developers. This is important, because patch quality is an important
-concern in this research area~\cite{Qi15}.
+concern in this area~\cite{Qi15}.
 
@@
 
+\vspace{1ex}
 \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
-a similar set of questions in C.  Beyond focusing on Java, we focus more on
-replacements, ommitted from that previous analysis, and target a
-larger dataset~\cite{dyer2013}.  Barr et al.~\cite{Barr14fse} studied changes to
+a similar set of questions as we do, for C.  Beyond focusing on Java in a larger dataset~\cite{dyer2013}, we also study
+replacements, ommitted from that analysis.  Barr et al.~\cite{Barr14fse} studied changes to
 Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
-certain types of program repair, an important but orthogonal
+certain types of program repair, an orthogonal
 concern. Kim et al.~\cite{kim2013} manually analyze 
 changes to Java programs to inform an automated repair
-technique and show that doing so results in higher-quality repairs; 
-we attempt to validate their templates heuristically on
-a different dataset, and take their results as
-motivation for understanding human repairs (as it may result in better patches).
+technique, and show that doing so results in higher-quality repairs; 
+we study their templates heuristically on
+a different dataset. Their results motivate
+studies of human repairs, as it may result in better patches.
 Long and Rinard learn probabilistic models from bug fixes to C
 code~\cite{Long2016}. Our analysis is significantly less precise and does not
-inform a new repair technique.  Rather, it serves as a starting
-point for research investigating the repair of bugs in Java code.
+inform a new technique.  Rather, it serves as a starting
+point for research on the repair of Java bugs.
 
@@
 
-We begin by broadly characterizing the bug-fixing changes to Java code in the
-dataset.  We perform our analysis on the \emph{2015 September/Github} dataset on
-Boa, including $7,830,023$ Java projects with $23,229,406$ revisions. Boa
-identifies $4,590,679$ as bug fixing.
+First, we broadly characterize bug-fixing commits to Java code.  In this paper,
+we study the \emph{2015 September/Github} dataset on Boa, including $7,830,023$
+Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
+fixing.
 
@@
 We consider a file changed if it is new, modified, or
-deleted in a commit. In total, $52,052,571$ files were changed. Thus, on average each bug
-fixing revision changes $11.3$ files.  This is surprisingly high:
+deleted in a commit. In total, $52,052,571$ files were changed, an average of 
+$11.3$ files per bug-fixing commit.  This is surprisingly high:
 most automatic program repair techniques assume that bugs are local.
-We hypothesize several explanations. Other
+We hypothesize several explanations: Other
 software artifacts (e.g.  documentation) may be updated after bug  
 fixing, or fixing commits may contain changes
-unrelated to fixing bug (e.g. refactoring, adding new features by
-creating new files). To better understand this
+unrelated to fixing the bug (e.g. refactoring, feature addition). 
+To better understand this
 phenomenon, we ask:
-
-\vspace{1ex}
-\noindent\textbf{What are the file types of those changed files?}
-%
-To answer this question, we iterate over all changed files in each bug fixing
-revision and count the total number for each file type. Results are shown in
-Table~\ref{tbl:fileType}.
 
@@
 \end{table}
-
+\vspace{1ex}
+\noindent\textbf{What are the types of those changed files?}
+%
+To answer this question, we iterate over all changed files in each bug fixing
+revision and count the total number for each file type. Results are shown in
+Table~\ref{tbl:fileType}.
+%
 JAVA (ERROR) files are those that Boa failed to parse. JLS2,
-JLS3, and JLS4 represent Java files written in different J2SE versions. From
-Table~\ref{tbl:fileType}, we see that Text and Binary files are
-changed least frequently. This is unsurprising, since text are often
-documentation files, and binaries should only be changed rarely. If we consider all 4 kinds of Java
+JLS3, and JLS4 represent Java files written in different J2SE versions.  We see that text and Binary files are
+changed least frequently. This is unsurprising, since text files are often
+documentation, and binaries should only be changed rarely. If we consider all 4 kinds of Java
 files as one kind, on average, each bug fixing revision changes $4.47$ Java
 files. This still does not conform to our assumption of bug locality. XML
-files in Java projects usually represents build files; changing a build
+files in Java projects usually represent build files; changing a build
 file is unsurprising.  Rather more surprising is how frequently UNKNOWN files
@@
 languages. We hypothesize they might be test resources.
+\todo{possibly mention median, if Chu Pan gets that information}
 To better understand what changes are usually made to Java source code
@@
 This question is interesting because most automatic program repair approaches
-target C, and do not consider
-object-oriented concerns, like fields or classes.
+do not create methods or variable declarations, nor do most explicitly consider
+object-oriented features, like fields or classes.
 
@@
   \label{tbl:new}
+\vspace{-0.5cm}
 \end{table}
@@
 One of the best-known program repair techniques to target Java is
-PAR~\cite{kim2013}.  Par searches for specific patterns
-and modifies java code according to predefined templates, constructed by humans
-to cover a large set of bug fixes from an existing corpus.  Par serves as an
+PAR~\cite{kim2013}.  PAR
+modifies Java code according to predefined templates, constructed by humans
+to cover a large set of bug fixes from an existing corpus.  These templates provide
 important source of possible 
 mutations to study to inform future directions. 
-We therefore search for and analyze most of the bug fixing patterns proposed by
-Kim et al. and estimate their prevalence in this
+We therefore search for most of the PAR bug fixing patterns,
+estimating their prevalence in this
 dataset.
@@
 
-\subsection{Detecting PAR patterns in Boa}
+\subsection{Detecting PAR templates using Boa}
 
 Boa's capabilities are powerful, but limited in the precision it enables in
-our detection of Par bug-fixing patterns. For example, it is unable to directly perform a
-diff between two file versions. Thus, rather than finding the exact count of
-bug fixing patterns, we find an approximate count by processing pre- and
+our detection of Par bug-fixing patterns. For example, it cannot directly \texttt{diff}
+two files versions. Thus, rather than finding the exact count of
+bug fixing patterns, we approximate by processing pre- and
 post- fix files separately.  Additionally, there are
-two of the originally proposed 10 patterns that cannot be easily detected by
+two of the 10 patterns that cannot be easily detected by
 Boa, as we describe below. 
@@
 The patterns we search for are as follows, including our mechanism for
-detecting them using Boa:
+detecting them:
 
 \vspace{1ex}
-\noindent {\bf Altering method parameters (AMP)}.  This pattern changes 
+\noindent {\bf Altering method parameters (AMP)}.  This template changes 
 input method parameters. %(\texttt{obj.method(v1,v2) $\rightarrow$
 %obj.method(v1,v3)}). 
-To detect this pattern, for both pre-fix and post-fix version
+To detect this pattern, for both pre-fix and post-fix versions
 of a buggy file, we create a custom method call signature that
-contains the name, literal parameters, and variable parameters (more complex
+contains the name, literal parameters, and variable parameters (complex
 expressions are listed as OTHER).
@@
 versions, and then identify methods with the same name and the
-same number of parameters, but different parameter signatures in pre- and
-post-fix versions.% If it exists, we consider that AMP pattern is found.
+same number of parameters, but different signatures between versions.
 
@@
 \noindent {\bf Calling another method with the same parameters (MSM)}.  This
-pattern changes a method name. % (\texttt{obj.method1(param) $\rightarrow$
+template changes a method name. % (\texttt{obj.method1(param) $\rightarrow$
 %obj.method2(param)}).  
-To detect this pattern, we create method signature similar
-to the above for the AMP pattern, looking for methods
+To detect it, we create a method signature similar
+to the above for AMP, looking for methods
 with the exact same parameter signature but different names in pre- and
@@
 {\bf Calling another overloaded method with one more parameter (COM)}. This
-pattern adds one more parameter to a method. %(\texttt{obj.method(v1) $\rightarrow$ obj.method(v1,v2)}).
-We create method signature similar to the above, seeking methods with
+template adds a parameter to a method. %(\texttt{obj.method(v1) $\rightarrow$ obj.method(v1,v2)}).
+We create a method signature similar to the above, seeking methods with
   the same name, one more parameter in the post-fix version.
@@
 \noindent
- {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
+ {\bf Changing a branch condition (CBC)}. This template adds or removes a condition.
 %(e.g., \texttt{if(a != b) $\rightarrow$ if(a != b \&\& c == 0)}).
-  To detect CBC pattern, we count the number of { \em logical and} and {\em
+We count the number of { \em logical and} and {\em
     logical or} inside if conditional expression sfor both pre-fix and post-fix
@@
 \noindent
-{\bf Initializing an object (IAO)}. This pattern adds a initialization to object
+{\bf Initializing an object (IAO)}. This template adds a initialization to object
 declaration.  We count the number of NEW expressions in variable declarations
@@
 \noindent
- {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
+ {\bf Adding a null checker (ANC)}.  This template inserts a condition to check whether an
     object is null.
@@
 bound.  This suggests that these fixing patterns might not generalize
-beyond an initial dataset, and that more work remains to categorize the programmer's fixing behavior.
+beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.
 
@@
 	\centering
-	\resizebox{15cm}{!}{
+	\resizebox{\textwidth}{!}{
 	%\renewcommand{\arraystretch}{0.9}% Tighter
-		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
-			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
-			\\ \hline
+		\begin{tabular}{l|rrrrrrrrrrrrrrr} \toprule
+			&\texttt{Assert}&\texttt{Break}&\texttt{Continue}&\texttt{Do}&\texttt{For}&\texttt{If}&\texttt{Label}&\texttt{Return}&\texttt{Case}&\texttt{Switch}& \texttt{Synch}&\texttt{Throw}&\texttt{Try}&\texttt{TypeDecl}&\texttt{While}
+			\\ \midrule
 
 \texttt{Assert}	&-&7.48&3.76&0.53&8.30&23.05&0.31&20.04&4.90&4.62&1.30&13.50&7.23&0.03&4.95
-\\ \hline
+\\
 \texttt{Break} &1.00&-&4.08&0.60&9.93&26.03&0.13&25.39&2.48&1.57&1.79&8.39&11.73&0.10&6.77
-\\ \hline
+\\
 \texttt{Continue} &1.74&9.42&-&1.28&11.39&18.25&0.35&22.60&3.80&2.85&2.17&8.98&9.42&0.11&7.63
-\\   \hline
+\\
 \texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
-\\ \hline
+\\
 \texttt{For} &0.86&6.28&3.19&0.79&-&22.89&0.09&21.08&5.01&3.34&1.87&10.01&10.71&0.08&13.79
-\\ \hline
+\\
 \texttt{If}&1.64&8.43&2.87&0.60&13.49&-&0.24&26.46&7.45&4.80&2.85&9.89&15.11&0.08&6.11
-\\ \hline
+\\
 \texttt{Label} &1.30&8.33&7.86&1.11&5.18&22.85&-&15.17&3.05&2.04&14.62&10.45&4.16&0.09&3.79
-\\ \hline
+\\
 \texttt{Return} &1.13&9.41&3.11&0.49&13.33&27.24&0.24&-&5.59&3.65&2.55&14.91&12.61&0.12&5.61
-\\ \hline
+\\
 \texttt{Case} &0.78&2.84&2.84&0.39&10.27&31.79&0.16&22.40&-&0.46&2.07&7.37&11.69&0.08&6.87
-\\ \hline
+\\
 \texttt{Switch}&1.14&2.72&3.80&0.55&11.07&34.14&0.13&21.86&0.75&-&1.53&8.65&9.02&0.05&4.58
-\\ \hline
+\\
 \texttt{Synch} &0.80&6.57&2.28&0.43&10.21&24.18&0.05&19.77&6.35&2.07&-&9.16&12.16&0.04&5.93
-\\ \hline
+\\
 \texttt{Throw} &2.11&6.57&2.58&0.48&11.87&18.84&0.17&32.28&4.64&3.30&2.74&-&10.08&0.07&4.27
-\\ \hline
+\\
 \texttt{Try}&0.71&7.41&3.02&0.66&11.73&27.75&0.11&23.24&5.63&2.65&2.58&8.99&-&0.09&5.42
-\\ \hline
+\\
 \texttt{TypeDecl} &0.00&4.51&7.52&1.00&10.28&21.05&0.50&17.79&6.02&1.75&2.01&9.27&11.53&-&6.77
-\\ \hline
+\\
 \texttt{While}& 0.72&8.02&3.82&1.96&23.16&19.78&0.12&16.48&6.56&3.09&1.64&6.81&7.80&0.04&-
-			\\ \hline
+			\\ \bottomrule
 		\end{tabular}
 		}
-		\caption{Likeliness to replace the statement in the first column for the statement in the top row, in Java}\label{tab:likeliness}
+		\caption{Likelihood of replacing a statement type (row) by a statement of
+          another type (column), for Java.}\label{tab:likeliness}
 \end{table*}
 
-\begin{figure*}[!t] \centering \includegraphics[height=0.23\textheight,
-	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
+\begin{figure*}[!t] \centering \includegraphics[width=\textwidth]{StmtType} \caption{For each kind of statement, how many
 	bug fixing revisions add/delete statements of the same kind?}

### 2016-02-19 MSRChallenge2016.tex
and, really, 4 pages

@@
 Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
-Java dataset. The most common pattern we observed is CBC; and the least common
-pattern is AOB. If we assume that these patterns never appear together, they
-cover 14.78\% of buggy files. Kim et al. mentioned that the patterns that they
-use cover almost 30\% of real patches~\cite{kim2013}. Although we only detect 8
+Java dataset. The most common pattern we observed is CBC (changing a branch condition); and the least common
+pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
+cover 14.78\% of buggy files. In the dataset studied by Kim et al., the overall
+10 patterns cover almost 30\% of real patches~\cite{kim2013}. Although we only analyze 8
 out of 10 bug fixing patterns, it is unlikely the final two will cover the
@@
 
-Some automatic program repair approaches mutate source code using predefined
-mutation operators such as addition, deletion and replacement. In order to
-generate patches that make more sense to human developers, it would be
-beneficial to analyze how developers mutate source code to fix bugs.
+Some automatic program repair approaches seek generality by using
+higher-granularity mutation operators such as statement-level addition, deletion and replacement. To
+support the generation of high-quality patches, we 
+next analyze how developers mutate source code to fix bugs at this granularity
+level.
 
-\vspace{1ex}\textbf{Approach.}
-Because direct diffs are difficult to identify, we heuristically approximate the
-extent to which one statement type appears to be ``replaced'' by another across
-this dataset.  To do this, for each modified file, we count the number of
+\subsection{Detection Approach}
+Because direct diffs are difficult to identify on this dataset, we heuristically approximate the
+extent to which one statement type appears to be ``replaced'' by another.
+For each modified file, we count the number of
 appearances of each statement type in the file pre- and post-commit.  We then
@@
 
-\vspace{1ex}
+\subsection{Results}
+
 \noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
@@
 
-There exist threats to the validity of our study. Since we are using a DSL
-provided by Boa to implement our analysis, the correctness of our analysis
-depends on our programs as well as Boa itself. To mitigate the risk of errors in
-implementation, we open source our implementation on
-Github~\footnote{\url{https://github.com/}}.\todo{FIX THIS NOW.}  Some threats
-to our study arise from limitations of Boa. For example, we rely on Boa to
+\noindent\textbf{Threats to validity.} Since we are using a DSL
+provided by Boa, the correctness of our analysis
+depends on both our programs and Boa itself. For example, we rely on Boa to
 identify bug fixing revisions; however, precisely accomplishing this is an open
-problem. Another big limitation is that Boa does not provide an easy mechanism
-to identify precise, statement-level diffs between revisions. Thus, our template
-matching and analysis of code changes (by counting each statement kind) could be
-inaccurate. However, our results should provide upper bounds.
+problem.  To mitigate the risk of errors in
+implementation, we open source our scripts~\footnote{\todo{FIX THIS NOW}}.
+Because Boa does not provide an easy mechanism
+to identify precise, statement-level diffs between revisions, our template
+matching and analysis of code changes (by counting each statement kind) only
+provide estimates of behavior; we consider our results as informative
+approximations.
 
-We have characterized bug fixing changes in Java.
-The findings of our study provide a set of useful insights for automatic
-program repair tools in Java. It suggests that patterns proposed by the
-state-of-the-art in generate and validate bug report for Java are not enough to
-cover the entirety of bug fixes in Java. Adding more patterns is one solution,
-but may not be a permanent one. Our finding on Java bug fixes characteristic
-suggests that mutation based program repair may need to add new fields or
-methods to fix bugs in Java and achieve a human-like written patch. A deeper
-look suggests that it can also improve its search for a patch by having the knowledge of how
-likely it is to replace a faulty statement by the different kinds of statements
-available. Overall, our findings motivate additional study of the problem of
-repair in Java, as assumptions that underlie approaches that target C are
-unlikely to translate directly to this domain. 
+The findings of our study provide useful insights for automatic program repair
+tools in Java. It suggests that patterns proposed by the state-of-the-art in
+generate and validate bug report for Java are insufficient cover the extent of
+bug fixes in our dataset.  Adding more patterns is one solution, but may not be
+a general one.  Our findings further suggest that
+mutation based program repair may need to consider field or method insertion to
+achieve human-comparability in patches.  A deeper look suggests that such
+techniques may benefit from leveraging probabilistic knowledge of what types of
+statements are commonly inserted, deleted, or replaced in Java bug-fixing commits.
+Overall, our findings motivate additional study of 
+repair in Java, as assumptions that underlie approaches that target C seem
+unlikely to translate directly.
+
 % demonstrate that our knowledge of bug fixing

### 2016-02-19 MSRChallenge2016.tex
Added median and github link

@@
 %
-We consider a file changed if it is new, modified, or
-deleted in a commit. In total, $52,052,571$ files were changed, an average of 
-$11.3$ files per bug-fixing commit.  This is surprisingly high:
-most automatic program repair techniques assume that bugs are local.
-We hypothesize several explanations: Other
-software artifacts (e.g.  documentation) may be updated after bug  
-fixing, or fixing commits may contain changes
-unrelated to fixing the bug (e.g. refactoring, feature addition). 
-To better understand this
+
+We consider a file changed if it is new, modified, or deleted in a commit. In
+total, $52,052,571$ files were changed, an average of $11.3$ files per
+bug-fixing commit, and the median number is $2$.  Although the median number
+conforms to our intuition, the average is surprisingly high: most automatic
+program repair techniques assume that bugs are local.  We hypothesize several
+explanations: Other software artifacts (e.g.  documentation) may be updated
+after bug  fixing, or fixing commits may contain changes unrelated to fixing
+the bug (e.g.  refactoring, feature addition).  To better understand this
 phenomenon, we ask:
@@
 %
-JAVA (ERROR) files are those that Boa failed to parse. JLS2,
-JLS3, and JLS4 represent Java files written in different J2SE versions.  We see that text and Binary files are
-changed least frequently. This is unsurprising, since text files are often
-documentation, and binaries should only be changed rarely. If we consider all 4 kinds of Java
-files as one kind, on average, each bug fixing revision changes $4.47$ Java
-files. This still does not conform to our assumption of bug locality. XML
-files in Java projects usually represent build files; changing a build
-file is unsurprising.  Rather more surprising is how frequently UNKNOWN files
-are changed. Given that all the projects are Java projects, 
-it is unclear whether these are written in other proramming
-languages. We hypothesize they might be test resources.
-\todo{possibly mention median, if Chu Pan gets that information}
-To better understand what changes are usually made to Java source code
-files, we next ask:
+
+JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4
+represent Java files written in different J2SE versions.  We see that text and
+Binary files are changed least frequently. This is unsurprising, since text
+files are often documentation, and binaries should be changed rarely. If we
+consider all 4 kinds of Java files as one kind, on average, each bug fixing
+revision changes $4.47$ Java files. This does not conform to our assumption of
+bug locality. XML files in Java projects usually represent build files;
+changing build files is unsurprising.  Rather more surprising is how frequently
+UNKNOWN files are changed. Given that all projects are Java projects, it is
+unclear whether these are written in other programming languages. We
+hypothesize they might be test resources.  To better understand what changes
+are usually made to Java files, we next ask:
 
@@
 \end{table}
-
-% \todo{Is there room/call to include any element of Chu Pan's replacement
-%   analysis in here?}
 
@@
 problem.  To mitigate the risk of errors in
-implementation, we open source our scripts~\footnote{\todo{FIX THIS NOW}}.
+implementation, we open source our scripts~\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
 Because Boa does not provide an easy mechanism

### 2016-02-20 MSRChallenge2016.tex
polishing

@@
 
-\title{A deeper look into bug fixes: Patterns, replacements, deletions, and additions}
+\title{A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions}
 
@@
 years~\cite{kim2013,legoues2012,pan2009,
-  Mechtaev15,Long2016}, among many others),
+  Mechtaev15,Long2016}.
 %
@@
 
-A considerable proportion of this works targets programs written in C.
+A considerable proportion of these works target programs written in C.
 Indeed, researchers targeting Java often start from or compare against
@@
 a similar set of questions as we do, for C.  Beyond focusing on Java in a larger dataset~\cite{dyer2013}, we also study
-replacements, ommitted from that analysis.  Barr et al.~\cite{Barr14fse} studied changes to
+replacements, omitted from that analysis.  Barr et al.~\cite{Barr14fse} studied changes to
 Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
@@
 First, we broadly characterize bug-fixing commits to Java code.  In this paper,
-we study the \emph{2015 September/Github} dataset on Boa, including $7,830,023$
+we study the \emph{September 2015/Github} dataset on Boa, including $7,830,023$
 Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
@@
 represent Java files written in different J2SE versions.  We see that text and
-Binary files are changed least frequently. This is unsurprising, since text
+binary files are changed least frequently. This is unsurprising, since text
 files are often documentation, and binaries should be changed rarely. If we
@@
 Boa's capabilities are powerful, but limited in the precision it enables in
-our detection of Par bug-fixing patterns. For example, it cannot directly \texttt{diff}
+our detection of PAR bug-fixing patterns. For example, it cannot directly \texttt{diff}
 two files versions. Thus, rather than finding the exact count of
 bug fixing patterns, we approximate by processing pre- and
-post- fix files separately.  Additionally, there are
+post-fix files separately.  Additionally, there are
 two of the 10 patterns that cannot be easily detected by
@@
 %obj.method(v1,v3)}). 
-To detect this pattern, for both pre-fix and post-fix versions
+To detect this pattern, for both pre- and post-fix versions
 of a buggy file, we create a custom method call signature that
-contains the name, literal parameters, and variable parameters (complex
-expressions are listed as OTHER).
+contains the name string, literal parameters string, and variable parameters string (complex
+expressions are listed as ``OTHER'' string).
 %  This is due to inexistence of
@@
 % Boa. 
-We discard method signatures that appear both in pre-fix and post-fix
+We discard method signatures that appear both in pre- and post-fix
 versions, and then identify methods with the same name and the
@@
 We create a method signature similar to the above, seeking methods with
-  the same name, one more parameter in the post-fix version.
+  the same name, but with one more parameter in the post-fix version.
 
@@
 \noindent
- {\bf Changing a branch condition (CBC)}. This template adds or removes a condition.
+ {\bf Add or remove a branch condition (ABC)}. This template adds or removes a condition.
 %(e.g., \texttt{if(a != b) $\rightarrow$ if(a != b \&\& c == 0)}).
 We count the number of { \em logical and} and {\em
-    logical or} inside if conditional expression sfor both pre-fix and post-fix
+    logical or} inside if conditional expression for both pre- and post-fix
   version. We assume that the addition/removal of logical operators indicate
-  addition/removal of condition. If there is a larger count in post-fix version,
-  we consider the CBC pattern is found.
+  addition/removal of condition. If there is a count difference between pre- and post-fix version,
+  we consider an instance of the ABC pattern is found.
 
@@
 for both pre- and post-fix versions. If there is a larger count in post-fix
-version, we consider that IAO pattern is found.
+version, we consider that an instance of the IAO pattern is found.
 
@@
   To detect ANC pattern, we count the number of if conditional expressions that
-  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
+  contains {\em !=null} or {\em ==null} for both pre- and post-fix
   version. If there is a larger count in post-fix version,
-  we consider that ANC pattern found.
+  we consider that an instance of the ANC pattern found.
 
@@
  We count the number of if conditional expression that
-  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
-  post-fix version. If there is a larger count in post-fix version, we consider that AOB pattern is found.
+  contains {\em expr<var.length} or {\em var.length>expr} for both pre- and
+  post-fix version. If there is a larger count in post-fix version, we consider that an instance of the AOB pattern is found.
 
@@
 To detect COB pattern, we count the number of if conditional expression that
-contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
-post-fix version. If the count is different between pre- and post-fix
-version, we consider the COB pattern found.
+contains {\em expr<col.size()} or {\em col.size()>expr} for both pre- and
+post-fix version. If the is a larger count in post-fix
+version, we consider that an instance of the COB pattern is found.
 
@@
 PAR. The other two patterns are (1) Class Cast Checker (cannot be analyzed because
-Boa does not support the {\em instanceof} expression); and (2) Expression Changer (requires us to track scope between pre-fix and post-fix version; not
+Boa does not support the {\em instanceof} expression); and (2) Expression Changer (requires us to track scope between pre- and post-fix version; not
 easily supported by Boa). Investigating 8 out of
@@
 		COM Pattern & 270,128 & 0.58\%\\ 
-		CBC Pattern & 1,959,377 & 4.23\%\\  
+		ABC Pattern & 1,959,377 & 4.23\%\\  
 		IAO Pattern & 1,308,006 & 2.82\%\\  
@@
 Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
-Java dataset. The most common pattern we observed is CBC (changing a branch condition); and the least common
+Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
 pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
@@
 out of 10 bug fixing patterns, it is unlikely the final two will cover the
-difference. Moreover, our detection is imprecise, and likely represents an upper
+difference. Moreover, our detection is imprecise, and might represent an upper
 bound.  This suggests that these fixing patterns might not generalize
@@
 
-\begin{figure*}[!t] \centering \includegraphics[width=\textwidth]{StmtType} \caption{For each kind of statement, how many
+\begin{figure*}[!t] \centering \includegraphics[width=\textwidth]{StmtType}
+	\vspace{-0.7cm} \caption{For each kind of statement, how many
 	bug fixing revisions add/delete statements of the same kind?}
@@
 the cell in the DoStatement row (row 5) and AssertStatement column (column 2)
-shows 0.81, meaning that Do statements were
+shows 0.81, it means that Do statements were
 replaced by Assert statements 0.81\% of the times.
@@
 problem.  To mitigate the risk of errors in
-implementation, we open source our scripts~\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
+implementation, we open source our scripts\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
 Because Boa does not provide an easy mechanism

### 2016-03-10 MSRChallenge2016.tex
For Camera ready Changes to address Points 3 and 5

@@
 \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
-a similar set of questions as we do, for C.  Beyond focusing on Java in a larger dataset~\cite{dyer2013}, we also study
-replacements, omitted from that analysis.  Barr et al.~\cite{Barr14fse} studied changes to
+a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories, and we also study
+replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
 Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
@@
 was replaced by a statement of the type in the \emph{column}). For example, if
-the cell in the DoStatement row (row 5) and AssertStatement column (column 2)
+the cell in the Do statement row (row 5) and Assert statement column (column 2)
 shows 0.81, it means that Do statements were
@@
 \emph{replacee} was the \texttt{Type Declaration}, with 399 appearances.
+
+An important study that works as a great complement for this study is~\cite{martinez2013}, in which they discuss a probability distribution for when to apply which kind of edit, meanwhile we go finer grain and discuss a probability distribution of each statement type, once the program has already chosen a kind of edit.
+It is also worth mentioning that this paper has studied 14 repositories with 89,993 versioning transactions, while our study studies 380,125 repositories with 23,229,406 revisions.
 

### 2016-03-10 MSRChallenge2016.tex
small change in phrasing

@@
 \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
-a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories, and we also study
-replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
+a similar set of questions in 5 projects.
+In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more statement types, and we have studied replacements, omitted from Zhong and Su's analysis.
+Barr et al.~\cite{Barr14fse} studied changes to
 Java programs to understand the ``Plastic Surgery Hypothesis'' underlying

### 2016-03-10 MSRChallenge2016.tex
Point 1
Related work (Point 2)

@@
 
-\vspace{1ex}
-\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
-a similar set of questions in 5 projects.
-In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more statement types, and we have studied replacements, omitted from Zhong and Su's analysis.
-Barr et al.~\cite{Barr14fse} studied changes to
-Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
-certain types of program repair, an orthogonal
-concern. Kim et al.~\cite{kim2013} manually analyze 
-changes to Java programs to inform an automated repair
-technique, and show that doing so results in higher-quality repairs; 
-we study their templates heuristically on
-a different dataset. Their results motivate
-studies of human repairs, as it may result in better patches.
-Long and Rinard learn probabilistic models from bug fixes to C
-code~\cite{Long2016}. Our analysis is significantly less precise and does not
-inform a new technique.  Rather, it serves as a starting
-point for research on the repair of Java bugs.
+\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
+a similar set of questions in 5 projects. In this paper we have studied a much
+larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more
+statement types, and we have studied replacements, omitted from Zhong and Su's
+analysis. Similar to our study in Section~\ref{sec:stmtstudy}, researchers have
+studied AST-level changes~\cite{Martinez:2015ez} or line
+changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
+Although granularity differs, our approach is novel with respect to scale of
+analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
+understand the ``Plastic Surgery Hypothesis'' underlying certain types of
+program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
+analyze changes to Java programs to inform an automated repair technique, and
+show that doing so results in higher-quality repairs; we study their templates
+heuristically on a different dataset. Their results motivate studies of human
+repairs, as it may result in better patches.  Long and Rinard learn
+probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
+significantly less precise and does not inform a new technique.  Rather, it
+serves as a starting point for research on the repair of Java bugs.
 
@@
 
-\section{Statement-level mutations}
+\section{Statement-level mutations}\label{sec:stmtstudy}
 \begin{table*}
@@
 
-An important study that works as a great complement for this study is~\cite{martinez2013}, in which they discuss a probability distribution for when to apply which kind of edit, meanwhile we go finer grain and discuss a probability distribution of each statement type, once the program has already chosen a kind of edit.
-It is also worth mentioning that this paper has studied 14 repositories with 89,993 versioning transactions, while our study studies 380,125 repositories with 23,229,406 revisions.
-
 \vspace{1ex}
@@
 flow of the program.
+
+An important study that complements for our study is the repair model approach
+proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, in which they discuss
+a probability distribution for when to apply which kind of edit. Although their
+approach is able to trace more fine-grain AST-level changes, our results are
+consistent with their findings. For example, their empirical
+analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
+and variable declaration statements are added/deleted/updated most often, which
+is also illustrated in Figure~\ref{fig:StmtType} (In Boa, method invocation and
+variable declaration fall into the category of expression). It is also worth
+mentioning that their study covers 14 repositories with 89,993 versioning
+transactions, while our study studies 380,125 repositories with 23,229,406
+revisions.
 

### 2016-03-10 MSRChallenge2016.tex
Slightly revised Discussion
Emphasize that direct translation from C to Java may not work

@@
 out of 10 bug fixing patterns, it is unlikely the final two will cover the
-difference. Moreover, our detection is imprecise, and might represent an upper
-bound.  This suggests that these fixing patterns might not generalize
+difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we are still assuming that the patterns never appear together. 
+%Moreover, our detection is imprecise, and might represent an upper bound. 
+This suggests that these fixing patterns might not generalize
 beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.
@@
 
-The findings of our study provide useful insights for automatic program repair
-tools in Java. It suggests that patterns proposed by the state-of-the-art in
-generate and validate bug report for Java are insufficient cover the extent of
-bug fixes in our dataset.  Adding more patterns is one solution, but may not be
-a general one.  Our findings further suggest that
-mutation based program repair may need to consider field or method insertion to
-achieve human-comparability in patches.  A deeper look suggests that such
-techniques may benefit from leveraging probabilistic knowledge of what types of
-statements are commonly inserted, deleted, or replaced in Java bug-fixing commits.
-Overall, our findings motivate additional study of 
-repair in Java, as assumptions that underlie approaches that target C seem
-unlikely to translate directly.
+\noindent\textbf{Lessons learned.} The findings of our study provide useful
+insights for automatic program repair tools in Java. It suggests that patterns
+proposed by the state-of-the-art approaches for Java are insufficient to cover
+the extent of bug fixes in our dataset.  Adding more patterns is one solution,
+but may not be a general one.  Our findings further suggest that mutation based
+program repair may need to consider field or method insertion to achieve
+human-comparability in patches. This finding indicates that direct translation
+of mutation based approaches from C to Java is not likely to succeed due to the
+different language constructs.  A deeper look suggests that such techniques may
+benefit from leveraging probabilistic knowledge of what types of statements are
+commonly inserted, deleted, or replaced in Java bug-fixing commits. Again, the
+probabilistic knowledge for C is not likely to work for Java program if
+different coding conventions are considered.  Overall, our findings motivate
+additional study of repair in Java, as assumptions that underlie approaches that
+target C seem unlikely to translate directly.
 

### 2016-03-10 MSRChallenge2016.tex
some modification to first page, for length

@@
   Many implementations of research techniques that automatically repair software
-  bugs target programs written in C. Work that targets Java often begins from, or at
-  least compares to, direct translations of such techniques to a Java context.
-  However, Java and C are very different languages, and so Java should be
-  studied to inform understanding of how to translate existing approaches to target it.
+  bugs target programs written in C. Work that targets Java often begins from or
+  compares to, direct translations of such techniques to a Java context.  
+  However, Java and C are very different languages, and Java should be
+  studied to inform the translation of existing approaches to target it.
   We conduct a large-scale study of bug-fixing commits
@@
 
-\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
-a similar set of questions in 5 projects. In this paper we have studied a much
-larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more
-statement types, and we have studied replacements, omitted from Zhong and Su's
-analysis. Similar to our study in Section~\ref{sec:stmtstudy}, researchers have
-studied AST-level changes~\cite{Martinez:2015ez} or line
+\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} ask
+some of the same questions we do, on  5 projects. We study a much
+larger dataset~\cite{dyer2013} with 380,125 repositories; and we look at more
+statement types, as well as replacements. Similar to our study in
+Section~\ref{sec:stmtstudy}, researchers have 
+studied AST-level~\cite{Martinez:2015ez} and line-level
 changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
-Although granularity differs, our approach is novel with respect to scale of
+Although the granularity differs, our approach is also novel with respect to scale of
 analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
@@
 program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
-analyze changes to Java programs to inform an automated repair technique, and
+analyze changes to Java programs to inform automated repair, and
 show that doing so results in higher-quality repairs; we study their templates

### 2016-03-10 MSRChallenge2016.tex
some shortening through page 2

@@
   bugs target programs written in C. Work that targets Java often begins from or
-  compares to, direct translations of such techniques to a Java context.  
+  compares to direct translations of such techniques to a Java context.  
   However, Java and C are very different languages, and Java should be
-  studied to inform the translation of existing approaches to target it.
+  studied to inform the construction of repair approaches to target it.
   We conduct a large-scale study of bug-fixing commits
-  to Java projects, focusing on assumptions underlying common
+  in Java projects, focusing on assumptions underlying common
   search-based repair approaches.  We make observations that can be
   leveraged to guide high quality automatic software repair to target Java specifically,
-  including common and uncommon statement replacements as conducted by human
-  developers and the applicability of previously-proposed patch construction
+  including common and uncommon statement modifications in human patches and the
+  applicability of previously-proposed patch construction 
   operators in the Java context. 
@@
 program repair in recent
-years~\cite{kim2013,legoues2012,pan2009,
-  Mechtaev15,Long2016}.
+years (e.g.,~\cite{kim2013,legoues2012,
+  Mechtaev15,Long2016}).
 %
@@
 %
-
-We consider a file changed if it is new, modified, or deleted in a commit. In
+Most
+program repair techniques assume that bugs are local to only one or two files.
+We consider a file \emph{changed} if it is new, modified, or deleted in a commit. In
 total, $52,052,571$ files were changed, an average of $11.3$ files per
-bug-fixing commit, and the median number is $2$.  Although the median number
-conforms to our intuition, the average is surprisingly high: most automatic
-program repair techniques assume that bugs are local.  We hypothesize several
-explanations: Other software artifacts (e.g.  documentation) may be updated
+bug-fixing commit. The median number of file changed is $2$.  Although the median
+conforms to our intuition, the average is surprisingly high, suggesting a long
+tailed distribution.   We hypothesize that
+other software artifacts (e.g.  documentation) may be updated
 after bug  fixing, or fixing commits may contain changes unrelated to fixing
@@
 \bottomrule
+  \toprule
+  Introducing & Total Number & Average \\ \midrule
+  Class & 729,201 & 0.16 \\ 
+  Methods & 3,186,867 & 0.69 \\ 
+  Fields & 6,076,646 & 1.32 \\ 
+  Variables & 924,259 & 0.2 \\ 
+\bottomrule
   \end{tabular}
-  \caption{File Types of Changed Files}
-  \label{tbl:fileType}
+  \caption{Top: File Types of Changed Files.  Bottom: Introduction of new
+    classes, methods, fields, local variables to fix bugs.   \label{tbl:fileType}\label{tbl:new}}
+\vspace{-0.5cm}
 \end{table}
@@
 %
-To answer this question, we iterate over all changed files in each bug fixing
-revision and count the total number for each file type. Results are shown in
-Table~\ref{tbl:fileType}.
+The top of Table~\ref{tbl:fileType} shows the types of the changed files in the
+Boa dataset. 
+Text and
+binary files are changed least frequently. This is unsurprising, since such
+files are often documentation, and binaries should be changed rarely. 
 %
-
-JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4
-represent Java files written in different J2SE versions.  We see that text and
-binary files are changed least frequently. This is unsurprising, since text
-files are often documentation, and binaries should be changed rarely. If we
-consider all 4 kinds of Java files as one kind, on average, each bug fixing
-revision changes $4.47$ Java files. This does not conform to our assumption of
-bug locality. XML files in Java projects usually represent build files;
+XML files in Java projects usually represent build files;
 changing build files is unsurprising.  Rather more surprising is how frequently
@@
 unclear whether these are written in other programming languages. We
-hypothesize they might be test resources.  To better understand what changes
-are usually made to Java files, we next ask:
+hypothesize they might be test resources.  JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4 are
+Java files in different J2SE versions.  If we group
+all Java types, on average, each bug fixing
+revision changes $4.47$ Java files. This does not conform to our assumption of
+bug locality.  To better understand what changes
+are usually made to those Java files, we next ask:
 
@@
 object-oriented features, like fields or classes. 
-
+%
 Table~\ref{tbl:new} shows that introducing new
-classes and new variables is rare. On average, we still have $0.69$ new methods
-per bug fix. These methods naturally contain new test methods (annotated by
-@Test, for example), which is not too alarming. However,
-what surprises us is that $1.32$ fields are created per bug fix.  This indicates
+classes or variables is rare. On average, we still have $0.69$ new methods
+per bug fix. These methods include new test methods (annotated by
+@Test, for example), which is not too alarming. However, we note
+that $1.32$ fields are created per bug fix, suggesting
 that automatic program repair approaches should pay attention to the state of
 the class when fixing Java programs.
-
-\begin{table}
-\centering
-  \begin{tabular}{l | r  r }
-  \toprule
-  Introducing & Total Number & Average \\ \midrule
-  Class & 729,201 & 0.16 \\ 
-  Methods & 3,186,867 & 0.69 \\ 
-  Fields & 6,076,646 & 1.32 \\ 
-  Variables & 924,259 & 0.2 \\ 
-\bottomrule
-  \end{tabular}
-  \caption{Introducing new classes, methods, fields, local variables to fix bugs}
-  \label{tbl:new}
-\vspace{-0.5cm}
-\end{table}
 
@@
 Boa's capabilities are powerful, but limited in the precision it enables in
-our detection of PAR bug-fixing patterns. For example, it cannot directly \texttt{diff}
-two files versions. Thus, rather than finding the exact count of
+detection of PAR bug-fixing patterns. For example, it cannot directly \texttt{diff}
+two files. Rather than finding exact counts of
 bug fixing patterns, we approximate by processing pre- and
-post-fix files separately.  Additionally, there are
-two of the 10 patterns that cannot be easily detected by
+post-fix files separately.  Additionally, 
+two of the 10 patterns cannot be easily detected by
 Boa, as we describe below. 
 %
-The patterns we search for are as follows, including our mechanism for
-detecting them:
+We search for the following patterns:
 

### 2016-03-11 MSRChallenge2016.tex
boom.  4 pages.

@@
 
-There has been considerable attention paid to automatic
-program repair in recent
-years (e.g.,~\cite{kim2013,legoues2012,
+There has been considerable recent attention paid to automatic
+program repair (e.g.,~\cite{kim2013,legoues2012,
   Mechtaev15,Long2016}).
@@
 studied AST-level~\cite{Martinez:2015ez} and line-level
-changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
+changes~\cite{Asaduzzaman:2013gu} across bug fixing commits.
 Although the granularity differs, our approach is also novel with respect to scale of
@@
   \toprule
-  Introducing & Total Number & Average \\ \midrule
+  Introducing & Total & Average \\ \midrule
   Class & 729,201 & 0.16 \\ 
@@
   Fields & 6,076,646 & 1.32 \\ 
-  Variables & 924,259 & 0.2 \\ 
+  Variables & 924,259 & 0.20 \\ 
 \bottomrule
@@
 
-\vspace{1ex}
+%\vspace{1ex}
 \noindent {\bf Altering method parameters (AMP)}.  This template changes 
@@
 of a buggy file, we create a custom method call signature that
-contains the name string, literal parameters string, and variable parameters string (complex
+contains the name, literal parameters, and variable parameters, all as string (complex
 expressions are listed as ``OTHER'' string).
-%  This is due to inexistence of
-% function that can print Abstract Syntax Tree (AST) back to source code in
-% Boa. 
-We discard method signatures that appear both in pre- and post-fix
-versions, and then identify methods with the same name and the
-same number of parameters, but different signatures between versions.
+We discard signatures that appear both in pre- and post-fix
+versions, and then identify methods with the same name and 
+number of parameters, but different signatures between versions.
 
-\vspace{1ex}
+%\vspace{1ex}
 \noindent {\bf Calling another method with the same parameters (MSM)}.  This
@@
 
-\vspace{1ex}
+%\vspace{1ex}
 \noindent
@@
   version. We assume that the addition/removal of logical operators indicate
-  addition/removal of condition. If there is a count difference between pre- and post-fix version,
+  addition/removal of condition. If there is a difference in count between versions,
   we consider an instance of the ABC pattern is found.
 
-\vspace{1ex}
+%\vspace{1ex}
 \noindent
@@
 
-\vspace{1ex} The above patterns cover 8 out of 10 bug fixing patterns in
-PAR. The other two patterns are (1) Class Cast Checker (cannot be analyzed because
+These patterns cover 8 of the 10 bug fixing patterns in
+PAR. We do not investigate (1) Class Cast Checker (cannot be analyzed because
 Boa does not support the {\em instanceof} expression); and (2) Expression Changer (requires us to track scope between pre- and post-fix version; not
 easily supported by Boa). Investigating 8 out of
-10 patterns still shows us how common the patterns actually are.
+10 patterns provides an informative approximation of their prevalence.
 
@@
 
-Some automatic program repair approaches seek generality by using
+Some automatic repair approaches seek generality by using
 higher-granularity mutation operators such as statement-level addition, deletion and replacement. To
 support the generation of high-quality patches, we 
-next analyze how developers mutate source code to fix bugs at this granularity
+analyze how developers mutate source code to fix bugs at this granularity
 level.
@@
 appearances of each statement kind.
-
-We follow a similar approach to approximate a count of deletions and
+%
+We follow a similar approach to approximately count deletions and
 insertions. 
-For each bug fixing revision $r$ and each statement kind $k$, we count how many
-statements of kind $k$ are there in revision $r$ and $r-1$ ($r-1$ means the
-revision before revision $r$), and then compare the two numbers.
+For each bug fixing revision $r$ and each statement kind $k$, we compare the
+count of statements of kind $k$ in revision $r$ and $r-1$.
 
@@
 (each cell shows the percent of the time that the statement in the \emph{row}
-was replaced by a statement of the type in the \emph{column}). For example, if
-the cell in the Do statement row (row 5) and Assert statement column (column 2)
-shows 0.81, it means that Do statements were
-replaced by Assert statements 0.81\% of the times.
+was replaced by a statement of the type in the \emph{column}). For example, 
+the corresponding to the $\mathtt{Do}$ row (row 5) and $\mathtt{Assert}$ column (column 2)
+shows 0.81, indicating that $\mathtt{Do}$ statements were
+replaced by $\mathtt{Assert}$ statements 0.81\% of the times.
 
-Additional results (raw numbers not shown) show that the most common replacement
-is replacing Return statement with If statement (appearing in 30,489 files). The
-second most common replacement is replacing an If statement with a Return
-statement, which had 28,536 appearances. 
-By contrast, the least common replacement was an Assert
-statement replacing a Type Declaration statement, which we did not observe. 
-The second least common replacement was a Do statement for a Type
-Declaration or a Label with a Type; we observed these once each.
+Additional analysis (raw numbers not shown) show that the most common replacement
+replaces $\mathtt{Return}$ statements with $\mathtt{If}$ statements (in 30,489 files). The
+second most common replacement replaces an $\mathtt{If}$ statement with a $\mathtt{Return}$
+(28,536 incidences). 
+By contrast, the least common replacement was an $\mathtt{Assert}$
+statement replacing a $\mathtt{TypeDecl}$, which we did not observe. 
+The second least common replacements were replacing $\mathtt{Do}$ statements or $\mathtt{Label}$s for a $\mathtt{TypeDecl}$; we observed these once each.
 
 The most common
-\emph{replacer} statement kind (the statement kind that most commonly replaces
-others) is the \texttt{If Statement} (101,366 appearances). The least
-common \emph{replacer} is the \texttt{Type Declaration Statement} with 447
-appearances.
+\emph{replacement} statement (the statement kind that most commonly replaces
+others) is the $\mathtt{If}$ statement (101,366 appearances). The least
+common \emph{replacement} is the $\mathtt{TypeDecl}$ (447
+appearances).
 The most common \emph{replacee} was the
-\texttt{Return Statement} with 111,938 appearances; and the least common
-\emph{replacee} was the \texttt{Type Declaration}, with 399 appearances.
+$\mathtt{Return}$ (111,938 appearances); the least common
+\emph{replacee} was again the $\mathtt{TypeDecl}$ (399 appearances).
 
@@
 \noindent \textbf{Potential deletions and insertions} From Figure~\ref{fig:StmtType}, we
-can see that, expression, if, return, for and try catch statements are added
-most often. Meanwhile, the same types of statements are also deleted most
-often. This finding indicates that most bugs were fixed by changing the control
-flow of the program.
+can see that $\mathtt{expression}$, $\mathtt{If}$, $\mathtt{Return}$,
+$\mathtt{for}$ and $\mathtt{Try}$ statements are both added and deleted
+most often as compared to the other statement times. 
+These findings indicate that most bugs were fixed by changing control
+flow.
 
-An important study that complements for our study is the repair model approach
-proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, in which they discuss
-a probability distribution for when to apply which kind of edit. Although their
+An important study that complements ours is the repair model approach
+proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, which proposes
+a probability distribution suggesting when to apply which kind of edit. Although their
 approach is able to trace more fine-grain AST-level changes, our results are
@@
 analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
-and variable declaration statements are added/deleted/updated most often, which
-is also illustrated in Figure~\ref{fig:StmtType} (In Boa, method invocation and
-variable declaration fall into the category of expression). It is also worth
-mentioning that their study covers 14 repositories with 89,993 versioning
-transactions, while our study studies 380,125 repositories with 23,229,406
-revisions.
+and variable declarations are added/deleted/updated most often, which
+is also illustrated in Figure~\ref{fig:StmtType} (Boa groups method invocations and
+variable declarations into the $\mathtt{Expression}$ category).  Our study
+complements there at a much larger scale (we study 380,125 repositories with 23,229,406
+revisions as compared to the 14 repositories in the prior work).
 
@@
 
-\noindent\textbf{Threats to validity.} Since we are using a DSL
-provided by Boa, the correctness of our analysis
-depends on both our programs and Boa itself. For example, we rely on Boa to
+\noindent\textbf{Threats to validity.} The correctness of our analysis
+depends on both our programs and Boa and its DSL. For example, we rely on Boa to
 identify bug fixing revisions; however, precisely accomplishing this is an open
-problem.  To mitigate the risk of errors in
-implementation, we open source our scripts\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
+problem.  To mitigate the risk of implementation errors,
+we released our scripts\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
 Because Boa does not provide an easy mechanism

### 2016-03-11 MSRChallenge2016.tex
update java project count

@@
 First, we broadly characterize bug-fixing commits to Java code.  In this paper,
-we study the \emph{September 2015/Github} dataset on Boa, including $7,830,023$
+we study the \emph{September 2015/Github} dataset on Boa, including $554,864$
 Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
@@
 out of 10 bug fixing patterns, it is unlikely the final two will cover the
-difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we are still assuming that the patterns never appear together. 
+difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we still assume that the patterns never appear together. 
 %Moreover, our detection is imprecise, and might represent an upper bound. 

### 2016-03-11 MSRChallenge2016.tex
fix spelling
Two fixes

@@
 studied AST-level~\cite{Martinez:2015ez} and line-level
-changes~\cite{Asaduzzaman:2013gu} across bug fixing commits.
+changes~\cite{Asaduzzaman:2013df} across bug fixing commits.
 Although the granularity differs, our approach is also novel with respect to scale of
@@
 
-Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
+Table~\ref{tab:freqpattern} estimates the prevalence of PAR templates in the
 Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
@@
 \\
-\texttt{Do} &0.81&5.26&6.60&0.00&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
+\texttt{Do} &0.81&5.26&6.60&-&9.44&14.21&0.18&15.86&3.73&1.67&1.97&5.88&6.39&0.03&27.98
 \\

### 2016-03-11 MSRChallenge2016.tex
changes
changes for Hoan

@@
 \vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} ask
-some of the same questions we do, on  5 projects. We study a much
+some of the same questions we do, on 6 projects. We study a much
 larger dataset~\cite{dyer2013} with 380,125 repositories; and we look at more
@@
 %
-Table~\ref{tbl:new} shows that introducing new
+The bottom section of Table~\ref{tbl:new} shows that introducing new
 classes or variables is rare. On average, we still have $0.69$ new methods
@@
 additional study of repair in Java, as assumptions that underlie approaches that
-target C seem unlikely to translate directly.
+target C are unlikely to translate directly.
 

### 2016-03-14 MSRChallenge2016.tex
acknowledgements, plus some spacing

@@
 
-\subsection{Detection Approach}
+\vspace{1ex}
+\noindent\textbf{Detection Approach}
 Because direct diffs are difficult to identify on this dataset, we heuristically approximate the
@@
 
-\subsection{Results}
-
+\vspace{1ex}
 \noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
@@
 
+\section{Acknowledgements}
+
+This work is partially supported by the US Department of Defense through the
+Systems Engineering Research Center (SERC), Contract H98230-08-D-0171.
+
 \bibliographystyle{abbrv}

### 2016-03-14 MSRChallenge2016.tex
Spellcheck and update ISBN
Fixed margin violations

@@
 % ISBN
-\isbn{123-4567-24-567/08/06}
+\isbn{978-1-4503-4186-8}
 
@@
 (cf. Prophet~\cite{Long2016}, for C)?  What types of semantic scoping
-should limit mutations, given the relative stringence of the Java
+should limit mutations, given the relative stringency of the Java
 compiler?
@@
 
-First, we broadly characterize bug-fixing commits to Java code.  In this paper,
-we study the \emph{September 2015/Github} dataset on Boa, including $554,864$
-Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
-fixing.
+First, we broadly characterize bug-fixing commits to Java code.  In this
+paper, we study the \emph{September 2015/Github} dataset offered by Boa, including
+$554,864$ Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$
+as bug fixing.
 
@@
 \noindent
- {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
+ {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a
+ condition check to check that an array
     index is within bound right before the index is used.
@@
   contains {\em expr<var.length} or {\em var.length>expr} for both pre- and
-  post-fix version. If there is a larger count in post-fix version, we consider that an instance of the AOB pattern is found.
+  post-fix versions. If there is a larger count in post-fix version, we consider that an instance of the AOB pattern is found.
 
@@
 
-An important study that complements ours is the repair model approach
-proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, which proposes
-a probability distribution suggesting when to apply which kind of edit. Although their
-approach is able to trace more fine-grain AST-level changes, our results are
+An important study that complements ours is the repair model approach proposed
+by Martinez and Monperrus~\cite{Martinez:2015ez}, which proposes a probability
+distribution suggesting when to apply which kind of edit. Although their
+approach can trace more fine-grain AST-level changes, our results are
 consistent with their findings. For example, their empirical
 analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
-and variable declarations are added/deleted/updated most often, which
-is also illustrated in Figure~\ref{fig:StmtType} (Boa groups method invocations and
+and variable declarations are added/deleted/updated most often, which is also
+illustrated in Figure~\ref{fig:StmtType} (Boa groups method invocations and
 variable declarations into the $\mathtt{Expression}$ category).  Our study
-complements there at a much larger scale (we study 380,125 repositories with 23,229,406
-revisions as compared to the 14 repositories in the prior work).
+complements there at a much larger scale (we study 380,125 repositories with
+23,229,406 revisions as compared to the 14 repositories in the prior work).
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 
